### 2018-11-01 paper.tex
Initial commit

\documentclass[a4paper, twoside]{article}

\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
\usepackage{booktabs}

\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{apalike}

\subfigtopskip=0pt
\subfigcapskip=0pt
\subfigbottomskip=0pt

\usepackage{siunitx}
\usepackage{tikz}

\usetikzlibrary{calc,arrows.meta,intersections,backgrounds,shapes.misc}

\usepackage{SCITEPRESS}     % Please add other packages that you may need BEFORE the SCITEPRESS.sty package.

\begin{document}

\title{Designing an Indoor Guidance System for the Visually Impaired}

\author{
  \authorname{John Anon{\sup{1}}}
  \affiliation{\sup{1}Anon University of Anon, Anonville, Anonistan}
  \email{anon.anon@anon.com}
%\affiliation{\sup{1}Lincoln Centre for Autonomous Systems (L-CAS), University of Lincoln, Lincoln, UK}
%\email{jlock@lincoln.ac.uk}
}

\keywords{Active vision, vision impaired, Markov decision process, object search}

\abstract{In this work, we propose an active vision system that uses a Markov Decision Process and mobile phone to enable a user to find an object in an unknown environment. This project aims to deliver a workable system to the visually impaired, but a set of experiments were carried out with sighted participants to determine the effectiveness of the system. We found that the system works reasonably well and compares well to similar systems. However, some improvements are required before it is ready for real-world use. }

\onecolumn \maketitle \normalsize \vfill

\section{\uppercase{Introduction}}

\noindent We are designing an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely safely navigate towards their desired destination or find an object in an unknown and dynamic environment. One requirement for this is the ability for a device to automatically make sense of the user's surroundings and determine the optimal route to get to the final destination based on what the user/camera sees, thereby roughly emulating a normally sighted user's navigation strategy in an unknown environment.

In this paper we discuss the first steps we've taken into implementing such a system. Specifically, we implemented a system with the capability to understand the user's surroundings and determine what the next best course of action is to reach the target location, based on what the system is currently seeing and what it has seen in the past. We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action, $a$, our agent (the guidance system in this case) takes when it is in some state $s$.

This work's main contribution is the design of a guidance system and MDP that can drive a user to point a mobile device's camera towards a given point in space in and find a target object. The interface is pictured in Figure~\ref{fig:system-screenshot}. We also present and discuss preliminary experimental results to show how effective the system is at finding a target.

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{figures/system_screenshot.png}
  \caption{A screenshot of the guidance interface showing a waypoint (based on an 3D Android model), the object scanner area and the guidance instruction arrows. }\label{fig:system-screenshot}
\end{figure}

The next section discusses other relevant work done in this field, followed by a detailed discussion on the design of the guidance system and MDP\@. Then we discuss the experiment and present its results, after which we conclude the paper and discuss the project's next steps.

\section{\uppercase{Previous Work}}

\noindent Assistive vision and guidance for the VI is an active and diverse field of study. In recent years, the increase in mobile processing power and computer vision improvements have led to researchers investigating using a cellphone camera to augment or enhance a user's vision and help them find objects or another point of interest. Earlier attempts at the problem involved placing special markers or barcodes, encoded with information about an object or the area, around an environment, which the user then scans with a cellphone or similar mobile device~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}. This device then uses some feedback mode, e.g.\ Braille and sound, to guide the user towards the target. The major drawbacks to this approach is the significant upfront effort required to augment entire areas with markers to a point where the system will be useful to a VI user. Furthermore, these passive systems rely on the user scanning the marker in the first place; something that can be made more complicated with markers degrading over time, changing ambient lighting, different viewing angles and marker occlusion.

Another approach is to discard tags completely and rely on computer vision to perform the object detection, something that has become more plausible with recent improvements to feature detectors and deep networks~\cite{huang2017speed,redmon2016you}. The system described~\cite{schauerte2012assistive} uses a combination of Scale Invariant Feature Transform (SIFT)~\cite{lowe1999object} and Speeded Up Robust Features (SURF)~\cite{bay2006surf} to detect known objects when they are in the camera's view and guide the user to them using sonified guidance instructions. This system is more flexible than the tag-based ones, but have the same drawback of being passive and rely on chance for the user to place the object within the camera's view in the first place. The paper also does not report on any performance metrics. In~\cite{bigham2010vizwiz}, the authors discuss their VizWiz system that offloads the object recognition tasks to an Amazon Mechanical Turk worker that then provides feedback on where the object of interest is located relative to the user. The VizWiz has the advantage of being fairly robust and is able to classify a great deal of objects with little effort from the user and can provide natural, human-generated and curated directions. However, this approach does not address the issue of enhancing user independence, since the user is now beholden to an online worker instead of a relative, friend or bystander. Furthermore, a good internet connection is required on the device, perhaps limiting use in some poor-reception areas.

As shown here, much research has been performed on object recognition and guidance towards an object once detected. However, work on active object search is harder to come by. Therefore, in this work we attempt to implement a system that uses active vision~\cite{aloimonos1988active} to guide a user towards an out-of-view target object by using the history of past object observations made during the search. With this, we hope to make the searching process less random and move towards a more natural search object searching process.

\section{\uppercase{Guidance System Design}}

\noindent The guidance system is built into an Android app with Android's ARCore~\footnote{https://developers.google.com/ar/} API enabled and is designed with the goal of generating a path of waypoints for the user to follow with a camera that will lead to the target object. This path is generated one waypoint at a time by the system and is updated with every object observation the user makes when adjusting the camera. We modelled this optimal path search problem as a grid-world problem that is solved by an Markov Decision Process (MDP) model. The details of the grid layout and the MDP model are discussed in the sections below. For this initial design, the system only works in the pan and tilt dimension and the depth dimension will be added after successful testing of this version of the guidance system.

\subsection{Environment Design}\label{sec:env-design}

\noindent We model this problem on the familiar grid-world problem, where an agent is tasked move to a terminal square from an origin square given some constraints. However, instead of the traditional, linear grid-world problem, we use the grid in a radial coordinate system which surrounds the user and each grid square represent a pan/tilt angle coordinate. See Fig.~\ref{fig:environment} for an example grid. Since we do not consider the depth dimension yet, each grid square is equidistant from the user and agent. The agent translates between the squares as the user points the camera in different directions.

\begin{figure}  
  \centering
  \input{figures/fig.tex}
\caption{A diagram of the radial grid-world used in the MDP is modelled with. }\label{fig:environment}
\end{figure}

MDPs are well-suited to solving this class of problem, i.e.\ to find the optimal route from the origin square to the terminal square, so modelling our problem as a grid-world allows us to design our guidance system and MDP model with existing and well-understood models and techniques. Each square of the grid represents a combination of the agent's pan-tilt-observation, or state, which is discussed in more detail in Sec.~\ref{sec:states}. The terminal square is the square whose state contains the target object, or observation. The grid size can be adjusted to control the model's resolution: smaller squares will increase accuracy, but at the cost of performance, both during use (more squares need to be traversed) and training (much larger state space). For the initial system design, we set the grid resolution to \SI{30}{\degree}.

\subsection{MDP Design}

\noindent The MDP model was used to produce a policy that defines a set of optimal actions for the agent to take in any given state. In this case, the agent is defined as the mobile phone and guidance system and the policy is used to generate the next waypoint on the search path towards the square on the grid that contains the target object. We initially assume perfect state and transition observability for each timestep and once we have a better understanding of the sensor limitations, we can expand the problem to a more sophisticated, and perhaps more representative, Partially Observable MDP (POMDP) problem. For now, the problem is given by the 5-tuple

\begin{equation}
  <\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \gamma>, 
\end{equation}
where $\mathbf{S}$ is a set of possible states the agent can be in, $\mathbf{A}$ is a set of possible actions an agent can take in any given state, $\mathbf{T}$, is a set of state transition probabilities defining the probability of transitioning from state $s$ to state $s'$. $\mathbf{R}$ is the reward function defining the immediate reward the agent receives from executing an action $a$ in state $s$, and $\gamma$ is a discount factor which represents the models priority in maximising immediate rewards over long-term reward. Each of these elements are defined and discussed here.

\subsubsection{States}\label{sec:states}

\noindent The state is a combination of different trackable parameters that the agent may possess at any given time that defines the agent's decision process. The agent's state vector is given by

\begin{equation}
  \mathbf{S} = s(o, n, s), 
\end{equation}
where $o$ is the current observation, $n$ is the number of steps taken during the search and $s$ is a binary variable that tracks whether a pan/tilt position has been visited before during the search. There are 8 observations encoded into the system, including a `nothing' observation where nothing of note is observed, and they are also the possible targets. For an initial implementation, we are simulating a simple office and we selected the possible objects as objects one might typically expect to see in a normal office. These objects are

\begin{equation}
  \begin{aligned}
    o\in \{monitor, mouse, keyboard, window, mug,\\ office\;supplies, desk, nothing\}.
  \end{aligned}
\end{equation}

The model tracks a total of 12 steps to the target. We select 12 since the longest route one could take between the furthest corners on the 6$\times$6 grid we used is 12. The MDP therefore has a total of 216 possible states ($8\times12\times2$).

\subsubsection{Actions}

The policy produced by an MDP define the action an agent will take when it finds itself in any given state. In this case, the action is the direction the user should move towards in a grid-world context, i.e.\ the angular adjustment the user must make to the camera to move along the search path. This action is interpreted by the guidance system and a new waypoint is added to the search path toward the target object. The action is defined by

\begin{equation}
  \mathbf{A} = a(s),
\end{equation}
and the possible actions are

\begin{equation}
  a\in \{UP, DOWN, LEFT, RIGHT\}.
\end{equation}

The number of actions can of course be expanded to increase resolution, but for this experiment and grid setup, they are sufficient.

\subsubsection{State Transition Probabilities}

\noindent The state transition function, $\mathbf{T}$, defines the likelihood of the agent transitioning into a state $s'$ from state $s$ when taking an action $a$, i.e.\ the likelihood of moving into a square and making observation $o$ after performing action $a$. It therefore contains the spatial relationships between the different objects in the observation set. Formally, the transition function is defined by

\begin{equation}
  T(s, a, s') = t.
\end{equation}

The spatial relationships are extracted from Google's OpenImage dataset\footnote{https://storage.googleapis.com/openimages/web/index.html}~\cite{openimages}. This dataset consists of 1.74M images containing 14.6M labelled bounding boxes manually drawn around objects and is primarily aimed toward object recognition researchers to test their models on. However, with the bounding boxes and object labels we can extract the spatial relationships between the different objects in our observation set. Since the camera perspectives and absolute distances between the objects in the images aren't given, we can only extract the relationships in simple terms with little context, e.g.\ we can only say that object 1 is above object 2, but not how far above. Our simple action-space and grid environment somewhat compensates for this lack of complexity in the dataset.

\subsubsection{Reward Function}

\noindent The reward function, $\mathbf{R}$, is the immediate reward that the agent receives after transitioning from state $s$ to state $s'$ and is given by

\begin{equation}
  \mathbf{R} = r(s, s').
\end{equation} 
This is an important parameter for training the agent to produce the most effective policy.

During training, we define a negative reward for exceeding the 12-step limit we defined in the model, as well as if it re-enters a previous search location. Conversely, the agent is given a significant reward when it finds the target object. The goal of the agent is to maximise its cumulative reward over time. These numbers are chosen such that they motivate the agent to reach the target, while hastening the process by punishing it every time it re-explores a state and the longer it takes to reach the target.

\subsubsection{Model Training}

\noindent The policy is generated through a training process where the agent is placed in an environment with some constraints and attempts to maximise its short- and long-term reward through interacting with the environment. This problem is solved as an optimisation problem, where the agent will potentially start with a very inefficient, or wholly ineffective, policy and over time and many iterations, improve its policy and reach the target in an optimum number of timesteps.

The training environment is a simple mathematical representation of the grid-world described in Sec.~\ref{sec:env-design} that have the following constraints during training to optimise the agent's search strategy:

\begin{itemize}
  \item the agent must face forward, i.e.\ viewing angle must be less than \SI{90}{\degree} from the vertical and horizontal planes,
  \item the agent can only move one square (angle interval) at a time, 
  \item the process terminates when the target object is observed,
\end{itemize}

The lack of absolute spatial information in the OpenImage dataset made the data seem fairly ambiguous in some cases, which makes it hard to find a single, optimal solution to the problem. We therefore could not use the popular value iteration algorithm~\cite{bellman1957markovian} and opted for the state-action-reward-state-action (SARSA) algorithm~\cite{rummery1994line} instead. SARSA is an on-policy algorithm with the advantage of being more exploratory in nature and is therefore more likely to find a solution. However, this solution is not guaranteed to be optimal, but can get very close to the optimal solution. This is a fairly simple MDP with a relatively small state-action-observation space, which makes it possible to find a solution in a reasonable amount of time. However, it should be noted that adjusting the angle interval or adding more actions or observations can easily blow up the size of the state-space.

\section{\uppercase{Experiments}}

\noindent To test the effectiveness of the policy the MDP produced, we designed a set of experiments that determined how effective the system is at directing a participant to pointing towards a target object. This section discusses all of the simulations and experiments that were carried out.

\subsection{Experiment Design}

\noindent To test the viability and effectiveness of our system, we carried out a set of experiments. For this, the MDP policies were integrated into an Android application that uses the camera to provide observation data and track the pose and viewing direction. We avoided adding unnecessary variability and complexity to the experiment by providing visual waypoints on screen which the participants were allowed to use. In addition to this, encoded QR codes and the Android barcode scanner library were used to simulate object detection. A generic environment mimicking a typical office desk layout was set up as the experiment environment and contains 7 different objects (i.e.\ encoded QR codes), one of which were the target object. See Figure~\ref{fig:env-picture} for a picture of the environment.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figures/test_env_picture.jpg}
  \caption{A picture of the environment used for the experiments. Each QR code represents an object. }\label{fig:env-picture}
\end{figure}

For each experiment, the participant was placed roughly \SI{1}{\meter} from the barcodes and was asked not to move from that spot during the experiment. The participant then pressed a button on the app that randomly selected a target object and was then guided towards that target by the app. Since the participants were allowed to use their vision, the targets were randomly selected and the participants were uninformed of what the target object was until it was found. This was done to avoid the participants learning the target objects' locations between each search run.

During in-house tests, we noted that the system sometimes makes guidance mistakes that lead the user towards the edge of the search space, at which point the system had difficulty guiding the user back to the centre. To avoid this having an adverse impact and drawing out the experiments too long, we set a search step limit of 16, which means that only 16 waypoints were be generated before the search was terminated. A search run therefore ended when the participant either successfully found the target object by pointing the phone camera to it and scanning the barcode, or exceeded the waypoint limit. After this, the participant then resets to the central position, selects a new target object and resumes the experiment.

The participants were left to repeat this process until we recorded 10 searches per object, giving us a total number of 70 recorded search samples per participant. We tested a total of 10 different participants (sex: 8 M, 2 F;\@ age: $\mu$ 31.2 years, $\sigma$ 8 years), most of which were sourced from our laboratory with none having any disabilities or handicaps. This gives our dataset a total of 700 search samples.

\subsection{Results}

\noindent In order to evaluate our system, we identified 3 different measures: target acquisition rate (TAR), number of steps to the target and the total time it took to find a target object. We present and discuss the results for each of these parameters in the next sections. All of the results are summarised in Table~\ref{tab:results-summary}.

\begin{table}
  \centering
  \caption{A table containing a summary of the TAR, steps and time to target means ($\mu$) and standard deviations ($\sigma$) for each individual participant and the entire participant population.}\label{tab:results-summary}
  \begin{tabular}{cc|cc|cc}
    \toprule
    \multirow{2}{*}{Participant} & \multirow{2}{*}{TAR [\%]} & \multicolumn{2}{c|}{Num. Steps} & \multicolumn{2}{c}{Time [s]} \\ 
				 &			     & $\mu$ & $\sigma$		       & $\mu$ & $\sigma$  \\ \midrule
    s1 & 6.3 & 7.2 & 5.4 & 29 & 22 \\ \midrule
    s2 & 21 & 6.7 & 4.8 & 34 & 5.1 \\ \midrule
    s3 & 8.8 & 6.3 & 4.9 & 31 & 21 \\ \midrule
    s4 & 21 & 6.7 & 4.3 & 37 & 5.6 \\ \midrule
    s5 & 24 & 7.2 & 4.9 & 33 & 14 \\ \midrule
    s6 & 40 & 8.2 & 5.4 & 24 & 10 \\ \midrule
    s7 & 14 & 8.5 & 5.8 & 31 & 16 \\ \midrule
    s8 & 12 & 5.1 & 4.0 & 39 & 21 \\ \midrule
    s9 & 2.5 & 7.2 & 5.4 & 39 & 18 \\ \midrule
    s10 & 33 & 6.6 & 5.4 & 26 & 12 \\ \midrule\midrule
    Population & $\mu$: 18 $\sigma$: 11 & 6.8 & 5.1 & 34 & 23 \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Target Acquisition Rate}

\noindent The target acquisition rate (TAR) is a measure of how successful the system was at directing a participant to the target object within the 16-step limit we imposed and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches. See Figure~\ref{fig:incomplete-searches-subjects} for a plot showing the TAR for each participant. Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/incomplete_searches_subjects.png}
  \caption{A plot giving the proportion of searches that reached the 16-step limit we imposed for each participant. }\label{fig:incomplete-searches-subjects}
\end{figure}

The inter-participant spread ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance  With an average TAR of $18.3\%$, it is clear that our system can be improved with regards to entering a no-recovery state where it directs a user into dead-space with no spatial information (e.g.\ a ceiling or wall section) and cannot gather the information it requires to intelligently guide the user. Subsequent system updates will have to consider implementing fall-back methods or other automatic recovery modes that can detect entry of a no-recovery state (e.g.\ exceeding a set number of steps/time without making an observation) and guide the user back to the initial position.

\subsection{Number of Steps to Target}

\noindent The number of steps to target indicates the number of waypoints the system generated for the participant during the guidance process is a major indication of system performance, where less waypoints means better performance. Figure~\ref{fig:nsteps-participants} shows the distributions of the number of steps to the target for each individual participant.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/boxplot_nsteps_subjects.png}
  \caption{The distributions of each participant's number of steps taken to find a target object. }\label{fig:nsteps-participants}
\end{figure}

The number of waypoints each participant required is fairly consistent across all of the participants with a inter-participant standard deviation of 1 waypoint. The population mean and standard deviation is 6.8 and 5.1 waypoints respectively. This is a reasonable result that was also somewhat expected, since most target objects were placed within approximately 4 grid squares away from the participants' initial looking directions.

It is interesting to note that participants $s6$ and $s10$ also found their targets within these reasonable bounds when accounted for the targets that they found within the 16-step limit. This supports the argument from the previous results that their decreased TAR was partly caused by an abnormally high number of entries into a no-recovery state and further reinforces the need to implement an automatic recovery feature in the system before deployment.

\subsection{Time to Target}

\noindent The total time it took a participant to reach the target object is given in Figure~\ref{fig:time-participants}. In it we see that the inter-participant variance in the temporal response, with mean 29.8s and standard deviation 6.2s (population standard deviation of 23s), is far greater than for the number of waypoints they required. Indeed, there is not a strong relationship between the number of waypoints a participant required and the time they took to find the target, as showcased by participant $s7$'s wide mean waypoint count and spread in Figure~\ref{fig:nsteps-participants} and the small spread and close-to-average time to target in Figure~\ref{fig:time-participants}. Furthermore, the opposite can be observed in participant $s8$'s small spread and low mean waypoint count in Figure~\ref{fig:nsteps-participants} and high spread and high mean time to target in Figure~\ref{fig:time-participants}.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/boxplot_time_to_target_subjects.png}
  \caption{The distributions of the each participant's time taken to find a target object. }\label{fig:time-participants}
\end{figure}

In comparison to the VizWiz system~\cite{bigham2010vizwiz} (mean 92s, standard deviation 37.7s), our results look fairly reasonable. However, our results may look very different when we test the system with VI participants like they did in~\cite{bigham2010vizwiz}.

\section{\uppercase{Future Work and Conclusion}}

\noindent In this work we presented and tested an MDP-based system to guide a visually impaired (VI) person towards a target object with no apriori knowledge of the environment. We implemented the system in an Android app that we tested with a small group of sighted people to determine its viability and effectiveness at guiding user at finding and pointing a camera at a specific target. We found that is works fairly well when compared to alternative systems, with a respectable mean time of target acquisition of 32s. However, the system can be improved by refining the search strategy and implementing an automatic fail-state recovery system that will guide a user back to neutral position if a fail-state is entered (e.g.\ a blank section of wall).

The next steps to this project will involve using the data recorded here to improve and refine the MDP model that provides the guidance. The model can also be expanded to include more objects and actions. However, an important consideration and expansion to the problem is to change the MDP to an Partially Observable MDP (POMDP) that will bring the model more in line with reality by acknowledging that the objects are not perfectly observable and humans do not perfectly follow guidance instructions. This adjustment may be very important when we consider that we will replace the QR code detector with object recognition models that are typically more prone to making classification errors. Finally, the model can be adapted to use on-line learning techniques in order to further refine its transition model as the user uses the guidance system.

\clearpage
\bibliographystyle{apalike}
\bibliography{bib}

\end{document}

### 2018-11-02 paper.tex
Starting edits, added new control loop figure

@@
 
-\noindent We are designing an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely safely navigate towards their desired destination or find an object in an unknown and dynamic environment.
-One requirement for this is the ability for a device to automatically make sense of the user's surroundings and determine the optimal route to get to the final destination based on what the user/camera sees, thereby roughly emulating a normally sighted user's navigation strategy in an unknown environment.
+\noindent We are designing an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment, expanding upon ideas originally proposed in~\cite{bellotto2013}.
+The proposed system implements ideas from the active vision field and places a human in the control loop.
+This control loop, pictured in Figure~\ref{fig:control-loop}, comprises of a controller, $K$, that is given a reference signal (the desired objects in this case) that generates a control signal, $u$, which a human, $H$, uses to manipulate a sensor, $P$, to gather more information on the environment and move closer to the target object.
+%The goal of this system is to automatically make sense of the user's surroundings and determine the optimal route to get to the final destination based on what the user/camera sees, thereby roughly emulating a normally sighted user's navigation strategy in an unknown environment.
 
-In this paper we discuss the first steps we've taken into implementing such a system.
-Specifically, we implemented a system with the capability to understand the user's surroundings and determine what the next best course of action is to reach the target location, based on what the system is currently seeing and what it has seen in the past.
+\begin{figure}
+  \includegraphics[width=0.4\textwidth]{figures/control_loop.png}
+  \caption{The control }\label{fig:control-loop}
+\end{figure}
+
+In this paper we discuss the first steps we've taken into implementing the control-block, $K$, from Figure~\ref{fig:control-loop}.
+The goal of this system is to understand the user's surroundings and determine what the next best course of action is to reach the target location, based on what the system is currently seeing and what it has seen in the past.
 We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action, $a$, our agent (the guidance system in this case) takes when it is in some state $s$.
@@
 This work's main contribution is the design of a guidance system and MDP that can drive a user to point a mobile device's camera towards a given point in space in and find a target object.
-The interface is pictured in Figure~\ref{fig:system-screenshot}.
 We also present and discuss preliminary experimental results to show how effective the system is at finding a target.
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figures/system_screenshot.png}
-  \caption{A screenshot of the guidance interface showing a waypoint (based on an 3D Android model), the object scanner area and the guidance instruction arrows. }\label{fig:system-screenshot}
-\end{figure}
+Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the guidance system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}.
+Then we discuss the experiment and present its results in Section~\ref{sec:experiments}, after which we conclude the paper and discuss the project's next steps in Section~\ref{sec:conclusion}.
 
-The next section discusses other relevant work done in this field, followed by a detailed discussion on the design of the guidance system and MDP\@.
-Then we discuss the experiment and present its results, after which we conclude the paper and discuss the project's next steps.
-
-\section{\uppercase{Previous Work}}
+\section{\uppercase{Previous Work}}\label{sec:previous-work}
 
@@
 This device then uses some feedback mode, e.g.\ Braille and sound, to guide the user towards the target.
-The major drawbacks to this approach is the significant upfront effort required to augment entire areas with markers to a point where the system will be useful to a VI user.
+%The major drawbacks to this approach is the significant upfront effort required to augment entire areas with markers to a point where the system will be useful to a VI user.
 Furthermore, these passive systems rely on the user scanning the marker in the first place; something that can be made more complicated with markers degrading over time, changing ambient lighting, different viewing angles and marker occlusion.
@@
 Another approach is to discard tags completely and rely on computer vision to perform the object detection, something that has become more plausible with recent improvements to feature detectors and deep networks~\cite{huang2017speed,redmon2016you}.
-The system described~\cite{schauerte2012assistive} uses a combination of Scale Invariant Feature Transform (SIFT)~\cite{lowe1999object} and Speeded Up Robust Features (SURF)~\cite{bay2006surf} to detect known objects when they are in the camera's view and guide the user to them using sonified guidance instructions.
+The system described~\cite{schauerte2012assistive} uses a combination of SIFT and SURF to detect known objects when they are in the camera's view and guide the user to them using sonified guidance instructions.
 This system is more flexible than the tag-based ones, but have the same drawback of being passive and rely on chance for the user to place the object within the camera's view in the first place.
@@
 However, work on active object search is harder to come by.
-Therefore, in this work we attempt to implement a system that uses active vision~\cite{aloimonos1988active} to guide a user towards an out-of-view target object by using the history of past object observations made during the search.
-With this, we hope to make the searching process less random and move towards a more natural search object searching process.
+Therefore, in this work we attempt to implement an active vision~\cite{aloimonos1988active, bellotto2013, lock2017portable} that can guide a user towards an out-of-view target object by using prior knowledge of the spatial distribution of objects within an indoor environment and the history of past object observations made during the search.
+With this, we hope to make the searching process less random and move towards a more natural search object searching process to the benefit of the VI.
 
-\section{\uppercase{Guidance System Design}}
+\section{\uppercase{Active Vision System Design}}\label{sec:system-design}
+
+\section{\uppercase{Human-control Module}}\label{sec:controller-design}
 
@@
 
-\section{\uppercase{Experiments}}
+\section{\uppercase{Experiments}}]\label{sec:experiments}
 
@@
   \caption{A picture of the environment used for the experiments. Each QR code represents an object. }\label{fig:env-picture}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.3\textwidth]{figures/system_screenshot.png}
+  \caption{A screenshot of the guidance interface showing a waypoint (based on an 3D Android model), the object scanner area and the guidance instruction arrows. }\label{fig:system-screenshot}
 \end{figure}
@@
 
-\section{\uppercase{Future Work and Conclusion}}
+\section{\uppercase{Future Work and Conclusion}}\label{sec:conclusion}
 

### 2018-11-05 paper.tex
First edit round for first 4 sections@

@@
 
-\noindent We are designing an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment, expanding upon ideas originally proposed in~\cite{bellotto2013}.
+\noindent We are designing an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment, expanding upon ideas originally proposed in~\cite{bellotto2013} and expanded on in~\cite{lock2017portable}.
 The proposed system implements ideas from the active vision field and places a human in the control loop.
@@
 
-\begin{figure}
-  \includegraphics[width=0.4\textwidth]{figures/control_loop.png}
-  \caption{The control }\label{fig:control-loop}
-\end{figure}
-
-In this paper we discuss the first steps we've taken into implementing the control-block, $K$, from Figure~\ref{fig:control-loop}.
+In this paper we discuss the first steps we have taken into implementing the control-block, $K$, from Figure~\ref{fig:control-loop}.
 The goal of this system is to understand the user's surroundings and determine what the next best course of action is to reach the target location, based on what the system is currently seeing and what it has seen in the past.
 We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action, $a$, our agent (the guidance system in this case) takes when it is in some state $s$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/control_loop.png}
+  \caption{MEME}\label{fig:control-loop}
+\end{figure}
 
@@
 However, work on active object search is harder to come by.
-Therefore, in this work we attempt to implement an active vision~\cite{aloimonos1988active, bellotto2013, lock2017portable} that can guide a user towards an out-of-view target object by using prior knowledge of the spatial distribution of objects within an indoor environment and the history of past object observations made during the search.
-With this, we hope to make the searching process less random and move towards a more natural search object searching process to the benefit of the VI.
+Therefore, in this work we attempt to implement an active vision~\cite{aloimonos1988active,bellotto2013,lock2017portable} that can guide a user towards an out-of-view target object by using prior knowledge of the spatial distribution of objects within an indoor environment and the history of past object observations made during the search.
+With this, we hope to make the searching process less random and move towards a more natural search object searching process to the benefit of the VI\@.
 
 \section{\uppercase{Active Vision System Design}}\label{sec:system-design}
+
+\noindent The ActiVis project's goal is to deliver a stand-alone system that is capable of accepting user input on a target object\textbackslash{}destination and guide a VI user to it.
+A complete system diagram is given is Figure~\ref{fig:control-loop} and consists of a number of elements, or blocks
+
+From Figure~\ref{fig:control-loop}, it can be seen that the system layout is similar to that of a classical control problem where a controller generates a control signal that drives a component towards some reference point.
+In this case, the reference signal, $r$, is the object the user wishes to find, which the system can achieve by placing that object within the camera's view.
+Therefore, the goal of the control block, $K$, is to generate guidance instructions, $u$, in the form of visual or audio instructions, to drive the along a search path.
+Since we are not working with a electro-mechanical system, we have an extra suer block, $H$, that interprets $u$ and executes a physical action, $u^*$, that manipulates the sensor, $P$, to point in another direction and make a new observation.
+The cycle is repeated if the target object is not observed.
+
+This work focusses on implementing $K$ and there are 2 points of interest to implementing such a controller successfully.
+Firstly, $K$ must be environment-agnostic, meaning that it cannot be constrained to specific environment since objects are not necessarily placed in the same place in every environment.
+Secondly, the controller must be robust enough to handle a badly interpreted $u$ signal.
+The risk of that happening can be minimised by generating clear and simple signals, ensuring $u^*$ closely tracks the original signal, $u$.
 
@@
 The details of the grid layout and the MDP model are discussed in the sections below.
-For this initial design, the system only works in the pan and tilt dimension and the depth dimension will be added after successful testing of this version of the guidance system.
+%For this initial design, the system only works in the pan and tilt dimension and the depth dimension will be added after successful testing of this version of the guidance system.
 
-\subsection{Environment Design}\label{sec:env-design}
+%\subsection{Environment Model}\label{sec:env-design}
 
-\noindent We model this problem on the familiar grid-world problem, where an agent is tasked move to a terminal square from an origin square given some constraints.
+%\noindent We model this problem on the familiar grid-world problem, where an agent is tasked move to a terminal square from an origin square given some constraints.
 However, instead of the traditional, linear grid-world problem, we use the grid in a radial coordinate system which surrounds the user and each grid square represent a pan/tilt angle coordinate.
@@
 
-\begin{figure}  
-  \centering
-  \input{figures/fig.tex}
-\caption{A diagram of the radial grid-world used in the MDP is modelled with. }\label{fig:environment}
-\end{figure}
+%\begin{figure}  
+  %\centering
+  %\input{figures/fig.tex}
+%\caption{A diagram of the radial grid-world used in the MDP is modelled with. }\label{fig:environment}
+%\end{figure}
 
-MDPs are well-suited to solving this class of problem, i.e.\ to find the optimal route from the origin square to the terminal square, so modelling our problem as a grid-world allows us to design our guidance system and MDP model with existing and well-understood models and techniques.
+%MDPs are well-suited to solving this class of problem, i.e.\ to find the optimal route from the origin square to the terminal square, so modelling our problem as a grid-world allows us to design our guidance system and MDP model with existing and well-understood models and techniques.
 Each square of the grid represents a combination of the agent's pan-tilt-observation, or state, which is discussed in more detail in Sec.~\ref{sec:states}.
@@
 
-\subsection{MDP Design}
+\subsection{MDP for Human Control}
 
-\noindent The MDP model was used to produce a policy that defines a set of optimal actions for the agent to take in any given state.
+\noindent An MDP was used to produce a policy that defines a set of optimal actions for the agent to take in any given state.
 In this case, the agent is defined as the mobile phone and guidance system and the policy is used to generate the next waypoint on the search path towards the square on the grid that contains the target object.
-We initially assume perfect state and transition observability for each timestep and once we have a better understanding of the sensor limitations, we can expand the problem to a more sophisticated, and perhaps more representative, Partially Observable MDP (POMDP) problem.
-For now, the problem is given by the 5-tuple
+We initially assume perfect state and transition observability for each timestep.
+The problem is given by the 5-tuple
 
 \begin{equation}
-  <\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \gamma>, 
+  \langle{}\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \gamma\rangle, 
 \end{equation}
 where $\mathbf{S}$ is a set of possible states the agent can be in, $\mathbf{A}$ is a set of possible actions an agent can take in any given state, $\mathbf{T}$, is a set of state transition probabilities defining the probability of transitioning from state $s$ to state $s'$.
-$\mathbf{R}$ is the reward function defining the immediate reward the agent receives from executing an action $a$ in state $s$, and $\gamma$ is a discount factor which represents the models priority in maximising immediate rewards over long-term reward.
-Each of these elements are defined and discussed here.
+$\mathbf{R}$ is the reward function defining the immediate reward the agent receives reaching state $s'$ after executing action $a$ in state $s$, and $\gamma$ is a discount factor which maximises immediate over long-term rewards.
+Each of these elements are defined and discussed next.
+
+\subsubsection{Reward Function}
+
+\noindent The reward function, $r$, is the immediate reward that the agent receives after transitioning from state $s$ to state $s'$ and is given by
+
+\begin{equation}
+  r = \langle{}s, s'\rangle, r\in{}\mathbf{R}.
+\end{equation}
+
+The reward function is a very important parameter for training the agent to produce the most effective policy.
+We define a constant negative reward for every step the agent takes, and increase this negative reward if the agent exceeds the 12-step limit we defined in the model, as well as if it regenerates a waypoint in a previously searched location.
+The values used here are given in Table~\ref{tab:rewards}.
+
+\begin{table}
+  \centering
+  \caption{MEME}\label{tab:rewards}
+  \begin{tabular}{ll}
+    \toprule
+    $s\in\mathbf{S}$ & -1.0  \\ \midrule
+    $s(n >= 9)$ & -10.0 \\ \midrule
+    $s(v = 1)$  & -10.0 \\ \midrule
+    $s(o = \text{target})$ & 10000 \\ \midrule
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+The goal of the agent is to maximise its cumulative reward over time and these numbers are chosen such that they actively motivate the agent to reach the target, while hastening the process by slightly punishing it for each step it takes and increasing the punishment every time it re-explores a state and the longer it takes to reach the target.
 
@@
 
-\noindent The state is a combination of different trackable parameters that the agent may possess at any given time that defines the agent's decision process. The agent's state vector is given by
+\noindent The state is a combination of parameters that defines the agent's decision process. The agent's state vector is given by
 
 \begin{equation}
-  \mathbf{S} = s(o, n, s), 
+  s = \langle{}o, n, v\rangle, s\in{}\mathbf{S}, 
 \end{equation}
-where $o$ is the current observation, $n$ is the number of steps taken during the search and $s$ is a binary variable that tracks whether a pan/tilt position has been visited before during the search.
-There are 8 observations encoded into the system, including a `nothing' observation where nothing of note is observed, and they are also the possible targets.
-For an initial implementation, we are simulating a simple office and we selected the possible objects as objects one might typically expect to see in a normal office.
-These objects are
+where $o$ is the current object, $n$ is the number of steps taken since the search started and $v$ is a binary variable that tracks whether a pan/tilt position has been generated as a waypoint before during the search.
+There are 8 objects encoded into the system, including a `nothing' instance where nothing of note is observed.
+Our initial implementation considers a simple office desk scenario containing the following objects:
 
@@
   \begin{aligned}
-    o\in \{monitor, mouse, keyboard, window, mug,\\ office\;supplies, desk, nothing\}.
+    o\in \mathbf{O} = \{monitor, mouse, keyboard, window,\\mug, stationary, desk, nothing\}.
   \end{aligned}
@@
 
-The model tracks a total of 12 steps to the target.
-We select 12 since the longest route one could take between the furthest corners on the 6$\times$6 grid we used is 12.
-The MDP therefore has a total of 216 possible states ($8\times12\times2$).
+Our implementation is designed for a 6$\times$6 discretised, radial grid for convenience and replicability through different experiments.
+The grid spans \SI{180}{\degree} in the pan and tilt dimensions, giving a grid resolution of \SI{30}{\degree} per grid square.
+We set the model to track a maximum of of 9 steps to the target, with 9 being the longest possible route on the grid.
+A search can take longer than 9 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function.
+The MDP therefore has a total of 144 possible states ($8\times9\times2$).
 
@@
 This action is interpreted by the guidance system and a new waypoint is added to the search path toward the target object.
-The action is defined by
+The possible actions are defined by
 
 \begin{equation}
-  \mathbf{A} = a(s),
+  a = \langle{}s\rangle, a\in{}\mathbf{A},
 \end{equation}
@@
 \begin{equation}
-  a\in \{UP, DOWN, LEFT, RIGHT\}.
+  \mathbf{A} = \{UP, DOWN, LEFT, RIGHT\}.
 \end{equation}
-
-The number of actions can of course be expanded to increase resolution, but for this experiment and grid setup, they are sufficient.
+These actions were chosen to conform to the grid implementation and increase the tracking performance of $u^*$ w.r.t\@ $u$.
 
@@
 
-\noindent The state transition function, $\mathbf{T}$, defines the likelihood of the agent transitioning into a state $s'$ from state $s$ when taking an action $a$, i.e.\ the likelihood of moving into a square and making observation $o$ after performing action $a$.
-It therefore contains the spatial relationships between the different objects in the observation set.
+\noindent The state transition function, $\mathbf{T}$, defines the likelihood of the agent transitioning into a state $s'$ from state $s$ when taking an action $a$, i.e.\ the likelihood of moving into a square and observing object $o$ after performing action $a$.
+It therefore represent the spatial relationships between the different objects in the environment model.
 Formally, the transition function is defined by
@@
 \begin{equation}
-  T(s, a, s') = t.
+  t\langle{}s, a, s'\rangle, t\in{}\mathbf{T}.
 \end{equation}
 
-The spatial relationships are extracted from Google's OpenImage dataset\footnote{https://storage.googleapis.com/openimages/web/index.html}~\cite{openimages}.
-This dataset consists of 1.74M images containing 14.6M labelled bounding boxes manually drawn around objects and is primarily aimed toward object recognition researchers to test their models on.
-However, with the bounding boxes and object labels we can extract the spatial relationships between the different objects in our observation set.
-Since the camera perspectives and absolute distances between the objects in the images aren't given, we can only extract the relationships in simple terms with little context, e.g.\ we can only say that object 1 is above object 2, but not how far above.
+The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset\footnote{https://storage.googleapis.com/openimages/web/index.html}~\cite{openimages}.
+This dataset consists of 1.74M images containing 14.6M labelled bounding boxes manually drawn around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to test their models on.
+However, using the bounding boxes and object labels we can extract the spatial relationships between the different objects in $\mathbf{O}$.
+Since the camera perspectives and absolute distances between the objects in the images are not given, we can only extract the relationships in terms of the actions specified in $\mathbf{A}$, e.g.\ we can only say that object 1 is above object 2, but not how far above.
 Our simple action-space and grid environment somewhat compensates for this lack of complexity in the dataset.
 
-\subsubsection{Reward Function}
-
-\noindent The reward function, $\mathbf{R}$, is the immediate reward that the agent receives after transitioning from state $s$ to state $s'$ and is given by
-
-\begin{equation}
-  \mathbf{R} = r(s, s').
-\end{equation} 
-This is an important parameter for training the agent to produce the most effective policy.
-
-During training, we define a negative reward for exceeding the 12-step limit we defined in the model, as well as if it re-enters a previous search location.
-Conversely, the agent is given a significant reward when it finds the target object.
-The goal of the agent is to maximise its cumulative reward over time.
-These numbers are chosen such that they motivate the agent to reach the target, while hastening the process by punishing it every time it re-explores a state and the longer it takes to reach the target.
+\begin{figure}
+  \centering
+  \begin{subfigure}
+    \centering
+    \includegraphics[width=0.4\textwidth]{figures/desk_example.png}
+  \end{subfigure}
+  \begin{subfigure}
+    \centering
+    \includegraphics[width=0.4\textwidth]{figures/mug_example.png}
+  \end{subfigure}
+  \caption{MEME~\cite{openimages}}\label{fig:openimage-example}
+\end{figure}
 
@@
 
-\noindent The policy is generated through a training process where the agent is placed in an environment with some constraints and attempts to maximise its short- and long-term reward through interacting with the environment.
-This problem is solved as an optimisation problem, where the agent will potentially start with a very inefficient, or wholly ineffective, policy and over time and many iterations, improve its policy and reach the target in an optimum number of timesteps.
+\noindent The output of an MDP is a so-called policy that defines the action an agent will take when it is in any given state.
+A policy is generated by having an agent explore the entire state-space and through many iterations improve its decision function, i.e.\ policy, in order to reach the target state in a way that maximises its cumulative reward.
+This method is called Q-learning and does not require a model of its environment during training.
 
-The training environment is a simple mathematical representation of the grid-world described in Sec.~\ref{sec:env-design} that have the following constraints during training to optimise the agent's search strategy:
+The agent's target state is any state combination where $o$ is the target object, since we are primarily concerned with finding the target object.
+Each target object has its own unique policy file and there are 18 terminal state in total (9$\times$2) per policy.
 
-\begin{itemize}
-  \item the agent must face forward, i.e.\ viewing angle must be less than \SI{90}{\degree} from the vertical and horizontal planes,
-  \item the agent can only move one square (angle interval) at a time, 
-  \item the process terminates when the target object is observed,
-\end{itemize}
+The lack of absolute spatial information in the OpenImage dataset generates ambiguities which makes it hard for the model to converge to a single, optimal solution.
+We therefore could not use the popular value iteration algorithm~\cite{bellman1957markovian} and opted for the state-action-reward-state-action (SARSA) algorithm~\cite{rummery1994line} instead.
+SARSA is an on-policy algorithm with the advantage of being more exploratory in nature and is therefore more likely to find a solution, but this solution is not guaranteed to be optimal.
+Our MDP has a relatively small state-action space.
+Therefore, a solution can be found in a reasonable amount of time.
+However, it should be noted that adjusting the angle interval, or adding more actions or objects, can easily blow up the size of the state-space.
 
-The lack of absolute spatial information in the OpenImage dataset made the data seem fairly ambiguous in some cases, which makes it hard to find a single, optimal solution to the problem.
-We therefore could not use the popular value iteration algorithm~\cite{bellman1957markovian} and opted for the state-action-reward-state-action (SARSA) algorithm~\cite{rummery1994line} instead.
-SARSA is an on-policy algorithm with the advantage of being more exploratory in nature and is therefore more likely to find a solution.
-However, this solution is not guaranteed to be optimal, but can get very close to the optimal solution.
-This is a fairly simple MDP with a relatively small state-action-observation space, which makes it possible to find a solution in a reasonable amount of time.
-However, it should be noted that adjusting the angle interval or adding more actions or observations can easily blow up the size of the state-space.
-
-\section{\uppercase{Experiments}}]\label{sec:experiments}
+\section{\uppercase{Experiments}}\label{sec:experiments}
 

### 2018-11-05 paper.tex
Fixed some small captions and titles I forgot about

@@
 \usepackage{siunitx}
-\usepackage{tikz}
+%\usepackage{tikz}
 
-\usetikzlibrary{calc,arrows.meta,intersections,backgrounds,shapes.misc}
+%\usetikzlibrary{calc,arrows.meta,intersections,backgrounds,shapes.misc}
 
@@
 
-\title{Designing an Indoor Guidance System for the Visually Impaired}
+\title{Designing an Active Vision Indoor Object Search Guidance System}
 
@@
 
-\keywords{Active vision, vision impaired, Markov decision process, object search}
+\keywords{Active vision, object search, vision impaired, Markov decision process}
 
 \abstract{In this work, we propose an active vision system that uses a Markov Decision Process and mobile phone to enable a user to find an object in an unknown environment.
-This project aims to deliver a workable system to the visually impaired, but a set of experiments were carried out with sighted participants to determine the effectiveness of the system.
+An initial implementation of this system was implemented and tested with a set of experiments were carried out with sighted participants to determine the effectiveness of the system.
 We found that the system works reasonably well and compares well to similar systems.
-However, some improvements are required before it is ready for real-world use.
 }
@@
 
-\noindent We are designing an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment, expanding upon ideas originally proposed in~\cite{bellotto2013} and expanded on in~\cite{lock2017portable}.
+\noindent We are designing an indoor navigation system (ActiVis) targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment, expanding upon ideas originally proposed in~\cite{bellotto2013} and expanded on in~\cite{lock2017portable}.
 The proposed system implements ideas from the active vision field and places a human in the control loop.
@@
 In this paper we discuss the first steps we have taken into implementing the control-block, $K$, from Figure~\ref{fig:control-loop}.
-The goal of this system is to understand the user's surroundings and determine what the next best course of action is to reach the target location, based on what the system is currently seeing and what it has seen in the past.
+The goal of ActiVis is to understand the user's surroundings and determine what the next best course of action is to reach the target location, based on what the it is currently seeing and what it has seen in the past.
 We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action, $a$, our agent (the guidance system in this case) takes when it is in some state $s$.
@@
   \includegraphics[width=0.4\textwidth]{figures/control_loop.png}
-  \caption{MEME}\label{fig:control-loop}
+  \caption{The ActVis system layout and control loop. }\label{fig:control-loop}
 \end{figure}
@@
 
-Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the guidance system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}.
+Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the ActiVisguidance  system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}.
 Then we discuss the experiment and present its results in Section~\ref{sec:experiments}, after which we conclude the paper and discuss the project's next steps in Section~\ref{sec:conclusion}.
@@
   \centering
-  \caption{MEME}\label{tab:rewards}
+  \caption{A table containing the model rewards for our MDP. }\label{tab:rewards}
   \begin{tabular}{ll}
@@
   \end{subfigure}
-  \caption{MEME~\cite{openimages}}\label{fig:openimage-example}
+  \caption{Examples of images from the OpenImage dataset containing objects from $\mathit{O}$~\cite{openimages}}\label{fig:openimage-example}
 \end{figure}

### 2018-11-13 paper.tex
Refined text and plots after edit suggestions

@@
 \usepackage{booktabs}
+\usepackage[normalem]{ulem}
 
@@
 
-\noindent We are designing an indoor navigation system (ActiVis) targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment, expanding upon ideas originally proposed in~\cite{bellotto2013} and expanded on in~\cite{lock2017portable}.
-The proposed system implements ideas from the active vision field and places a human in the control loop.
-This control loop, pictured in Figure~\ref{fig:control-loop}, comprises of a controller, $K$, that is given a reference signal (the desired objects in this case) that generates a control signal, $u$, which a human, $H$, uses to manipulate a sensor, $P$, to gather more information on the environment and move closer to the target object.
-%The goal of this system is to automatically make sense of the user's surroundings and determine the optimal route to get to the final destination based on what the user/camera sees, thereby roughly emulating a normally sighted user's navigation strategy in an unknown environment.
+\noindent It is estimated that there are 440 million people worldwide that live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable sufferers to lead more normal and independent lives.
+Modern improvements to mobile computing and image processing techniques have provided researchers with new and exciting tools to solve this problem.
 
-In this paper we discuss the first steps we have taken into implementing the control-block, $K$, from Figure~\ref{fig:control-loop}.
-The goal of ActiVis is to understand the user's surroundings and determine what the next best course of action is to reach the target location, based on what the it is currently seeing and what it has seen in the past.
-We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action, $a$, our agent (the guidance system in this case) takes when it is in some state $s$.
+The ActiVis project will contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment with minimal user input.
+The proposed system implements ideas from the field of active vision, but places a human in the control loop, pictured in Figure~\ref{fig:control-loop} instead of a electro-mechanical servo.
+This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
+
+The goal of ActiVis is to understand the user's surroundings and determine what the next best course of action is to reach the target location based on what the it is currently seeing and what it has seen in the past.
+We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action our agent (the guidance system in this case) takes when it finds itself in any state.
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/control_loop.png}
+  \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
   \caption{The ActVis system layout and control loop. }\label{fig:control-loop}
@@
 
-This work's main contribution is the design of a guidance system and MDP that can drive a user to point a mobile device's camera towards a given point in space in and find a target object.
+This work's main contribution is the design of a guidance system and MDP (the control-block, $K$, pictured in Figure~\ref{fig:control-loop}) that can drive a user to point a mobile device's camera towards a given point in space in and find a target object.
 We also present and discuss preliminary experimental results to show how effective the system is at finding a target.
+This guidance system will be implemented into the ActiVis project upon successful tests.
 
-Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the ActiVisguidance  system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}.
+Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the ActiVis guidance system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}.
 Then we discuss the experiment and present its results in Section~\ref{sec:experiments}, after which we conclude the paper and discuss the project's next steps in Section~\ref{sec:conclusion}.
@@
 
-\section{\uppercase{Active Vision System Design}}\label{sec:system-design}
+\section{\uppercase{Active Vision System}}\label{sec:system-design}
 
-\noindent The ActiVis project's goal is to deliver a stand-alone system that is capable of accepting user input on a target object\textbackslash{}destination and guide a VI user to it.
-A complete system diagram is given is Figure~\ref{fig:control-loop} and consists of a number of elements, or blocks
+\noindent The ActiVis project's goal is to deliver a stand-alone system that only requires a VI user's input for selecting a target object\textbackslash{}destination and then guide the user to it.
+A complete system diagram is given is Figure~\ref{fig:control-loop} and consists of a number of elements.
 
-From Figure~\ref{fig:control-loop}, it can be seen that the system layout is similar to that of a classical control problem where a controller generates a control signal that drives a component towards some reference point.
-In this case, the reference signal, $r$, is the object the user wishes to find, which the system can achieve by placing that object within the camera's view.
-Therefore, the goal of the control block, $K$, is to generate guidance instructions, $u$, in the form of visual or audio instructions, to drive the along a search path.
-Since we are not working with a electro-mechanical system, we have an extra suer block, $H$, that interprets $u$ and executes a physical action, $u^*$, that manipulates the sensor, $P$, to point in another direction and make a new observation.
-The cycle is repeated if the target object is not observed.
+The system design loop is similar to that of a classical control problem where a controller generates a control signal that drives a component towards some reference point.
+In this case, the reference signal, $r$, is the object the user wishes to find which is achieved by placing the target object within the camera's view.
+Therefore, the goal of the control block, $K$, is to generate guidance instructions, $u$ to drive the user along a search path towards the target object.
+Since we place a human in the control loop and are not working with a electro-mechanical system, we have an extra block, $H$, that interprets $u$ and executes a physical action, $u^*$, that manipulates the sensor, $P$, that makes a new observation.
+The new observation is then fed back to the loop and the error signal, $e$, is updated accordingly.
 
@@
 Secondly, the controller must be robust enough to handle a badly interpreted $u$ signal.
-The risk of that happening can be minimised by generating clear and simple signals, ensuring $u^*$ closely tracks the original signal, $u$.
+The risk of that happening can be minimised by generating clear and simple signals to help ensure that $u^*$ closely tracks $u$.
 
@@
 
-\noindent The guidance system is built into an Android app with Android's ARCore~\footnote{https://developers.google.com/ar/} API enabled and is designed with the goal of generating a path of waypoints for the user to follow with a camera that will lead to the target object.
-This path is generated one waypoint at a time by the system and is updated with every object observation the user makes when adjusting the camera.
-We modelled this optimal path search problem as a grid-world problem that is solved by an Markov Decision Process (MDP) model.
-The details of the grid layout and the MDP model are discussed in the sections below.
+\noindent The guidance system is built into an Android app and uses Android's ARCore\footnote{https://developers.google.com/ar/} API to track the device's pose.
+The system is designed with the goal of generating a path of waypoints for the user to follow, by pointing the device camera, that will lead the user to the target object.
+This path is generated one waypoint at a time by the system and is updated with every object observation the user makes after adjusting the camera.
+We modelled and solved the search problem using an Markov Decision Process (MDP) model.
+The details of the MDP model design and implementation are discussed in the sections below.
 %For this initial design, the system only works in the pan and tilt dimension and the depth dimension will be added after successful testing of this version of the guidance system.
@@
 
-\noindent An MDP was used to produce a policy that defines a set of optimal actions for the agent to take in any given state.
-In this case, the agent is defined as the mobile phone and guidance system and the policy is used to generate the next waypoint on the search path towards the square on the grid that contains the target object.
-We initially assume perfect state and transition observability for each timestep.
-The problem is given by the 5-tuple
+\noindent An MDP is used to produce a policy that defines a set of optimal actions for an agent to take in any given pre-defined state.
+In this case, the agent is defined as the guidance system and the policy is used to generate the next waypoint on the search path towards the target object.
+We assume perfect state and transition observability for each timestep and the problem is given by the 5-tuple
 
 \begin{equation}
-  \langle{}\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \gamma\rangle, 
+  (\text{R}, \mathbf{S}, \mathbf{A}, \mathbf{T}, \gamma), 
 \end{equation}
-where $\mathbf{S}$ is a set of possible states the agent can be in, $\mathbf{A}$ is a set of possible actions an agent can take in any given state, $\mathbf{T}$, is a set of state transition probabilities defining the probability of transitioning from state $s$ to state $s'$.
-$\mathbf{R}$ is the reward function defining the immediate reward the agent receives reaching state $s'$ after executing action $a$ in state $s$, and $\gamma$ is a discount factor which maximises immediate over long-term rewards.
+where $\text{R}$ is the reward function defining the immediate reward the agent receives for reaching state $s'$ after executing action $a$ in state $s$, $\mathbf{S}$ is a set of possible states the agent can be in and $\mathbf{A}$ is a set of possible actions an agent can take in any given state.
+$\mathbf{T}$ is a set of state transition probabilities defining the probability of transitioning from state $s$ to state $s'$ after executing action $a$ and $\gamma$ is a discount factor which prioritises immediate over long-term rewards and is set to 0.95 to maximise long-term reward.
 Each of these elements are defined and discussed next.
@@
 
-\noindent The reward function, $r$, is the immediate reward that the agent receives after transitioning from state $s$ to state $s'$ and is given by
+\noindent The reward function, $R$, is the immediate reward that the agent receives after transitioning from state $s$ to state $s'$ and is given by
 
 \begin{equation}
-  r = \langle{}s, s'\rangle, r\in{}\mathbf{R}.
+  R = r(s, s').
 \end{equation}
 
-The reward function is a very important parameter for training the agent to produce the most effective policy.
+The goal of the agent is to maximise the cumulative reward it receives and is a very important parameter for producing a good policy that will define the optimal action for the agent to execute for any given state.
+In order to encourage the agent to actively search for the target object, a set of negative rewards must be defined, along with a relatively large positive reward for successfully reaching the target object.
+These parameters must be finely balanced to ensure efficient object search behaviour from the agent.
+
+%The reward function is a very important parameter for training the agent to produce the most effective policy.
 We define a constant negative reward for every step the agent takes, and increase this negative reward if the agent exceeds the 12-step limit we defined in the model, as well as if it regenerates a waypoint in a previously searched location.
-The values used here are given in Table~\ref{tab:rewards}.
+The values we used were empirically chosen and are given in Table~\ref{tab:rewards}.
 
-\begin{table}
-  \centering
-  \caption{A table containing the model rewards for our MDP. }\label{tab:rewards}
-  \begin{tabular}{ll}
-    \toprule
-    $s\in\mathbf{S}$ & -1.0  \\ \midrule
-    $s(n >= 9)$ & -10.0 \\ \midrule
-    $s(v = 1)$  & -10.0 \\ \midrule
-    $s(o = \text{target})$ & 10000 \\ \midrule
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The goal of the agent is to maximise its cumulative reward over time and these numbers are chosen such that they actively motivate the agent to reach the target, while hastening the process by slightly punishing it for each step it takes and increasing the punishment every time it re-explores a state and the longer it takes to reach the target.
+%The goal of the agent is to maximise its cumulative reward over time and these numbers are chosen such that they actively motivate the agent to reach the target, while hastening the process by slightly punishing it for each step it takes and increasing the punishment every time it re-explores a state and the longer it takes to reach the target.
 
@@
 
-\noindent The state is a combination of parameters that defines the agent's decision process. The agent's state vector is given by
+\noindent The state is a combination of parameters that defines the agent's world and decision process. The agent's state vector is given by
 
@@
 \end{equation}
-where $o$ is the current object, $n$ is the number of steps taken since the search started and $v$ is a binary variable that tracks whether a pan/tilt position has been generated as a waypoint before during the search.
-There are 8 objects encoded into the system, including a `nothing' instance where nothing of note is observed.
-Our initial implementation considers a simple office desk scenario containing the following objects:
-
-\begin{equation}
-  \begin{aligned}
-    o\in \mathbf{O} = \{monitor, mouse, keyboard, window,\\mug, stationary, desk, nothing\}.
-  \end{aligned}
-\end{equation}
-
-Our implementation is designed for a 6$\times$6 discretised, radial grid for convenience and replicability through different experiments.
-The grid spans \SI{180}{\degree} in the pan and tilt dimensions, giving a grid resolution of \SI{30}{\degree} per grid square.
-We set the model to track a maximum of of 9 steps to the target, with 9 being the longest possible route on the grid.
-A search can take longer than 9 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function.
-The MDP therefore has a total of 144 possible states ($8\times9\times2$).
+where $o$ is the current object in view, $n$ is the number of steps taken since the search started and $v$ is a binary variable that tracks whether a waypoint has been generated in the same pan/tilt position before during the search.
 
@@
 The policy produced by an MDP define the action an agent will take when it finds itself in any given state.
-In this case, the action is the direction the user should move towards in a grid-world context, i.e.\ the angular adjustment the user must make to the camera to move along the search path.
-This action is interpreted by the guidance system and a new waypoint is added to the search path toward the target object.
-The possible actions are defined by
+In this case, the action is the direction the next waypoint should be generated relative to the device's current view pose.
+The actions are defined by
 
@@
 \end{equation}
-and the possible actions are
+\uline{and the possible actions are}
 
@@
 \end{equation}
-These actions were chosen to conform to the grid implementation and increase the tracking performance of $u^*$ w.r.t\@ $u$.
+%These actions were chosen to conform to the grid implementation and increase the tracking performance of $u^*$ w.r.t\@ $u$.
 
@@
 
-\noindent The state transition function, $\mathbf{T}$, defines the likelihood of the agent transitioning into a state $s'$ from state $s$ when taking an action $a$, i.e.\ the likelihood of moving into a square and observing object $o$ after performing action $a$.
-It therefore represent the spatial relationships between the different objects in the environment model.
+\noindent The state transition function, $\mathbf{T}$, defines the likelihood of the agent transitioning into a state $s'$ from state $s$ when taking an action $a$, i.e.\ the likelihood of moving to a new pan/tilt position and observing object $o$ after performing action $a$.
+Therefore, it represent the spatial relationships between the different objects in the environment model.
 Formally, the transition function is defined by
@@
 
-The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset\footnote{https://storage.googleapis.com/openimages/web/index.html}~\cite{openimages}.
-This dataset consists of 1.74M images containing 14.6M labelled bounding boxes manually drawn around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to test their models on.
-However, using the bounding boxes and object labels we can extract the spatial relationships between the different objects in $\mathbf{O}$.
-Since the camera perspectives and absolute distances between the objects in the images are not given, we can only extract the relationships in terms of the actions specified in $\mathbf{A}$, e.g.\ we can only say that object 1 is above object 2, but not how far above.
-Our simple action-space and grid environment somewhat compensates for this lack of complexity in the dataset.
+The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset\footnote{https://storage.googleapis.com/openimages/web/index.html}~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to test their models on.
+Using the bounding boxes and object labels, we can extract the spatial relationships between the different objects in $\mathbf{O}$.
+Since the camera perspectives and absolute distances between the objects in the images are not given, we can only extract the relationships in the basic action terms specified in $\mathbf{A}$, e.g.\ we can only say that object 1 is above object 2, but not how far above.
+Our simple action-space and grid environment somewhat compensates for the dataset's lack of complexity.
 
@@
   \end{subfigure}
-  \caption{Examples of images from the OpenImage dataset containing objects from $\mathit{O}$~\cite{openimages}}\label{fig:openimage-example}
+  \caption{Examples of images from the OpenImage dataset containing objects from $\mathit{O}$~\cite{openimages}. }\label{fig:openimage-example}
 \end{figure}
+
+\subsection{MDP Implementation}
 
@@
 
-\noindent The output of an MDP is a so-called policy that defines the action an agent will take when it is in any given state.
-A policy is generated by having an agent explore the entire state-space and through many iterations improve its decision function, i.e.\ policy, in order to reach the target state in a way that maximises its cumulative reward.
+\noindent A policy that defines the optimal action for an agent to take for any given state is generated through a training process that involves letting the agent explore the entire state-space and iteratively improve its decision function, i.e.\ policy, in order to reach the target state in a way that maximises its cumulative reward.
 This method is called Q-learning and does not require a model of its environment during training.
 
-The agent's target state is any state combination where $o$ is the target object, since we are primarily concerned with finding the target object.
-Each target object has its own unique policy file and there are 18 terminal state in total (9$\times$2) per policy.
+For our system, the agent's target state is any state where $s = \langle{}o_{target}, n, v\rangle$.
+Each target object has its own unique policy file and there are 18 terminal states in total (9$\times$2) per policy, since the target object can can be found at any point in the search or in a position that was previously explored by the agent and user.
+
+The reward function was crafted by hand and the parameters were empirically selected.
+The function values can be found in Table~\ref{tab:rewards}.
+$R$ punishes the agent for every step it takes where it does not find the target object, and the negative reward is increased if the agent is taking too long to find the target ($n > n_{max}$) or when it wants to search in a site that has been searched already ($v = true$).
+Conversely, it gives a significant positive reward when the target object is found.
+
+\begin{table}
+  \centering
+  \caption{A table containing the model rewards for our MDP.\ }\label{tab:rewards}
+  \begin{tabular}{ll}
+    \toprule
+    $r(s, s'), s\in\mathbf{S}$ & -1.0  \\ \midrule
+    $r(n >= n_{max})$ & -10.0 \\ \midrule
+    $r(v = true)$  & -10.0 \\ \midrule
+    $r(o = o_{target})$ & 10000 \\ \midrule
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+Currently there are 8 objects encoded into the system, including a `nothing' instance where nothing of note is observed.
+Our initial implementation considers a simple office desk scenario containing the following objects:
+
+\begin{equation}
+  \begin{aligned}
+    o\in \mathbf{O} = \{monitor, mouse, keyboard, window,\\mug, stationary, desk, nothing\}.
+  \end{aligned}
+\end{equation}
+
+\uline{We set the model to track a maximum of of 9 steps to the target, with 9 being the longest possible route on the grid (more details about the grid are in Section~\ref{sec:system-implementation}).
+A search can take longer than 9 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function.
+The MDP therefore has a total of 144 reachable states ($8\times9\times2$).}
 
@@
 
-\section{\uppercase{Experiments}}\label{sec:experiments}
+\subsubsection{Android Implementation}\label{sec:system-implementation}
 
-\noindent To test the effectiveness of the policy the MDP produced, we designed a set of experiments that determined how effective the system is at directing a participant to pointing towards a target object.
-This section discusses all of the simulations and experiments that were carried out.
-
-\subsection{Experiment Design}
-
-\noindent To test the viability and effectiveness of our system, we carried out a set of experiments.
-For this, the MDP policies were integrated into an Android application that uses the camera to provide observation data and track the pose and viewing direction.
-We avoided adding unnecessary variability and complexity to the experiment by providing visual waypoints on screen which the participants were allowed to use.
-In addition to this, encoded QR codes and the Android barcode scanner library were used to simulate object detection.
-A generic environment mimicking a typical office desk layout was set up as the experiment environment and contains 7 different objects (i.e.\ encoded QR codes), one of which were the target object.
-See Figure~\ref{fig:env-picture} for a picture of the environment.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.4\textwidth]{figures/test_env_picture.jpg}
-  \caption{A picture of the environment used for the experiments. Each QR code represents an object. }\label{fig:env-picture}
-\end{figure}
+We incorporated the trained MDP model and policies into an Android app (see Figure~\ref{fig:system-screenshot} for a screenshot).
+This app is responsible for generating the guidance instructions and tracking the agent and sensor ($K$ and $P$ blocks in Figure~\ref{fig:control-loop}) throughout a search session.
+Tracking the agent's pose allows the app to infer the current state and look up the optimal action to take.
 
@@
 
+The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes.
+In this setup, the policy action is interpreted by the app and a new search waypoint is generated in the centre of the cell specified by the action, e.g.\ an `$UP$' action will generate a waypoint one grid cell up from where the suer is currently pointing the camera.
+The app's guidance system then uses the new waypoint's location to provide the user with guidance instructions.
+The grid is generated at the app's start-up and is tracked in absolute terms.
+However, the policy actions, and waypoints by extension, are given in relative terms (relative to the user's current viewing pan/tilt position).
+The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.
+
+By recording the previous positions and waypoint locations the app generated, it can infer the state values for $v$ and $n$.
+Furthermore, the camera provides the ID of the object in view, populating $o$ in the state.
+A real-time object detector was not used in this system to avoid unnecessary complexity and processing overhead and encoded QR codes and barcode scanner library were used to simulate object detection instead.
+
+\section{\uppercase{Experiments}}\label{sec:experiments}
+
+\noindent To test the effectiveness of our MDP and its policies, we designed a set of experiments that determined how effective the system is at directing a participant to point the device's camera towards a target object.
+This section discusses the experiments and their results.
+
+\subsection{Experiment Design}
+
+\noindent For the experiment, the MDP policies were integrated into an Android application that uses the camera to provide observation data and track the pose and viewing direction.
+We avoided adding unnecessary variability and complexity to the experiment by providing visual waypoints on screen which the participants were allowed to use.
+A generic environment mimicking a typical office desk layout was set up as the experiment environment and contains 7 different objects (i.e.\ encoded QR codes), one of which could be selected for each experiment run.
+See Figure~\ref{fig:env-picture} for a picture of the environment.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/test_env_picture.jpg}
+  \caption{A picture of the environment used for the experiments. Each QR code represents an object. OVERLAY GRID AND PRESENT EXAMPLE SEARCH}\label{fig:env-picture}
+\end{figure}
+
 For each experiment, the participant was placed roughly \SI{1}{\meter} from the barcodes and was asked not to move from that spot during the experiment.
@@
 
-During in-house tests, we noted that the system sometimes makes guidance mistakes that lead the user towards the edge of the search space, at which point the system had difficulty guiding the user back to the centre.
+During in-house tests, we noted that the system sometimes makes guidance mistakes that lead the user towards an uncluttered edge of the search space, at which point the system had difficulty guiding the user back to the centre.
 To avoid this having an adverse impact and drawing out the experiments too long, we set a search step limit of 16, which means that only 16 waypoints were be generated before the search was terminated.
@@
 We present and discuss the results for each of these parameters in the next sections.
-All of the results are summarised in Table~\ref{tab:results-summary}.
+The results for each individual participant is presented in Table~\ref{tab:results-full} and Table~\ref{tab:results-summary} gives the results across all of the participants.
 
@@
   \centering
-  \caption{A table containing a summary of the TAR, steps and time to target means ($\mu$) and standard deviations ($\sigma$) for each individual participant and the entire participant population.}\label{tab:results-summary}
+  \caption{A table containing the results for the TAR, number of steps and time to target means ($\mu$) and standard deviations ($\sigma$) for each individual participant.}\label{tab:results-full}
   \begin{tabular}{cc|cc|cc}
@@
 				 &			     & $\mu$ & $\sigma$		       & $\mu$ & $\sigma$  \\ \midrule
-    s1 & 6.3 & 7.2 & 5.4 & 29 & 22 \\ \midrule
-    s2 & 21 & 6.7 & 4.8 & 34 & 5.1 \\ \midrule
-    s3 & 8.8 & 6.3 & 4.9 & 31 & 21 \\ \midrule
-    s4 & 21 & 6.7 & 4.3 & 37 & 5.6 \\ \midrule
-    s5 & 24 & 7.2 & 4.9 & 33 & 14 \\ \midrule
-    s6 & 40 & 8.2 & 5.4 & 24 & 10 \\ \midrule
-    s7 & 14 & 8.5 & 5.8 & 31 & 16 \\ \midrule
-    s8 & 12 & 5.1 & 4.0 & 39 & 21 \\ \midrule
-    s9 & 2.5 & 7.2 & 5.4 & 39 & 18 \\ \midrule
-    s10 & 33 & 6.6 & 5.4 & 26 & 12 \\ \midrule\midrule
-    Population & $\mu$: 18 $\sigma$: 11 & 6.8 & 5.1 & 34 & 23 \\
+    s1 & 94 & 7.2 & 5.4 & 29 & 22 \\ \midrule
+    s2 & 79 & 6.7 & 4.8 & 34 & 5.1 \\ \midrule
+    s3 & 91 & 6.3 & 4.9 & 31 & 21 \\ \midrule
+    s4 & 79 & 6.7 & 4.3 & 37 & 5.6 \\ \midrule
+    s5 & 76 & 7.2 & 4.9 & 33 & 14 \\ \midrule
+    s6 & 60 & 8.2 & 5.4 & 24 & 10 \\ \midrule
+    s7 & 86 & 8.5 & 5.8 & 31 & 16 \\ \midrule
+    s8 & 88 & 5.1 & 4.0 & 39 & 21 \\ \midrule
+    s9 & 98 & 7.2 & 5.4 & 39 & 18 \\ \midrule
+    s10 & 67 & 6.6 & 5.4 & 26 & 12 \\ \midrule\midrule
+    % Population & $\mu$: 82 $\sigma$: 11 & 6.8 & 5.1 & 34 & 23 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}
+  \centering
+  \caption{A table summarising the means ($\mu$) and standard deviations ($\sigma$) for the entire participant population.}\label{tab:results-summary}
+  \begin{tabular}{lcc}
+    \toprule
+    & $\mu$ & $\sigma$ \\ \midrule
+    TAR [\%]   & 82  & 11  \\ \midrule
+    Num. Steps & 6.8 & 5.1 \\ \midrule
+    Time [s]   & 34  & 23  \\ \midrule
     \bottomrule
@@
 
-\noindent The target acquisition rate (TAR) is a measure of how successful the system was at directing a participant to the target object within the 16-step limit we imposed and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches.
-See Figure~\ref{fig:incomplete-searches-subjects} for a plot showing the TAR for each participant.
+\noindent The TAR is a measure of how successful the system was at directing a participant to the target object within the 16-step limit we imposed and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches.
+See Figure~\ref{fig:complete-searches-subjects} for a plot showing the cumulative TAR for all the participants.
 Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/incomplete_searches_subjects.png}
-  \caption{A plot giving the proportion of searches that reached the 16-step limit we imposed for each participant. }\label{fig:incomplete-searches-subjects}
+  \includegraphics[width=0.5\textwidth]{figures/cdf_tar.png}
+  \caption{A plot giving the cumulative proportion of searches that successfully found the target object before reaching the 16-step limit. }\label{fig:complete-searches-subjects}
 \end{figure}
 
-The inter-participant spread ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance  With an average TAR of $18.3\%$, it is clear that our system can be improved with regards to entering a no-recovery state where it directs a user into dead-space with no spatial information (e.g.\ a ceiling or wall section) and cannot gather the information it requires to intelligently guide the user.
+Figure~\ref{fig:complete-searches-subjects} shows a fairly consistent spread for the TAR across the participants.
+The inter-participant spread ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance, but with an average TAR of $81.2\%$, it is clear that the system successfully finds the target object during the vast majority of searches.
+
+The TAR can be improved with regards to entering a no-recovery state where it directs a user into dead-space with no spatial information (e.g.\ a ceiling or wall section) and cannot gather the information it requires to intelligently guide the user.
 Subsequent system updates will have to consider implementing fall-back methods or other automatic recovery modes that can detect entry of a no-recovery state (e.g.\ exceeding a set number of steps/time without making an observation) and guide the user back to the initial position.
@@
 
-\noindent The number of steps to target indicates the number of waypoints the system generated for the participant during the guidance process is a major indication of system performance, where less waypoints means better performance.
-Figure~\ref{fig:nsteps-participants} shows the distributions of the number of steps to the target for each individual participant.
+\noindent The number of steps target indicates the number of waypoints the system generated for the participant during the guidance process and is a major indication of system performance, where less waypoints means faster target acquisition and better performance.
+Figure~\ref{fig:nsteps-participants} shows the cumulative distribution of the number of steps to the target for all the participants.
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/boxplot_nsteps_subjects.png}
-  \caption{The distributions of each participant's number of steps taken to find a target object. }\label{fig:nsteps-participants}
+  \includegraphics[width=0.5\textwidth]{figures/cdf_total_steps.png}
+  \caption{The cumulative distribution of the participants' number of steps taken to find a target object. }\label{fig:nsteps-participants}
 \end{figure}
 
-The number of waypoints each participant required is fairly consistent across all of the participants with a inter-participant standard deviation of 1 waypoint.
+The number of waypoints each participant required is fairly evenly spread across all of the participants.
 The population mean and standard deviation is 6.8 and 5.1 waypoints respectively.
 This is a reasonable result that was also somewhat expected, since most target objects were placed within approximately 4 grid squares away from the participants' initial looking directions.
+However, the relatively high standard deviation should be noted and can also be reduced by implementing the automatic recovery mode mentioned previously, and avoiding information-sparse areas.
 
-It is interesting to note that participants $s6$ and $s10$ also found their targets within these reasonable bounds when accounted for the targets that they found within the 16-step limit.
+% It is interesting to note that participants $s6$ and $s10$ also found their targets within these reasonable bounds when accounted for the targets that they found within the 16-step limit.
 This supports the argument from the previous results that their decreased TAR was partly caused by an abnormally high number of entries into a no-recovery state and further reinforces the need to implement an automatic recovery feature in the system before deployment.
@@
 
-\noindent The total time it took a participant to reach the target object is given in Figure~\ref{fig:time-participants}.
-In it we see that the inter-participant variance in the temporal response, with mean 29.8s and standard deviation 6.2s (population standard deviation of 23s), is far greater than for the number of waypoints they required.
+\noindent The distribution of the total time it took the participants to reach the target object is given in Figure~\ref{fig:time-participants}.
+We see that the distribution is heavily skewed to the bottom with a long tail.
+The mean and standard deviation of the data is 29.8s and 23s respectively.
+%, is far greater than for the number of waypoints they required.
 Indeed, there is not a strong relationship between the number of waypoints a participant required and the time they took to find the target, as showcased by participant $s7$'s wide mean waypoint count and spread in Figure~\ref{fig:nsteps-participants} and the small spread and close-to-average time to target in Figure~\ref{fig:time-participants}.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/boxplot_time_to_target_subjects.png}
-  \caption{The distributions of the each participant's time taken to find a target object. }\label{fig:time-participants}
+  \includegraphics[width=0.5\textwidth]{figures/cdf_total_time.png}
+  \caption{The cumulative distribution of the participants' time taken to find a target object. }\label{fig:time-participants}
 \end{figure}
 
-In comparison to the VizWiz system~\cite{bigham2010vizwiz} (mean 92s, standard deviation 37.7s), our results look fairly reasonable.
-However, our results may look very different when we test the system with VI participants like they did in~\cite{bigham2010vizwiz}.
+In comparison to the VizWiz system~\cite{bigham2010vizwiz} (mean 92s, standard deviation 37.7s), our results look very reasonable.
+However, these results may greatly change when we test the system with VI participants like they did in~\cite{bigham2010vizwiz}.
 
@@
 \noindent In this work we presented and tested an MDP-based system to guide a visually impaired (VI) person towards a target object with no apriori knowledge of the environment.
-We implemented the system in an Android app that we tested with a small group of sighted people to determine its viability and effectiveness at guiding user at finding and pointing a camera at a specific target.
-We found that is works fairly well when compared to alternative systems, with a respectable mean time of target acquisition of 32s.
+We implemented the system in an Android app that we tested with a small group of sighted people to determine its viability and effectiveness at guiding a user to manipulating a camera and finding a target object.
+We found that is works well when compared to alternative systems, with a respectable mean time of target acquisition of 32s.
 However, the system can be improved by refining the search strategy and implementing an automatic fail-state recovery system that will guide a user back to neutral position if a fail-state is entered (e.g.\ a blank section of wall).
@@
 The model can also be expanded to include more objects and actions.
-However, an important consideration and expansion to the problem is to change the MDP to an Partially Observable MDP (POMDP) that will bring the model more in line with reality by acknowledging that the objects are not perfectly observable and humans do not perfectly follow guidance instructions.
-This adjustment may be very important when we consider that we will replace the QR code detector with object recognition models that are typically more prone to making classification errors.
-Finally, the model can be adapted to use on-line learning techniques in order to further refine its transition model as the user uses the guidance system.
+However, an important consideration and expansion to the problem is to change the MDP to an Partially Observable MDP (POMDP) model that will bring the model more in line with reality by acknowledging that the objects are not perfectly observable and humans do not perfectly follow guidance instructions.
+This adjustment may be very important when we replace the QR code scanner with an object recognition that are typically more prone to making classification errors.
+Finally, the model can be adapted to use on-line learning techniques in order to further refine its transition model as the guidance system is used.
 

### 2018-11-13 paper.tex
Refined text and plots after edit suggestions

@@
 
-\title{Designing an Active Vision Indoor Object Search Guidance System}
+\title{Designing an Agent for an Active Guidance System for Object Search}
 
@@
 
-\abstract{In this work, we propose an active vision system that uses a Markov Decision Process and mobile phone to enable a user to find an object in an unknown environment.
-An initial implementation of this system was implemented and tested with a set of experiments were carried out with sighted participants to determine the effectiveness of the system.
+\abstract{In this work, we propose a Markov Decision Process-based system that generates guidance instructions for a user to find a target object in an unknown environment and forms part of an active vision indoor guidance system for the visually impaired.
+An initial implementation of this system was implemented in an Android app and a set of experiments were carried out with sighted participants to determine its effectiveness.
 We found that the system works reasonably well and compares well to similar systems.
@@
 \end{equation}
-\uline{and the possible actions are}
+and the possible actions are
 
@@
 
-\uline{We set the model to track a maximum of of 9 steps to the target, with 9 being the longest possible route on the grid (more details about the grid are in Section~\ref{sec:system-implementation}).
+We set the model to track a maximum of of 9 steps to the target, with 9 being the longest possible route on the grid (more details about the grid are in Section~\ref{sec:system-implementation}).
 A search can take longer than 9 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function.
-The MDP therefore has a total of 144 reachable states ($8\times9\times2$).}
+The MDP therefore has a total of 144 reachable states ($8\times9\times2$).
 
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{figures/system_screenshot.png}
+  \includegraphics[width=0.45\textwidth]{figures/system_screenshot2.png}
   \caption{A screenshot of the guidance interface showing a waypoint (based on an 3D Android model), the object scanner area and the guidance instruction arrows. }\label{fig:system-screenshot}
@@
   \includegraphics[width=0.4\textwidth]{figures/test_env_picture.jpg}
-  \caption{A picture of the environment used for the experiments. Each QR code represents an object. OVERLAY GRID AND PRESENT EXAMPLE SEARCH}\label{fig:env-picture}
+  \caption{A picture of the environment used for the experiments. Each QR code represents an object.}\label{fig:env-picture}
 \end{figure}

### 2018-11-20 paper.tex
New figures, edits

@@
 \usepackage{siunitx}
+\usepackage{multirow}
 %\usepackage{tikz}
@@
 
-This work's main contribution is the design of a guidance system and MDP (the control-block, $K$, pictured in Figure~\ref{fig:control-loop}) that can drive a user to point a mobile device's camera towards a given point in space in and find a target object.
+This work's contributions are
+
+\begin{itemize}
+  \item a policy-driven human controller that can drive a user towards a point in space,
+  \item an MDP model that understands the spatial relationship between objects that is based on real data and
+  \item experiments that prove the effectiveness of the current system implementation.
+\end{itemize}
+
+%is the design of a guidance system and MDP (the control-block, $K$, pictured in Figure~\ref{fig:control-loop}) that can drive a user to point a mobile device's camera towards a given point in space in and find a target object.
 We also present and discuss preliminary experimental results to show how effective the system is at finding a target.
@@
 \begin{equation}
-  (\text{R}, \mathbf{S}, \mathbf{A}, \mathbf{T}, \gamma), 
+  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \text{R}, \gamma), 
 \end{equation}
 where $\text{R}$ is the reward function defining the immediate reward the agent receives for reaching state $s'$ after executing action $a$ in state $s$, $\mathbf{S}$ is a set of possible states the agent can be in and $\mathbf{A}$ is a set of possible actions an agent can take in any given state.
-$\mathbf{T}$ is a set of state transition probabilities defining the probability of transitioning from state $s$ to state $s'$ after executing action $a$ and $\gamma$ is a discount factor which prioritises immediate over long-term rewards and is set to 0.95 to maximise long-term reward.
+$\mathbf{T}$ is a set of state transition probabilities defining the probability of transitioning from state $s$ to state $s'$ after executing action $a$ and $\gamma$ is a discount factor which prioritises immediate over long-term rewards.
 Each of these elements are defined and discussed next.
-
-\subsubsection{Reward Function}
-
-\noindent The reward function, $R$, is the immediate reward that the agent receives after transitioning from state $s$ to state $s'$ and is given by
-
-\begin{equation}
-  R = r(s, s').
-\end{equation}
-
-The goal of the agent is to maximise the cumulative reward it receives and is a very important parameter for producing a good policy that will define the optimal action for the agent to execute for any given state.
-In order to encourage the agent to actively search for the target object, a set of negative rewards must be defined, along with a relatively large positive reward for successfully reaching the target object.
-These parameters must be finely balanced to ensure efficient object search behaviour from the agent.
-
-%The reward function is a very important parameter for training the agent to produce the most effective policy.
-We define a constant negative reward for every step the agent takes, and increase this negative reward if the agent exceeds the 12-step limit we defined in the model, as well as if it regenerates a waypoint in a previously searched location.
-The values we used were empirically chosen and are given in Table~\ref{tab:rewards}.
-
-%The goal of the agent is to maximise its cumulative reward over time and these numbers are chosen such that they actively motivate the agent to reach the target, while hastening the process by slightly punishing it for each step it takes and increasing the punishment every time it re-explores a state and the longer it takes to reach the target.
 
@@
 
+Consider the scene in Figure~\ref{fig:route-example} which contains a number of simple, distinct objects (the red boxes).
+The MDP's task is to direct the user to point the camera to the target object (the mug in the bottom-left of Figure~\ref{fig:route-example}).
+It does this by inferring the current state by sampling the object currently within the camera's view, and generates an action that leads the user to the target object.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{figures/office_desk_example.png}
+  \caption{An example of a guidance strategy the MDP will generate. }\label{fig:route-example}
+\end{figure}
+
+The states are sampled and the actions are generated in discretised steps as the user moves the camera's view in the instructed direction.
+This discrete behaviour is similar to a waypoint navigation approach where the user goes from one waypoint to the next, until the user points the camera to target object.
+
 \subsubsection{State Transition Probabilities}
 
-\noindent The state transition function, $\mathbf{T}$, defines the likelihood of the agent transitioning into a state $s'$ from state $s$ when taking an action $a$, i.e.\ the likelihood of moving to a new pan/tilt position and observing object $o$ after performing action $a$.
-Therefore, it represent the spatial relationships between the different objects in the environment model.
+\noindent The state transition function, $\mathbf{T}$, defines the likelihood of the agent transitioning into state $s'$ from state $s$ when taking action $a$, i.e.\ the likelihood of moving to a new pan/tilt position and observing object $o$ after performing action $a$.
+Therefore, $\mathbf{T}$ represents the spatial relationships between the different objects in the environment model.
 Formally, the transition function is defined by
@@
 \begin{equation}
-  t\langle{}s, a, s'\rangle, t\in{}\mathbf{T}.
+  t=\langle{}s, a, s'\rangle, t\in{}\mathbf{T}.
+\end{equation}
+
+\subsubsection{Reward Function}
+
+\noindent The reward function, $R$, is the immediate reward that the agent receives after transitioning from state $s$ to state $s'$ and is given by
+
+\begin{equation}
+  R = r(s, s').
+\end{equation}
+
+The goal of the agent is to maximise the cumulative reward it receives and is a very important parameter for producing a good policy that will define the optimal action for the agent to execute for any given state.
+In order to encourage the agent to actively search for the target object, a set of negative rewards must be defined, along with a relatively large positive reward for successfully reaching the target object.
+These parameters must be finely balanced to ensure efficient object search behaviour from the agent.
+
+%The reward function is a very important parameter for training the agent to produce the most effective policy.
+We define a constant negative reward for every step the agent takes, and increase this negative reward if the agent exceeds the 12-step limit we defined in the model, as well as if it regenerates a waypoint in a previously searched location.
+The values we used were empirically chosen and are given in Table~\ref{tab:rewards}.
+
+%The goal of the agent is to maximise its cumulative reward over time and these numbers are chosen such that they actively motivate the agent to reach the target, while hastening the process by slightly punishing it for each step it takes and increasing the punishment every time it re-explores a state and the longer it takes to reach the target.
+
+\subsection{MDP Implementation}
+
+\subsubsection{Model Training}
+
+\noindent A policy that defines the optimal action for an agent to take for any given state is generated through a training process that involves letting the agent explore the entire state-space and iteratively improve its decision function, i.e.\ policy, in order to reach the target state in a way that maximises its cumulative reward.
+This method is called Q-learning and does not require a model of its environment during training.
+
+For our system, the agent's target state is any state where $s = \langle{}o=o_{target}, n, v\rangle$.
+This gives a total of 18 terminal states (9$\times$2) per policy, since the target object can can be found at any point in the search or in a position that was previously explored by the agent and user.
+Each target object has its own unique policy file.
+
+The reward function was crafted by hand and the parameters were empirically selected.
+The function values can be found in Table~\ref{tab:rewards}.
+$R$ punishes the agent for every step it takes where it does not find the target object and the negative reward is increased if the agent is taking too long to find the target ($n > n_{max}$) or when it wants to search in a site that has been searched already ($v = true$).
+Conversely, it gives a significant positive reward when the target object is found.
+
+\begin{table}
+  \centering
+  \caption{The reward functions for the MDP.\ }\label{tab:rewards}
+  \begin{tabular}{ll}
+    \toprule
+    $r(s, s'), s\in\mathbf{S}$ & -1  \\ \midrule
+    $r(n >= n_{max})$ & -10 \\ \midrule
+    $r(v = true)$  & -10 \\ \midrule
+    $r(o = o_{target})$ & 10000 \\ \midrule
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+Currently there are 8 objects encoded into the system, including a `nothing' instance where nothing of note is observed.
+Our initial implementation considers a simple office desk scenario containing the following objects:
+
+\begin{equation}
+  \begin{aligned}
+    o\in \mathbf{O} = \{monitor, mouse, keyboard, window,\\mug, stationary, desk, nothing\}.
+  \end{aligned}
 \end{equation}
@@
 The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset\footnote{https://storage.googleapis.com/openimages/web/index.html}~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to test their models on.
-Using the bounding boxes and object labels, we can extract the spatial relationships between the different objects in $\mathbf{O}$.
+The bounding boxes and object labels are used to extract the spatial relationships between the different objects in $\mathbf{O}$.
 Since the camera perspectives and absolute distances between the objects in the images are not given, we can only extract the relationships in the basic action terms specified in $\mathbf{A}$, e.g.\ we can only say that object 1 is above object 2, but not how far above.
@@
 
-\subsection{MDP Implementation}
+Figure~\ref{fig:obj-relationships} shows the spatial relationship between a subset of $\mathbf{O}$ (desk, keyboard and mouse).
+For example, when the agent is in state $s=\langle{}o=mouse, n, v\rangle$ and searching for a keyboard, there is a strong probability that the target object is $LEFT$ of the mouse.
+The MDP model considers all of the objects' spatial relationships when generating the optimal policy.
 
-\subsubsection{Model Training}
-
-\noindent A policy that defines the optimal action for an agent to take for any given state is generated through a training process that involves letting the agent explore the entire state-space and iteratively improve its decision function, i.e.\ policy, in order to reach the target state in a way that maximises its cumulative reward.
-This method is called Q-learning and does not require a model of its environment during training.
-
-For our system, the agent's target state is any state where $s = \langle{}o_{target}, n, v\rangle$.
-Each target object has its own unique policy file and there are 18 terminal states in total (9$\times$2) per policy, since the target object can can be found at any point in the search or in a position that was previously explored by the agent and user.
-
-The reward function was crafted by hand and the parameters were empirically selected.
-The function values can be found in Table~\ref{tab:rewards}.
-$R$ punishes the agent for every step it takes where it does not find the target object, and the negative reward is increased if the agent is taking too long to find the target ($n > n_{max}$) or when it wants to search in a site that has been searched already ($v = true$).
-Conversely, it gives a significant positive reward when the target object is found.
-
-\begin{table}
+\begin{figure}
   \centering
-  \caption{A table containing the model rewards for our MDP.\ }\label{tab:rewards}
-  \begin{tabular}{ll}
-    \toprule
-    $r(s, s'), s\in\mathbf{S}$ & -1.0  \\ \midrule
-    $r(n >= n_{max})$ & -10.0 \\ \midrule
-    $r(v = true)$  & -10.0 \\ \midrule
-    $r(o = o_{target})$ & 10000 \\ \midrule
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Currently there are 8 objects encoded into the system, including a `nothing' instance where nothing of note is observed.
-Our initial implementation considers a simple office desk scenario containing the following objects:
-
-\begin{equation}
-  \begin{aligned}
-    o\in \mathbf{O} = \{monitor, mouse, keyboard, window,\\mug, stationary, desk, nothing\}.
-  \end{aligned}
-\end{equation}
+  \includegraphics[width=0.5\textwidth]{figures/object_relationships.png}
+  \caption{Examples of the spatial relationships between the desk, keyboard and mouse objects.
+Each square corresponds to the probability of executing the action that square represent (top square for $UP$, etc.)}\label{fig:obj-relationships}
+\end{figure}
 
@@
 A search can take longer than 9 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function.
-The MDP therefore has a total of 144 reachable states ($8\times9\times2$).
+The MDP therefore has a total of 144 reachable states ($n_{states}=8\times9\times2$).
 
@@
 We therefore could not use the popular value iteration algorithm~\cite{bellman1957markovian} and opted for the state-action-reward-state-action (SARSA) algorithm~\cite{rummery1994line} instead.
-SARSA is an on-policy algorithm with the advantage of being more exploratory in nature and is therefore more likely to find a solution, but this solution is not guaranteed to be optimal.
+SARSA is an on-policy algorithm that allows us to control the level of exploration vs.\ exploitation that makes it easier to find a solution, but this solution is not guaranteed to be optimal.
+
+The model is trained until it converges to the optimal policy, or for a total of approximately 17 million episodes.
+The parameter, $\alpha$, that controls the exploration vs.\ exploitation behaviour during training maximises exploration when it is set to $1.0$ and exploitation when it is $0.0$.
+We set $\alpha$ to a function that starts at a high exploration value and exponentially changes it behaviour to exploitation as it becomes more trained.
+$\alpha$ is given by
+
+\begin{equation}
+  \alpha = \exp\Big(\frac{-i}{10n_{states}}\Big) - 0.001,
+\end{equation}
+where $i$ is the episode index.  $\gamma$ is set to 0.95 to prioritise long-term reward.
+
 Our MDP has a relatively small state-action space.
@@
 The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes.
-In this setup, the policy action is interpreted by the app and a new search waypoint is generated in the centre of the cell specified by the action, e.g.\ an `$UP$' action will generate a waypoint one grid cell up from where the suer is currently pointing the camera.
+In this setup, the policy action is interpreted by the app and a new search waypoint is generated in the centre of the cell specified by the action, e.g.\ an `$UP$' action will generate a waypoint one grid cell up from where the user is currently pointing the camera.
 The app's guidance system then uses the new waypoint's location to provide the user with guidance instructions.
-The grid is generated at the app's start-up and is tracked in absolute terms.
-However, the policy actions, and waypoints by extension, are given in relative terms (relative to the user's current viewing pan/tilt position).
+The grid is generated at the app's start-up and remains constant throughout the app's lifetime.
+The policy actions, and waypoints by extension, are given in relative to the user's current viewing pan/tilt position.
 The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.
@@
 A real-time object detector was not used in this system to avoid unnecessary complexity and processing overhead and encoded QR codes and barcode scanner library were used to simulate object detection instead.
+
+The QR code scanner requires raw image data.
+To avoid scanning multiple QR codes and using excess processing power by scanning large images, we only used the centre part of the screen to scan for a barcode.
+This scanner area is $300\times300$ pixels and scans for barcodes without causing any frame-rate drops.
+
+The app was developed on and experimented with an Asus ZenPhone AR\footnote{asus.com/uk/Phone/ZenFone-AR-ZS571KL/} running Android version 7.0 with the ARCore SDK enabled.
+No hardware or software modifications were required.
 
@@
 During in-house tests, we noted that the system sometimes makes guidance mistakes that lead the user towards an uncluttered edge of the search space, at which point the system had difficulty guiding the user back to the centre.
-To avoid this having an adverse impact and drawing out the experiments too long, we set a search step limit of 16, which means that only 16 waypoints were be generated before the search was terminated.
+To avoid this having an adverse impact and drawing out the experiments too long, we set a search step limit of 15, which means that the search was terminated when the number of waypoints exceeded 15.
 A search run therefore ended when the participant either successfully found the target object by pointing the phone camera to it and scanning the barcode, or exceeded the waypoint limit.
@@
 The results for each individual participant is presented in Table~\ref{tab:results-full} and Table~\ref{tab:results-summary} gives the results across all of the participants.
+
+To provide a baseline measure for the ideal case, we ran a number of simulations in an environment mimicking the experiment setup with an agent that perfectly executes the policy, i.e.\ $u=u^*$.
+The TAR and steps to target results for the simulation are included in Table~\ref{tab:results-summary}.
 
@@
     s10 & 67 & 6.6 & 5.4 & 26 & 12 \\ \midrule\midrule
-    % Population & $\mu$: 82 $\sigma$: 11 & 6.8 & 5.1 & 34 & 23 \\
     \bottomrule
@@
   \centering
-  \caption{A table summarising the means ($\mu$) and standard deviations ($\sigma$) for the entire participant population.}\label{tab:results-summary}
-  \begin{tabular}{lcc}
+  \caption{A table summarising the means ($\mu$) and standard deviations ($\sigma$) for the entire participant population for the experiment and simulation.}\label{tab:results-summary}
+  \begin{tabular}{llc}
     \toprule
-    & $\mu$ & $\sigma$ \\ \midrule
-    TAR [\%]   & 82  & 11  \\ \midrule
-    Num. Steps & 6.8 & 5.1 \\ \midrule
-    Time [s]   & 34  & 23  \\ \midrule
+    \multirow{2}{*}{TAR [\%]} & Experiment & 82 $\pm$ 11  \\ 
+			      & Simulation & 99.7 \\ \midrule
+    \multirow{2}{*}{Num. Steps} & Experiment & 6.8 $\pm$ 5.1 \\ 
+			        & Simulation & 5.4 \\ \midrule
+    Time [s] & Experiment & 34 $\pm$ 23  \\ \midrule
     \bottomrule
@@
 
-\subsection{Target Acquisition Rate}
+\subsubsection{Target Acquisition Rate}
 
 \noindent The TAR is a measure of how successful the system was at directing a participant to the target object within the 16-step limit we imposed and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches.
-See Figure~\ref{fig:complete-searches-subjects} for a plot showing the cumulative TAR for all the participants.
 Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present.
+
+\uline{From Figure~\ref{fig:tar-steps} we can see that the TAR has a gradual increase as we vary the step limit.
+This appears to justify our choice of a 15-waypoint cut-off.
+However, the spiking tail should be considered.
+}
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/cdf_tar.png}
-  \caption{A plot giving the cumulative proportion of searches that successfully found the target object before reaching the 16-step limit. }\label{fig:complete-searches-subjects}
+  \includegraphics[width=0.5\textwidth]{figures/cdf_tar_limit.png}
+  \caption{The distribution of the TAR as a function of the step limit for a search. }\label{fig:tar-steps}
 \end{figure}
 
-Figure~\ref{fig:complete-searches-subjects} shows a fairly consistent spread for the TAR across the participants.
+%\begin{figure}
+  %\centering
+  %\includegraphics[width=0.5\textwidth]{figures/cdf_tar.png}
+  %\caption{A plot giving the cumulative proportion of searches that successfully found the target object before reaching the 16-step limit. }\label{fig:complete-searches-subjects}
+%\end{figure}
+
+Table~\ref{tab:results-full} shows a fairly consistent spread for the TAR across the participants.
 The inter-participant spread ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance, but with an average TAR of $81.2\%$, it is clear that the system successfully finds the target object during the vast majority of searches.
+
+Figure~\ref{fig:tar-objects} shows the TAR for each object in $\mathbf{O}$.
+From it, we can see that there are variations the TAR for the different objects, with the smaller objects typically being the hardest to find.
+However, the differences are not extreme and indicate that all the objects in $\mathbf{O}$ are roughly equally hard to find.
+This is also displayed in the simulation's TAR in Table~\ref{tab:results-summary}, which could not achieve 100\% because of the difficulty the agent had in finding the objects on the fringes of the environment.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{figures/tar_objects.png}
+  \caption{The TAR for each of the objects within the target object set. }\label{fig:tar-objects}
+\end{figure}
 
@@
 
-\subsection{Number of Steps to Target}
+\subsubsection{Number of Steps to Target}
 
@@
 
+As expected, the number of steps on the simulation required on average to find the target object is less than for the experiments.
+The full set of results for the simulation is given in Figure~\ref{fig:sim-vs-experiment} which plots the number of coincidences between the simulation and experiment results.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{figures/experiment_vs_simulation.png}
+  \caption{A summary of the experiment and simulation steps to target results. }\label{fig:sim-vs-experiment}
+\end{figure}
+
 % It is interesting to note that participants $s6$ and $s10$ also found their targets within these reasonable bounds when accounted for the targets that they found within the 16-step limit.
@@
 
-\subsection{Time to Target}
+\subsubsection{Time to Target}
 

### 2018-11-20 figures/grid-world.tex
Added new figures

\tikzset{cross/.style={cross out, draw=black, minimum size=2*(#1-\pgflinewidth), inner sep=0pt, outer sep=0pt},cross/.default={1pt}}
\begin{tikzpicture}%[background rectangle/.style={fill=yellow!20}, show background rectangle]

  \def\thet{135}
  \def\ph{45}
  \def\l{2.2cm}
  \coordinate (O) at (0,0);
  \coordinate (U) at (3.5,-0.5);

  \node[below] (user) at ($(U)+(0,-0.4)$) {User};
  \draw[fill=black] (U) circle (0.3cm);

  \node[above] (gridlabel) at (2.3, 7.2) {Grid-world};

  % Draw the grid world outlines
  \coordinate (s0) at (0,0);
  \coordinate (s1) at (5,1);
  \coordinate (s2) at (5,6);
  \coordinate (s3) at (0,5);
  \draw[name path=bot_curve] (s0) to[out=90, in=140] (s1);
  \draw (s1) -- (s2);
  \draw[name path=top_curve] (s2) to[out=140, in=90] (s3);
  \draw (s3) -- (s0);% node[above right] {(0, 0)};

  %Draw horizontal grid lines 
  \draw[dashed] ($(s0)+(0,1)$) to[out=90, in=140] ($(s1)+(0,1)$);
  \draw[dashed] ($(s0)+(0,2)$) to[out=90, in=140] ($(s1)+(0,2)$);
  \draw[dashed] ($(s0)+(0,3)$) to[out=90, in=140] ($(s1)+(0,3)$);
  \draw[dashed] ($(s0)+(0,4)$) to[out=90, in=140] ($(s1)+(0,4)$);
  \draw[dashed] ($(s0)+(0,5)$) to[out=90, in=140] ($(s1)+(0,5)$);

  % Draw vertical grid lines
  \coordinate (v1) at ($(s0)!0.166!(s1)$);
  \coordinate (v2) at ($(s0)!0.33!(s1)$);
  \coordinate (v3) at ($(s0)!0.5!(s1)$);
  \coordinate (v4) at ($(s0)!0.66!(s1)$);
  \coordinate (v5) at ($(s0)!0.83!(s1)$);

  \draw[draw=none,name path=vert1] (v1) -- ($(v1)+(0,7)$);
  \draw[draw=none,name path=vert2] (v2) -- ($(v2)+(0,7)$);
  \draw[draw=none,name path=vert3] (v3) -- ($(v3)+(0,7)$);
  \draw[draw=none,name path=vert4] (v4) -- ($(v4)+(0,7)$);
  \draw[draw=none,name path=vert5] (v5) -- ($(v5)+(0,7)$);
  \coordinate[name intersections={of=bot_curve and vert1,by={int11}}];
  \coordinate[name intersections={of=top_curve and vert1,by={int12}}];
  \coordinate[name intersections={of=bot_curve and vert2,by={int21}}];
  \coordinate[name intersections={of=top_curve and vert2,by={int22}}];
  \coordinate[name intersections={of=bot_curve and vert3,by={int31}}];
  \coordinate[name intersections={of=top_curve and vert3,by={int32}}];
  \coordinate[name intersections={of=bot_curve and vert4,by={int41}}];
  \coordinate[name intersections={of=top_curve and vert4,by={int42}}];
  \coordinate[name intersections={of=bot_curve and vert5,by={int51}}];
  \coordinate[name intersections={of=top_curve and vert5,by={int52}}];
  \draw[dashed] (int11) -- (int12);
  \draw[dashed] (int21) -- (int22);
  \draw[dashed] (int31) -- (int32);
  \draw[dashed] (int41) -- (int42);
  \draw[dashed] (int51) -- (int52);

  % Draw user node and viewing angles
  \coordinate (c) at ($(U)+({\l*cos(\thet)}, {\l*sin(\thet)})$);
  \coordinate (cpan) at ($(c)+({-tan(\ph)*cos(\ph)}, {-tan(\ph)*sin(\ph)})$);
  \coordinate (ctilt) at ($(c)+({tan(\ph)*sin(\ph)}, {tan(\ph)*cos(\ph)})$);

  \draw[-Latex,] (U) -- coordinate (carc) (c) node[below] {C};
  \draw[dashed,-Latex] (U) -- coordinate (cpanarc) (cpan);
  \draw[dashed,-Latex] (U) -- coordinate (ctiltarc) (ctilt);

  \draw[-Latex] (carc) to[out=190, in=80] (cpanarc) node[right, yshift=0.13cm] {$\phi$};
  \draw[-Latex] (carc) to[out=80, in=190] (ctiltarc) node[below left] {$\theta$} ;

  % Add objects
  \coordinate (obj1) at ($(v1)!0.5!(v2) + (0,1.8)$);
  \coordinate (obj2) at ($(v3)!0.5!(v4) + (0,3.7)$);
  \coordinate (obj3) at ($(v2)!0.5!(v3) + (0,4.8)$);

  \draw (obj1) node[cross=3pt,rotate=12] {};
  \draw (obj2) node[cross=3pt,rotate=-3] {};
  \draw (obj3) node[cross=3pt,rotate=4] {};

  \node[left] (objectlabel) at (-0.4,2) {Objects};

  \draw[->] (objectlabel) -- ($(obj1)+(-0.1,0)$);
  \draw[->] (objectlabel) -- ($(obj2)+(-0.1,-0.1)$);
  \draw[->] (objectlabel) -- ($(obj3)+(-0.1,-0.1)$);

\end{tikzpicture}

### 2018-11-20 figures/route_example.tex
Added new figures

\tikzset{cross/.style={cross out, draw=black, minimum size=2*(#1-\pgflinewidth), inner sep=0pt, outer sep=0pt},cross/.default={1pt}}
\begin{tikzpicture}%[background rectangle/.style={fill=yellow!20}, show background rectangle]

  \coordinate (s0) at (0,0);
  \coordinate (s1) at (0,4);
  \coordinate (s2) at (4,4);
  \coordinate (s3) at (4,0);

  \draw (s0) -- (s1) -- (s2) -- (s3) -- cycle;

  \draw[dashed] ($(s0)!.25!(s1)$) -- ($(s2)!.75!(s3)$);
  \draw[dashed] ($(s0)!.5!(s1)$) -- ($(s2)!.5!(s3)$);
  \draw[dashed] ($(s0)!.75!(s1)$) -- ($(s2)!.25!(s3)$);

  \draw[dashed] ($(s0)!.25!(s3)$) -- ($(s1)!.25!(s2)$);
  \draw[dashed] ($(s0)!.5!(s3)$) -- ($(s1)!.5!(s2)$);
  \draw[dashed] ($(s0)!.75!(s3)$) -- ($(s1)!.75!(s2)$);

  \draw ($(s0)!0.125!(s1)+(s0)!0.125!(s3)$) node[cross=3pt,rotate=0] {};
  \node[circle,draw=black] () at ($(s0)!0.875!(s1)+(s0)!0.625!(s3)$) {};

\end{tikzpicture}

### 2018-11-21 paper.tex
Edits, updated simulation figure. Added new relevant work. Can perhaps compare system to these results

@@
 
-\noindent It is estimated that there are 440 million people worldwide that live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable sufferers to lead more normal and independent lives.
-Modern improvements to mobile computing and image processing techniques have provided researchers with new and exciting tools to solve this problem.
+\noindent It is estimated that there are 440 million people worldwide that live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives.
+Modern improvements to mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem.
+The ActiVis project aims to contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment with minimal user input.
+The proposed system implements ideas from the field of active vision, but places a human in the control loop, pictured in Figure~\ref{fig:control-loop}, instead of a electro-mechanical servo.
+%This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
 
-The ActiVis project will contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment with minimal user input.
-The proposed system implements ideas from the field of active vision, but places a human in the control loop, pictured in Figure~\ref{fig:control-loop} instead of a electro-mechanical servo.
-This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
-
-The goal of ActiVis is to understand the user's surroundings and determine what the next best course of action is to reach the target location based on what the it is currently seeing and what it has seen in the past.
-We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action our agent (the guidance system in this case) takes when it finds itself in any state.
+The goal of the ActiVis system is to understand the user's surroundings and determine what the next best course of action is to reach the target location based on what is currently within view and what has been observed in the past.
+We trained a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action the agent (the guidance system in this case) takes when it finds itself within some state.
 
@@
   \item a policy-driven human controller that can drive a user towards a point in space,
-  \item an MDP model that understands the spatial relationship between objects that is based on real data and
-  \item experiments that prove the effectiveness of the current system implementation.
+  \item a data-based MDP model that understands the spatial relationship between objects and
+  \item experiments that prove the effectiveness of the system implementation.
 \end{itemize}
@@
 
-As shown here, much research has been performed on object recognition and guidance towards an object once detected.
-However, work on active object search is harder to come by.
-Therefore, in this work we attempt to implement an active vision~\cite{aloimonos1988active,bellotto2013,lock2017portable} that can guide a user towards an out-of-view target object by using prior knowledge of the spatial distribution of objects within an indoor environment and the history of past object observations made during the search.
-With this, we hope to make the searching process less random and move towards a more natural search object searching process to the benefit of the VI\@.
+Researchers have begun implementing active search and perception~\cite{aloimonos2013active} strategies in robots (CITE) and image classifiers (CITE) in an attempt to optimise their classification and planning tasks by exploiting the structured nature of human object placements.
+
+In (CITE CLASSIFIER), the authors implemented an active search strategy for classifying objects within cluttered images.
+Their approaches use different methods, but both involve using a model to generate windows of interest to submit to a classifier for classification.
+The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets, and are iteratively changed based on the output from the respective models.
+The advantage of their approaches over their contemporaries is that far fewer windows are generated and submitted to the classifier, resulting in lower object classification times.
+They also report comparable accuracy when compared to their contemporaries.
+
+Similarly, roboticists have moved to incorporate similar strategies on robotic platforms to improve autonomous object search, manipulation and localisation tasks.
+The authors in (CITE A* PAPER) developed a planning algorithm that allows a robotic manipulator to select an object to move that optimally executes an object search or exploration task in a cluttered environment.
+In (CITE MDP ROBOT), the authors implemented an MDP that generates the optimal search strategy to find an object in a room over a belief state of object positions and configurations.
+However, the authors trained their MDP using a custom object-placement and configuration probabilities and have shown that the results are sensitive to changes within this distribution.
+
+In all, much research has been conducted on object recognition and guidance towards an object once detected, as well as active vision within image classifiers and robotic systems.
+However, work on active object search and guidance with a human is harder to come by.
+In this work we attempt to implement an active vision guidance system with a human in the loop~\cite{bellotto2013,lock2017portable} that can guide a user towards an out-of-view target object by using prior knowledge of the spatial distribution of objects within an indoor environment and the history of past object observations made during the search.
+With this, we hope to make the searching process less random and move towards a more natural and efficient object searching process to the benefit of the VI\@.
 
@@
 
-\noindent The ActiVis project's goal is to deliver a stand-alone system that only requires a VI user's input for selecting a target object\textbackslash{}destination and then guide the user to it.
+\noindent The ActiVis project's goal is to deliver a stand-alone system that only requires a VI user's input for selecting a target object/destination and then guide the user to it.
 A complete system diagram is given is Figure~\ref{fig:control-loop} and consists of a number of elements.
@@
   \includegraphics[width=0.5\textwidth]{figures/office_desk_example.png}
-  \caption{An example of a guidance strategy the MDP will generate. }\label{fig:route-example}
+  \caption{An example of a guidance strategy the MDP generates. }\label{fig:route-example}
 \end{figure}
@@
 The function values can be found in Table~\ref{tab:rewards}.
-$R$ punishes the agent for every step it takes where it does not find the target object and the negative reward is increased if the agent is taking too long to find the target ($n > n_{max}$) or when it wants to search in a site that has been searched already ($v = true$).
+$R$ punishes the agent for every step it takes where it does not find the target object and the negative reward is increased if the agent is taking too long to find the target ($n > n_{\max}$) or when it wants to search in a site that has been searched already ($v = true$).
 Conversely, it gives a significant positive reward when the target object is found.
@@
     $r(s, s'), s\in\mathbf{S}$ & -1  \\ \midrule
-    $r(n >= n_{max})$ & -10 \\ \midrule
+    $r(n > n_{\max})$ & -10 \\ \midrule
     $r(v = true)$  & -10 \\ \midrule
@@
 
-We set the model to track a maximum of of 9 steps to the target, with 9 being the longest possible route on the grid (more details about the grid are in Section~\ref{sec:system-implementation}).
-A search can take longer than 9 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function.
+We set the model to track a maximum of of 11 (inclusive) steps to the target, with 11 being the longest possible route on the grid (more details about the grid are in Section~\ref{sec:system-implementation}).
+A search can take longer than 11 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function.
 The MDP therefore has a total of 144 reachable states ($n_{states}=8\times9\times2$).
@@
   \caption{A table containing the results for the TAR, number of steps and time to target means ($\mu$) and standard deviations ($\sigma$) for each individual participant.}\label{tab:results-full}
-  \begin{tabular}{cc|cc|cc}
+  \begin{tabular}{cccc}
     \toprule
-    \multirow{2}{*}{Participant} & \multirow{2}{*}{TAR [\%]} & \multicolumn{2}{c|}{Num. Steps} & \multicolumn{2}{c}{Time [s]} \\ 
-				 &			     & $\mu$ & $\sigma$		       & $\mu$ & $\sigma$  \\ \midrule
-    s1 & 94 & 7.2 & 5.4 & 29 & 22 \\ \midrule
-    s2 & 79 & 6.7 & 4.8 & 34 & 5.1 \\ \midrule
-    s3 & 91 & 6.3 & 4.9 & 31 & 21 \\ \midrule
-    s4 & 79 & 6.7 & 4.3 & 37 & 5.6 \\ \midrule
-    s5 & 76 & 7.2 & 4.9 & 33 & 14 \\ \midrule
-    s6 & 60 & 8.2 & 5.4 & 24 & 10 \\ \midrule
-    s7 & 86 & 8.5 & 5.8 & 31 & 16 \\ \midrule
-    s8 & 88 & 5.1 & 4.0 & 39 & 21 \\ \midrule
-    s9 & 98 & 7.2 & 5.4 & 39 & 18 \\ \midrule
-    s10 & 67 & 6.6 & 5.4 & 26 & 12 \\ \midrule\midrule
+    Participant & TAR [\%] & Num. Steps & Time [s] \\ \midrule
+    %\multirow{2}{*}{Participant} & \multirow{2}{*}{TAR [\%]} & \multicolumn{2}{c|}{Num. Steps} & \multicolumn{2}{c}{Time [s]} \\ 
+				 %&			     & $\mu$ & $\sigma$		       & $\mu$ & $\sigma$  \\ \midrule
+    s1 & 94 & 7.2 $\pm$ 5.4 & 29 $\pm$ 22 \\ \midrule
+    s2 & 79 & 6.7 $\pm$ 4.8 & 34 $\pm$ 5.1 \\ \midrule
+    s3 & 91 & 6.3 $\pm$ 4.9 & 31 $\pm$ 21 \\ \midrule
+    s4 & 79 & 6.7 $\pm$ 4.3 & 37 $\pm$ 5.6 \\ \midrule
+    s5 & 76 & 7.2 $\pm$ 4.9 & 33 $\pm$ 14 \\ \midrule
+    s6 & 60 & 8.2 $\pm$ 5.4 & 24 $\pm$ 10 \\ \midrule
+    s7 & 86 & 8.5 $\pm$ 5.8 & 31 $\pm$ 16 \\ \midrule
+    s8 & 88 & 5.1 $\pm$ 4.0 & 39 $\pm$ 21 \\ \midrule
+    s9 & 98 & 7.2 $\pm$ 5.4 & 39 $\pm$ 18 \\ \midrule
+    s10 & 67 & 6.6 $\pm$ 5.4 & 26 $\pm$ 12 \\ \midrule
     \bottomrule                    

### 2018-11-21 paper.tex
Added author references

@@
 
-Researchers have begun implementing active search and perception~\cite{aloimonos2013active} strategies in robots (CITE) and image classifiers (CITE) in an attempt to optimise their classification and planning tasks by exploiting the structured nature of human object placements.
+Researchers have begun implementing active search and perception~\cite{aloimonos2013active} strategies in robots and image classifiers in an attempt to optimise their classification and planning tasks by exploiting the structured nature of human object placements.
 
-In (CITE CLASSIFIER), the authors implemented an active search strategy for classifying objects within cluttered images.
+In~\cite{caicedo2015active,gonzalez2015active}, the authors implemented an active search strategy for classifying objects within cluttered images.
 Their approaches use different methods, but both involve using a model to generate windows of interest to submit to a classifier for classification.
@@
 Similarly, roboticists have moved to incorporate similar strategies on robotic platforms to improve autonomous object search, manipulation and localisation tasks.
-The authors in (CITE A* PAPER) developed a planning algorithm that allows a robotic manipulator to select an object to move that optimally executes an object search or exploration task in a cluttered environment.
-In (CITE MDP ROBOT), the authors implemented an MDP that generates the optimal search strategy to find an object in a room over a belief state of object positions and configurations.
+The authors in~\cite{dogar2014object} developed a planning algorithm that allows a robotic manipulator to select an object to move that optimally executes an object search or exploration task in a cluttered environment.
+In~\cite{aydemir2011search}, the authors implemented an MDP that generates the optimal search strategy to find an object in a room over a belief state of object positions and configurations.
 However, the authors trained their MDP using a custom object-placement and configuration probabilities and have shown that the results are sensitive to changes within this distribution.

### 2018-11-21 paper.tex
new title/abstract and some fixes

@@
 
-\title{Designing an Agent for an Active Guidance System for Object Search}
+\title{Object Search with a Mobile Device for the Visually Impaired\\Using an Active Guidance System}
 
@@
 
-\keywords{Active vision, object search, vision impaired, Markov decision process}
+\keywords{Active vision, object search, vision impairment, Markov Decision Process}
 
-\abstract{In this work, we propose a Markov Decision Process-based system that generates guidance instructions for a user to find a target object in an unknown environment and forms part of an active vision indoor guidance system for the visually impaired.
-An initial implementation of this system was implemented in an Android app and a set of experiments were carried out with sighted participants to determine its effectiveness.
-We found that the system works reasonably well and compares well to similar systems.
-}
+\abstract{Nowadays, smartphones can be used to provide a multitude of services to assist people with visual impairments.
+The cameras embedded in these mobile devices, in particular, can be used for many useful tasks, including searching particular objects in unknown environments.
+Although previous research in computer vision has looked at ways to solve these tasks by processing the video frames of the mobile camera, very little work has been done in {\em actively} guiding the user towards specific point of interest that maximise the effectiveness of the underlying visual algorithms.
+In this paper, we propose a control algorithm based on a Markov Decision Process (MDP) that generates instructions, in real-time, to guide a user searching for a target object with a smartphone's camera.
+The solution is part of a more general active vision application for the visually impaired.
+An initial implementation of the system on an Android smartphone was experimentally evaluated with sighted participants to determine the performance of the control algorithm.
+The results show the effectiveness of our solution and its potential application to help the visually impaired find objects in unknown environments.}
 
@@
 
-\section{\uppercase{Future Work and Conclusion}}\label{sec:conclusion}
+\section{\uppercase{Conclusions}}\label{sec:conclusion}
 
@@
 
-\clearpage
+% \clearpage
 \bibliographystyle{apalike}

### 2018-11-21 paper.tex
Edits

--- 2018-11-21 paper.tex
@@
 \author{
-  \authorname{John Anon{\sup{1}}}
+  \authorname{Anon McAnon{\sup{1}}}
   \affiliation{\sup{1}Anon University of Anon, Anonville, Anonistan}
@@
 The ActiVis project aims to contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment with minimal user input.
-The proposed system implements ideas from the field of active vision, but places a human in the control loop, pictured in Figure~\ref{fig:control-loop}, instead of a electro-mechanical servo.
+The proposed system implements ideas from the field of active vision, but replaces the electro-mechanical servo used in a typical control loop, pictured in Figure~\ref{fig:control-loop}, with a human.
 %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
@@
 
-\noindent The ActiVis project's goal is to deliver a stand-alone system that only requires a VI user's input for selecting a target object/destination and then guide the user to it.
-A complete system diagram is given is Figure~\ref{fig:control-loop} and consists of a number of elements.
-
+\noindent The ActiVis project's goal is to deliver a stand-alone system that can guide a VI user to their destination with minimal user input or intervention.
+A complete system diagram is given is Figure~\ref{fig:control-loop}.
 The system design loop is similar to that of a classical control problem where a controller generates a control signal that drives a component towards some reference point.
@@
 Therefore, the goal of the control block, $K$, is to generate guidance instructions, $u$ to drive the user along a search path towards the target object.
-Since we place a human in the control loop and are not working with a electro-mechanical system, we have an extra block, $H$, that interprets $u$ and executes a physical action, $u^*$, that manipulates the sensor, $P$, that makes a new observation.
+Since we place a human in the control loop, we have an extra block, $H$, that interprets $u$ and executes a physical action, $u^*$, that manipulates the sensor, $P$, that makes a new object observation.
 The new observation is then fed back to the loop and the error signal, $e$, is updated accordingly.
@@
 This path is generated one waypoint at a time by the system and is updated with every object observation the user makes after adjusting the camera.
-We modelled and solved the search problem using an Markov Decision Process (MDP) model.
-The details of the MDP model design and implementation are discussed in the sections below.
+We modelled and solved the search problem using an MDP model.
+The details of the model's design and implementation are discussed in the following sections.
 %For this initial design, the system only works in the pan and tilt dimension and the depth dimension will be added after successful testing of this version of the guidance system.
@@
 It does this by inferring the current state by sampling the object currently within the camera's view, and generates an action that leads the user to the target object.
+The states are sampled and the actions are generated in discretised steps as the user moves the camera's view in the instructed direction.
+This discrete behaviour is similar to a waypoint navigation approach where the user goes from one waypoint to the next, until the user points the camera to target object.
 
@@
 
-The states are sampled and the actions are generated in discretised steps as the user moves the camera's view in the instructed direction.
-This discrete behaviour is similar to a waypoint navigation approach where the user goes from one waypoint to the next, until the user points the camera to target object.
-
 \subsubsection{State Transition Probabilities}
 
-\noindent The state transition function, $\mathbf{T}$, defines the likelihood of the agent transitioning into state $s'$ from state $s$ when taking action $a$, i.e.\ the likelihood of moving to a new pan/tilt position and observing object $o$ after performing action $a$.
+\noindent The state transition function, $\mathbf{T}$, defines the probability of the agent transitioning into state $s'$ from state $s$ when taking action $a$, i.e.\ the likelihood of moving to a new pan/tilt position and observing object $o$ after performing action $a$.
 Therefore, $\mathbf{T}$ represents the spatial relationships between the different objects in the environment model.
@@
 
-For our system, the agent's target state is any state where $s = \langle{}o=o_{target}, n, v\rangle$.
-This gives a total of 18 terminal states (9$\times$2) per policy, since the target object can can be found at any point in the search or in a position that was previously explored by the agent and user.
+The agent's target state is any state where $s = \langle{}o=o_{target}, n, v\rangle$.
+This gives a total of 14 terminal states (7$\times$2) per policy, since the target object can can be found at any point in the search or in a position that was previously explored by the agent and user.
 Each target object has its own unique policy file.
@@
 The function values can be found in Table~\ref{tab:rewards}.
-$R$ punishes the agent for every step it takes where it does not find the target object and the negative reward is increased if the agent is taking too long to find the target ($n > n_{\max}$) or when it wants to search in a site that has been searched already ($v = true$).
+$R$ punishes the agent for every step it takes where it does not find the target object and the negative reward is increased if the agent is taking too long to find the target ($n > n_{\max}$) or when it generates a waypoint in a location that it has generated a waypoint previously ($v = true$).
 Conversely, it gives a significant positive reward when the target object is found.
@@
 
-The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset\footnote{https://storage.googleapis.com/openimages/web/index.html}~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to test their models on.
+The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset\footnote{https://storage.googleapis.com/openimages/web/index.html}~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to benchmark their models.
 The bounding boxes and object labels are used to extract the spatial relationships between the different objects in $\mathbf{O}$.
@@
 A search can take longer than 11 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function.
-The MDP therefore has a total of 144 reachable states ($n_{states}=8\times9\times2$).
+The MDP therefore has a total of 154 reachable states ($s_{total}=11\times7\times2$).
 
@@
 As expected, the number of steps on the simulation required on average to find the target object is less than for the experiments.
-The full set of results for the simulation is given in Figure~\ref{fig:sim-vs-experiment} which plots the number of coincidences between the simulation and experiment results.
+The full set of results for the simulation is given by a frequency mapping of the coincidences between the simulation and experimental data in Figure~\ref{fig:sim-vs-experiment}.
 

### 2018-11-21 paper.tex
title update
Edit to result section

@@
 
-\noindent In order to evaluate our system, we identified 3 different measures: target acquisition rate (TAR), number of steps to the target and the total time it took to find a target object.
+\noindent We identified 3 different measures to evaluate the system's performance: target acquisition rate (TAR), number of steps to the target and the total time it took to find a target object.
 We present and discuss the results for each of these parameters in the next sections.
 The results for each individual participant is presented in Table~\ref{tab:results-full} and Table~\ref{tab:results-summary} gives the results across all of the participants.
-
 To provide a baseline measure for the ideal case, we ran a number of simulations in an environment mimicking the experiment setup with an agent that perfectly executes the policy, i.e.\ $u=u^*$.
@@
   \centering
-  \caption{A table containing the results for the TAR, number of steps and time to target means ($\mu$) and standard deviations ($\sigma$) for each individual participant.}\label{tab:results-full}
+  \caption{A table containing the results for the TAR, number of steps and time to target means ($\mu$) and standard deviations ($\sigma$) for each participant. }\label{tab:results-full}
   \begin{tabular}{cccc}
@@
   \centering                       
-  \caption{A table summarising the means ($\mu$) and standard deviations ($\sigma$) for the entire participant population for the experiment and simulation.}\label{tab:results-summary}
+  \caption{The means and standard deviations for the entire participant population for the experiments and simulations.}\label{tab:results-summary}
   \begin{tabular}{llc}
@@
 
-\noindent The TAR is a measure of how successful the system was at directing a participant to the target object within the 16-step limit we imposed and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches.
+\noindent The TAR is a measure of how successful the system was at directing a participant to the target object within the 15-step limit we set and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches.
 Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present.
-
-\uline{From Figure~\ref{fig:tar-steps} we can see that the TAR has a gradual increase as we vary the step limit.
-This appears to justify our choice of a 15-waypoint cut-off.
-However, the spiking tail should be considered.
-}
+Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off at higher step-limits.
+\uline{The angled tail at the 15-step limit is interesting to note, however.
+WHY}
 
@@
 Figure~\ref{fig:tar-objects} shows the TAR for each object in $\mathbf{O}$.
-From it, we can see that there are variations the TAR for the different objects, with the smaller objects typically being the hardest to find.
+There are variations the TAR for the different objects, with the smaller objects typically being the hardest to find.
 However, the differences are not extreme and indicate that all the objects in $\mathbf{O}$ are roughly equally hard to find.
@@
   \includegraphics[width=0.45\textwidth]{figures/tar_objects.png}
-  \caption{The TAR for each of the objects within the target object set. }\label{fig:tar-objects}
+  \caption{The TAR for each of the objects within $\mathbf{O}$. }\label{fig:tar-objects}
 \end{figure}
 
-The TAR can be improved with regards to entering a no-recovery state where it directs a user into dead-space with no spatial information (e.g.\ a ceiling or wall section) and cannot gather the information it requires to intelligently guide the user.
-Subsequent system updates will have to consider implementing fall-back methods or other automatic recovery modes that can detect entry of a no-recovery state (e.g.\ exceeding a set number of steps/time without making an observation) and guide the user back to the initial position.
+Failure cases were typically caused by the system entering a no-recovery state where the system directed a user into dead-space with no spatial information (e.g.\ a ceiling or wall section) and could not gather the information it required to intelligently guide the user.
+Subsequent system updates will have to consider implementing fall-back methods or automatic recovery modes that can detect entry of a no-recovery state (e.g.\ exceeding a set number of steps/time without making an observation) and guide the user back to the initial position and restart a search.
 
@@
 
-\noindent The number of steps target indicates the number of waypoints the system generated for the participant during the guidance process and is a major indication of system performance, where less waypoints means faster target acquisition and better performance.
+\noindent The number of steps to the target indicates the number of waypoints the system generated for the participant during the guidance process and is a major indication of system performance, where less waypoints means faster target acquisition and better performance.
 Figure~\ref{fig:nsteps-participants} shows the cumulative distribution of the number of steps to the target for all the participants.
@@
 
-The number of waypoints each participant required is fairly evenly spread across all of the participants.
+The number of waypoints each participant required is fairly evenly spread across all of the participants, with the majority of searches ending at $n < 4 \land n > 13$.
 The population mean and standard deviation is 6.8 and 5.1 waypoints respectively.
-This is a reasonable result that was also somewhat expected, since most target objects were placed within approximately 4 grid squares away from the participants' initial looking directions.
+This is a reasonable result, since most target objects were placed within approximately 4 grid squares away from the participants' initial looking directions.
 However, the relatively high standard deviation should be noted and can also be reduced by implementing the automatic recovery mode mentioned previously, and avoiding information-sparse areas.
 
-As expected, the number of steps on the simulation required on average to find the target object is less than for the experiments.
+As expected, the number of steps the simulation required on average to find the target object is less than the participants did during the experiments.
 The full set of results for the simulation is given by a frequency mapping of the coincidences between the simulation and experimental data in Figure~\ref{fig:sim-vs-experiment}.
@@
 
+\uline{COMPARE RESULTS FROM ROBOTS? APPROX 100s FOR PLANNING AND EXECUTION}
+
 \section{\uppercase{Conclusions}}\label{sec:conclusion}
@@
 However, the system can be improved by refining the search strategy and implementing an automatic fail-state recovery system that will guide a user back to neutral position if a fail-state is entered (e.g.\ a blank section of wall).
+Furthermore, a different dataset, purpose-built for object spatial relations, will give the MDP a more accurate understanding of the world and an improved transition model.
 

### 2018-11-22 paper.tex
minor fixes to intro. see red comments.

@@
 
+\newcommand{\todo}[1]{\textcolor{red}{[#1]}}
+
 \begin{document}
 
-\title{Object Search with a Mobile Device for the Visually Impaired\\Using an Active Guidance System}
+\title{Active Object Search with a Mobile Device for the Visually Impaired}
 
@@
 
-\abstract{Nowadays, smartphones can be used to provide a multitude of services to assist people with visual impairments.
+\abstract{Smartphones can be used to provide a multitude of services to assist people with visual impairments.
 The cameras embedded in these mobile devices, in particular, can be used for many useful tasks, including searching particular objects in unknown environments.
@@
 
-\noindent It is estimated that there are 440 million people worldwide that live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives.
+\noindent It is estimated that almost half billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives.
 Modern improvements to mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem.
-The ActiVis project aims to contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment with minimal user input.
-The proposed system implements ideas from the field of active vision, but replaces the electro-mechanical servo used in a typical control loop, pictured in Figure~\ref{fig:control-loop}, with a human.
+%The ActiVis project aims to contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or
+The work here presented is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone.
+The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of the moving camera with the body (i.e.
+arm, hand) of the user holding the smartphone.
+Schematically, the actuators used in a typical control loop, pictured in Figure~\ref{fig:control-loop}, are replaced by a human.
 %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
@@
   \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
-  \caption{The ActVis system layout and control loop. }\label{fig:control-loop}
+  \caption{The ActVis system layout and control loop.
+\todo{Explain the meanings of the symbols r, e, ...
+in the caption.
+Remove all direct references to ActiVis with more generic ``our project''.}}\label{fig:control-loop}
 \end{figure}
@@
 
-Researchers have begun implementing active search and perception~\cite{aloimonos2013active} strategies in robots and image classifiers in an attempt to optimise their classification and planning tasks by exploiting the structured nature of human object placements.
+Researchers implemented active search and perception~\cite{Bajcsy2017} strategies in robots and image classifiers in an attempt to optimise their classification and planning tasks by exploiting the structured nature of human object placements.
 

### 2018-11-22 paper.tex
Added new figure. Other minor edits
Edit/fix to figure and not using project name. Other small edits

@@
 
-\noindent It is estimated that almost half billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives.
+\noindent It is estimated that almost half a billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives.
 Modern improvements to mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem.
 %The ActiVis project aims to contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or
-The work here presented is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone.
-The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of the moving camera with the body (i.e.
-arm, hand) of the user holding the smartphone.
+The work presented here is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone.
+The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of the moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}.
 Schematically, the actuators used in a typical control loop, pictured in Figure~\ref{fig:control-loop}, are replaced by a human.
@@
 
-The goal of the ActiVis system is to understand the user's surroundings and determine what the next best course of action is to reach the target location based on what is currently within view and what has been observed in the past.
-We trained a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action the agent (the guidance system in this case) takes when it finds itself within some state.
-
 \begin{figure}
   \centering
+  \begin{subfigure}
+    \centering
+    \includegraphics[width=0.38\textwidth]{figures/system_use.png}
+    \caption{The system in use during an experiment. }\label{fig:system-use}
+  \end{subfigure}
+  \begin{subfigure}
+    \centering
     \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
-  \caption{The ActVis system layout and control loop.
-\todo{Explain the meanings of the symbols r, e, ...
-in the caption.
-Remove all direct references to ActiVis with more generic ``our project''.}}\label{fig:control-loop}
+    \caption{The system layout and control loop.
+$r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation.
+$K$, $H$ and $P$ are the control, human and sensor blocks respectively.
+}\label{fig:control-loop}
+  \end{subfigure}
 \end{figure}
+
+The goal of this system is to understand the user's surroundings and determine what the next best course of action is to reach the target location based on what is currently within view and what has been observed in the past.
+We trained a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action the agent (the guidance system in this case) takes when it finds itself within some state.
 
@@
 
-Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the ActiVis guidance system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}.
+Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the guidance system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}.
 Then we discuss the experiment and present its results in Section~\ref{sec:experiments}, after which we conclude the paper and discuss the project's next steps in Section~\ref{sec:conclusion}.
@@
 
-\noindent The ActiVis project's goal is to deliver a stand-alone system that can guide a VI user to their destination with minimal user input or intervention.
+\noindent This project's goal is to deliver a stand-alone system that can guide a VI user to their destination with minimal user input or intervention.
 A complete system diagram is given is Figure~\ref{fig:control-loop}.
@@
   \caption{The reward functions for the MDP.\ }\label{tab:rewards}
-  \begin{tabular}{ll}
+  \begin{tabular}{cc}
     \toprule
@@
   \caption{The means and standard deviations for the entire participant population for the experiments and simulations.}\label{tab:results-summary}
-  \begin{tabular}{llc}
+  \begin{tabular}{ccc}
     \toprule

### 2018-11-22 paper.tex
Removed unessessary images from git, edit to section 4

@@
 
-\noindent The guidance system is built into an Android app and uses Android's ARCore\footnote{https://developers.google.com/ar/} API to track the device's pose.
-The system is designed with the goal of generating a path of waypoints for the user to follow, by pointing the device camera, that will lead the user to the target object.
+\noindent The system guides a user by generating a set of waypoints to indicate an area for the user to investigate with the camera and will lead the user to the target object.
 This path is generated one waypoint at a time by the system and is updated with every object observation the user makes after adjusting the camera.
-We modelled and solved the search problem using an MDP model.
-The details of the model's design and implementation are discussed in the following sections.
+We modelled the problem using an MDP and the details of the model's design and implementation are discussed in the following sections.
 %For this initial design, the system only works in the pan and tilt dimension and the depth dimension will be added after successful testing of this version of the guidance system.
-
+ %The guidance system is built into an Android app and uses Android's ARCore API to track the device's pose. 
 %\subsection{Environment Model}\label{sec:env-design}
@@
 The MDP's task is to direct the user to point the camera to the target object (the mug in the bottom-left of Figure~\ref{fig:route-example}).
-It does this by inferring the current state by sampling the object currently within the camera's view, and generates an action that leads the user to the target object.
+It does this by inferring the current state by sampling the object currently within the camera's view and generates an action that leads the user to the target object.
 The states are sampled and the actions are generated in discretised steps as the user moves the camera's view in the instructed direction.
-This discrete behaviour is similar to a waypoint navigation approach where the user goes from one waypoint to the next, until the user points the camera to target object.
+%This discrete behaviour is similar to a waypoint navigation approach where the user goes from one waypoint to the next, until the user points the camera to target object.
 
@@
 
-The app was developed on and experimented with an Asus ZenPhone AR\footnote{asus.com/uk/Phone/ZenFone-AR-ZS571KL/} running Android version 7.0 with the ARCore SDK enabled.
+The app was developed on and experimented with an Asus ZenPhone AR\footnote{asus.com/uk/Phone/ZenFone-AR-ZS571KL/} running Android version 7.0 with the ARCore\footnote{https://developers.google.com/ar/} SDK enabled.
 No hardware or software modifications were required.

### 2018-11-22 paper.tex
Edit figure, edit to way work was referened in sec2

@@
 Another approach is to discard tags completely and rely on computer vision to perform the object detection, something that has become more plausible with recent improvements to feature detectors and deep networks~\cite{huang2017speed,redmon2016you}.
-The system described~\cite{schauerte2012assistive} uses a combination of SIFT and SURF to detect known objects when they are in the camera's view and guide the user to them using sonified guidance instructions.
+SIFT and SURF-based object detectors have also been used to detect known objects when they are in the camera's view and guide the user to them using sonified guidance instructions~\cite{schauerte2012assistive}.
 This system is more flexible than the tag-based ones, but have the same drawback of being passive and rely on chance for the user to place the object within the camera's view in the first place.
 The paper also does not report on any performance metrics.
-In~\cite{bigham2010vizwiz}, the authors discuss their VizWiz system that offloads the object recognition tasks to an Amazon Mechanical Turk worker that then provides feedback on where the object of interest is located relative to the user.
+The VizWize system~\cite{bigham2010vizwiz} offloads the object recognition tasks to an Amazon Mechanical Turk worker that then provides feedback on where the object of interest is located relative to the user.
 The VizWiz has the advantage of being fairly robust and is able to classify a great deal of objects with little effort from the user and can provide natural, human-generated and curated directions.
@@
 
-In~\cite{caicedo2015active,gonzalez2015active}, the authors implemented an active search strategy for classifying objects within cluttered images.
+Two research teams have recently implemented an active object search strategy into their image classifiers~\cite{caicedo2015active,gonzalez2015active}.
 Their approaches use different methods, but both involve using a model to generate windows of interest to submit to a classifier for classification.
@@
 The advantage of their approaches over their contemporaries is that far fewer windows are generated and submitted to the classifier, resulting in lower object classification times.
-They also report comparable accuracy when compared to their contemporaries.
+They also report comparable accuracy compared to their counterparts.
 
 Similarly, roboticists have moved to incorporate similar strategies on robotic platforms to improve autonomous object search, manipulation and localisation tasks.
-The authors in~\cite{dogar2014object} developed a planning algorithm that allows a robotic manipulator to select an object to move that optimally executes an object search or exploration task in a cluttered environment.
-In~\cite{aydemir2011search}, the authors implemented an MDP that generates the optimal search strategy to find an object in a room over a belief state of object positions and configurations.
+Researchers have developed a planning algorithm that allows a robotic manipulator to select an object to move that optimally executes an object search or exploration task in a cluttered environment~\cite{dogar2014object}.
+Another team implemented an MDP that generates the optimal search strategy to find an object in a room over a belief state of object positions and configurations~\cite{aydemir2011search}.
 However, the authors trained their MDP using a custom object-placement and configuration probabilities and have shown that the results are sensitive to changes within this distribution.
@@
 The model is trained until it converges to the optimal policy, or for a total of approximately 17 million episodes.
-The parameter, $\alpha$, that controls the exploration vs.\ exploitation behaviour during training maximises exploration when it is set to $1.0$ and exploitation when it is $0.0$.
+The parameter, $\alpha$, that controls the exploration vs.\ exploitation behaviour during training maximises exploration when it is set to $1$ and exploitation when it is $0$.
 We set $\alpha$ to a function that starts at a high exploration value and exponentially changes it behaviour to exploitation as it becomes more trained.
@@
 \begin{equation}
-  \alpha = \exp\Big(\frac{-i}{10n_{states}}\Big) - 0.001,
+  \alpha = \exp\Big(\frac{-i}{10s_{total}}\Big) - 0.001,
 \end{equation}
@@
 
-The app was developed on and experimented with an Asus ZenPhone AR\footnote{asus.com/uk/Phone/ZenFone-AR-ZS571KL/} running Android version 7.0 with the ARCore\footnote{https://developers.google.com/ar/} SDK enabled.
+The app was developed on and experimented with an Asus ZenPhone AR\todo{No footers}\footnote{asus.com/uk/Phone/ZenFone-AR-ZS571KL/} running Android version 7.0 with the ARCore\footnote{https://developers.google.com/ar/} SDK enabled.
 No hardware or software modifications were required.
@@
 Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off at higher step-limits.
-\uline{The angled tail at the 15-step limit is interesting to note, however.
-WHY}
+The angled tail at the 15-step limit is interesting to note, however.
+\todo{WHY}
 
@@
 
-\uline{COMPARE RESULTS FROM ROBOTS? APPROX 100s FOR PLANNING AND EXECUTION}
+\todo{COMPARE RESULTS FROM ROBOTS? APPROX 100s FOR PLANNING AND EXECUTION}
 
@@
 \bibliographystyle{apalike}
-\bibliography{bib}
+{\small
+\bibliography{bib}}
 

### 2018-11-22 paper.tex
Edits

@@
 Table~\ref{tab:results-full} shows a fairly consistent spread for the TAR across the participants.
-The inter-participant spread ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance, but with an average TAR of $81.2\%$, it is clear that the system successfully finds the target object during the vast majority of searches.
+The inter-participant spread ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance, but with an average TAR of $81.9\%$, it is clear that the system successfully finds the target object during the vast majority of searches.
 

### 2018-11-22 paper.tex
Edits

@@
 Table~\ref{tab:results-full} shows a fairly consistent spread for the TAR across the participants.
-The inter-participant spread ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance, but with an average TAR of $81.9\%$, it is clear that the system successfully finds the target object during the vast majority of searches.
+The inter-participant spread ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance, but with an average TAR of $82\%$, it is clear that the system successfully finds the target object during the vast majority of searches.
 

### 2018-11-22 paper.tex
Removed confusing figure, changed 2 plots to clarify info, implemented changes discussed in office

@@
   \end{subfigure}
+  \hspace{8mm}
   \begin{subfigure}
@@
 \begin{equation}
-  R = r(s, s').
+  R\in r(s, s').
 \end{equation}
@@
 
-The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset\footnote{https://storage.googleapis.com/openimages/web/index.html}~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to benchmark their models.
+The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to benchmark their models.
 The bounding boxes and object labels are used to extract the spatial relationships between the different objects in $\mathbf{O}$.
@@
 
-The app was developed on and experimented with an Asus ZenPhone AR\todo{No footers}\footnote{asus.com/uk/Phone/ZenFone-AR-ZS571KL/} running Android version 7.0 with the ARCore\footnote{https://developers.google.com/ar/} SDK enabled.
+The app was developed on and experimented with an Asus ZenPhone AR running Android version 7.0 with Google's augmented reality toolkit (ARCore) enabled for measurement and device tracking.
 No hardware or software modifications were required.
@@
   \centering
-  \caption{A table containing the results for the TAR, number of steps and time to target means ($\mu$) and standard deviations ($\sigma$) for each participant. }\label{tab:results-full}
+  \caption{A table containing the results for the TAR, number of steps and time to target means and standard deviations for each participant. }\label{tab:results-full}
   \begin{tabular}{cccc}
@@
 Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present.
-Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off at higher step-limits.
-The angled tail at the 15-step limit is interesting to note, however.
-\todo{WHY}
+Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off as the step-limit increases.
 
@@
   \includegraphics[width=0.5\textwidth]{figures/cdf_tar_limit.png}
-  \caption{The distribution of the TAR as a function of the step limit for a search. }\label{fig:tar-steps}
+  \caption{The distribution of the TAR as a function of the step limit for a search. The `x' indicates the cases that exceeded the 15-step limit. }\label{fig:tar-steps}
 \end{figure}
@@
 
-The number of waypoints each participant required is fairly evenly spread across all of the participants, with the majority of searches ending at $n < 4 \land n > 13$.
+The number of waypoints each participant required is fairly evenly spread across all of the participants, with the majority of searches ending within 4 steps of initialisation or ending.
 The population mean and standard deviation is 6.8 and 5.1 waypoints respectively.
@@
 
-As expected, the number of steps the simulation required on average to find the target object is less than the participants did during the experiments.
+%As expected, the number of steps the simulation required on average to find the target object is less than the participants did during the experiments.
 The full set of results for the simulation is given by a frequency mapping of the coincidences between the simulation and experimental data in Figure~\ref{fig:sim-vs-experiment}.
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{figures/experiment_vs_simulation.png}
-  \caption{A summary of the experiment and simulation steps to target results. }\label{fig:sim-vs-experiment}
-\end{figure}
+%\begin{figure}
+  %\centering
+  %\includegraphics[width=0.5\textwidth]{figures/experiment_vs_simulation.png}
+  %\caption{A summary of the experiment and simulation steps to target results. }\label{fig:sim-vs-experiment}
+%\end{figure}
 

### 2018-11-22 paper.tex
Removed confusing figure, changed 2 plots to clarify info, implemented changes discussed in office
sec I and II revised

@@
 
-\abstract{Smartphones can be used to provide a multitude of services to assist people with visual impairments.
-The cameras embedded in these mobile devices, in particular, can be used for many useful tasks, including searching particular objects in unknown environments.
-Although previous research in computer vision has looked at ways to solve these tasks by processing the video frames of the mobile camera, very little work has been done in {\em actively} guiding the user towards specific point of interest that maximise the effectiveness of the underlying visual algorithms.
+\abstract{Modern smartphones can provide a multitude of services to assist people with visual impairments.
+The cameras embedded in these mobile devices, in particular, can be used for many useful tasks, like reading signs or searching for objects in unknown environments.
+Although previous research in computer vision has looked at ways to solve these tasks by processing the video frames of the mobile camera, very little work has been done in {\em actively} guiding the user towards specific points of interest that maximise the effectiveness of the underlying visual algorithms.
 In this paper, we propose a control algorithm based on a Markov Decision Process (MDP) that generates instructions, in real-time, to guide a user searching for a target object with a smartphone's camera.
@@
 The work presented here is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone.
-The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of the moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}.
-Schematically, the actuators used in a typical control loop, pictured in Figure~\ref{fig:control-loop}, are replaced by a human.
+The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}.
+Schematically, the actuators used in a typical control loop, shown in Figure~\ref{fig:control-loop}, are replaced by a human.
 %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
@@
   \centering
-  \begin{subfigure}
-    \centering
   \includegraphics[width=0.38\textwidth]{figures/system_use.png}
   \caption{The system in use during an experiment. }\label{fig:system-use}
-  \end{subfigure}
-  \hspace{8mm}
-  \begin{subfigure}
+\end{figure}
+
+\begin{figure}
   \centering
   \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
-    \caption{The system layout and control loop.
-$r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation.
+  \caption{System control loop: $r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation.
 $K$, $H$ and $P$ are the control, human and sensor blocks respectively.
 }\label{fig:control-loop}
-  \end{subfigure}
 \end{figure}
 
-The goal of this system is to understand the user's surroundings and determine what the next best course of action is to reach the target location based on what is currently within view and what has been observed in the past.
-We trained a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action the agent (the guidance system in this case) takes when it finds itself within some state.
-
-This work's contributions are
+The goal of our active search system is to understand the user's surroundings and determine what the next best course of action is to reach the target object based on what is currently within view and what has been observed in the past.
+To this end, we implemented a smartphone's guidance system based on a Markov Decision Process (MDP)~\cite{bellman1957markovian} that generates, in real-time, an optimal set of instructions (policy) for the user to point to the target, depending on a previously-learned spatial distribution of known objects and on the current camera's view.
+%
+This work includes three main contributions:
 
 \begin{itemize}
-  \item a policy-driven human controller that can drive a user towards a point in space,
-  \item a data-based MDP model that understands the spatial relationship between objects and
-  \item experiments that prove the effectiveness of the system implementation.
+  \item an MDP-based human controller that can guide a user in a visual search task;
+  \item a data-based transition model for the MDP which includes spatial relations between known objects;
+  \item a set of user experiments that prove the effectiveness of our active search implementation.
 \end{itemize}
@@
 
-Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the guidance system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}.
-Then we discuss the experiment and present its results in Section~\ref{sec:experiments}, after which we conclude the paper and discuss the project's next steps in Section~\ref{sec:conclusion}.
+Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a general explanation of the active vision system for human guidance in Sections~\ref{sec:system-design}, and a detailed explanation of the human-control module in Section~\ref{sec:controller-design}.
+The experimental results are presented in Section~\ref{sec:experiments}, after which we conclude the paper and discuss future work in Section~\ref{sec:conclusion}.
 
@@
 
-\noindent Assistive vision and guidance for the VI is an active and diverse field of study.
-In recent years, the increase in mobile processing power and computer vision improvements have led to researchers investigating using a cellphone camera to augment or enhance a user's vision and help them find objects or another point of interest.
-Earlier attempts at the problem involved placing special markers or barcodes, encoded with information about an object or the area, around an environment, which the user then scans with a cellphone or similar mobile device~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}.
-This device then uses some feedback mode, e.g.\ Braille and sound, to guide the user towards the target.
+\noindent Assistive vision and guidance for the VI is a growing research area.
+In recent years, the increase in mobile processing power and computer vision improvements have led to research in the use of smartphone cameras to augment or enhance a user's vision and help them find objects or other points of interest.
+Earlier attempts at the problem involved placing special markers or barcodes around an environment, which the user then scans with a smartphone or similar mobile device~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}.
+This device then uses some feedback mode, e.g.~Braille or sound, to guide the user towards the target.
 %The major drawbacks to this approach is the significant upfront effort required to augment entire areas with markers to a point where the system will be useful to a VI user.
@@
 
-Another approach is to discard tags completely and rely on computer vision to perform the object detection, something that has become more plausible with recent improvements to feature detectors and deep networks~\cite{huang2017speed,redmon2016you}.
-SIFT and SURF-based object detectors have also been used to detect known objects when they are in the camera's view and guide the user to them using sonified guidance instructions~\cite{schauerte2012assistive}.
-This system is more flexible than the tag-based ones, but have the same drawback of being passive and rely on chance for the user to place the object within the camera's view in the first place.
-The paper also does not report on any performance metrics.
-The VizWize system~\cite{bigham2010vizwiz} offloads the object recognition tasks to an Amazon Mechanical Turk worker that then provides feedback on where the object of interest is located relative to the user.
+Another approach is to discard tags completely and rely on computer vision to perform the object detection, something that has become more practical with recent improvements to feature detectors and deep networks~\cite{huang2017speed,redmon2016you}.
+SIFT and SURF-based object detectors have also been used to detect known objects, when they are in the camera's view, and to guide the user to them using sonified instructions~\cite{schauerte2012assistive}.
+This type of systems is more flexible than the tag-based ones, but it has the same drawback of being {\em passive}, in the sense that it relies on having the object within the camera's view in the first place.
+Also, no clear performance metrics are reported in the previous paper.
+The VizWize system~\cite{bigham2010vizwiz} offloads the object recognition tasks to an Amazon Mechanical Turk worker who then provides feedback on where the object of interest is located relative to the user.
 The VizWiz has the advantage of being fairly robust and is able to classify a great deal of objects with little effort from the user and can provide natural, human-generated and curated directions.
-However, this approach does not address the issue of enhancing user independence, since the user is now beholden to an online worker instead of a relative, friend or bystander.
-Furthermore, a good internet connection is required on the device, perhaps limiting use in some poor-reception areas.
+However, this approach does not enhance user independence, since the VI person is now beholden to an online worker instead of a relative, friend or bystander.
+Furthermore, a good internet connection is required on the device, possibly limiting its use in some poor-reception areas.
 
-Researchers implemented active search and perception~\cite{Bajcsy2017} strategies in robots and image classifiers in an attempt to optimise their classification and planning tasks by exploiting the structured nature of human object placements.
+Many previous researchers have implemented active search and perception strategies in robots and image classifiers~\cite{Bajcsy2017} in an attempt to optimise their classification and planning tasks, for example by exploiting the structured nature of human environments and object placements.
+%
+Two research teams have recently implemented an active object search strategy into their image classifiers~\cite{caicedo2015active,gonzalez2015active}.
+Their approaches use different methods but conceptually similar models to generate windows of interest for visual classification.
+The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets~\cite{song2016ssc,Everingham10}, and are iteratively changed based on the output from the respective models.
+The advantage of their approaches is that fewer windows are generated and submitted to the classifier, resulting in lower object classification times.
+The authors also report comparable accuracy compared to their counterparts.
 
-Two research teams have recently implemented an active object search strategy into their image classifiers~\cite{caicedo2015active,gonzalez2015active}.
-Their approaches use different methods, but both involve using a model to generate windows of interest to submit to a classifier for classification.
-The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets, and are iteratively changed based on the output from the respective models.
-The advantage of their approaches over their contemporaries is that far fewer windows are generated and submitted to the classifier, resulting in lower object classification times.
-They also report comparable accuracy compared to their counterparts.
+Similar strategies have been incorporated on robotic platforms to improve autonomous object search, manipulation and localisation tasks.
+For example, some researchers have developed a planning algorithm for a robotic manipulator that performs an optimal object search in a cluttered environment~\cite{dogar2014object}.
+Another team implemented an MDP-based system generating an optimal object search strategy in a room over a belief state of object positions and configurations~\cite{aydemir2011search}.
+However, the authors trained their MDP using a custom object-placement and configuration scenario, so their results are sensitive to changes within this distribution.
 
-Similarly, roboticists have moved to incorporate similar strategies on robotic platforms to improve autonomous object search, manipulation and localisation tasks.
-Researchers have developed a planning algorithm that allows a robotic manipulator to select an object to move that optimally executes an object search or exploration task in a cluttered environment~\cite{dogar2014object}.
-Another team implemented an MDP that generates the optimal search strategy to find an object in a room over a belief state of object positions and configurations~\cite{aydemir2011search}.
-However, the authors trained their MDP using a custom object-placement and configuration probabilities and have shown that the results are sensitive to changes within this distribution.
-
-In all, much research has been conducted on object recognition and guidance towards an object once detected, as well as active vision within image classifiers and robotic systems.
-However, work on active object search and guidance with a human is harder to come by.
-In this work we attempt to implement an active vision guidance system with a human in the loop~\cite{bellotto2013,lock2017portable} that can guide a user towards an out-of-view target object by using prior knowledge of the spatial distribution of objects within an indoor environment and the history of past object observations made during the search.
-With this, we hope to make the searching process less random and move towards a more natural and efficient object searching process to the benefit of the VI\@.
+In summary, much research has been conducted on recognition of and guidance towards target objects, including active vision solutions for image classifiers and robotic systems.
+However, to our knowledge, no previous work has been done on {\em active} object search and guidance for humans, which would especially benefit VI users.
+In this paper, we implement such an active vision system with a human in the loop
+% ~\cite{bellotto2013,lock2017portable}
+that guides the user towards an out-of-view target object.
+Our system exploits prior knowledge of the objects spatial distribution within an indoor environment, learned from a dataset of real-world images, and the history of past object observations made during the search.
+%With this, we hope to make the searching process less random and move towards a more natural and efficient object searching process to the benefit of the VI\@.
 
@@
 In comparison to the VizWiz system~\cite{bigham2010vizwiz} (mean 92s, standard deviation 37.7s), our results look very reasonable.
-However, these results may greatly change when we test the system with VI participants like they did in~\cite{bigham2010vizwiz}.
-
-\todo{COMPARE RESULTS FROM ROBOTS? APPROX 100s FOR PLANNING AND EXECUTION}
+However, these results may greatly change when we test the system with VI participants.
 

### 2018-11-22 paper.tex
small typo revisions in sec1+2

@@
 \abstract{Modern smartphones can provide a multitude of services to assist people with visual impairments.
-The cameras embedded in these mobile devices, in particular, can be used for many useful tasks, like reading signs or searching for objects in unknown environments.
+The cameras embedded in these mobile devices, in particular, can be useful for many tasks, like reading signs or searching for objects in unknown environments.
 Although previous research in computer vision has looked at ways to solve these tasks by processing the video frames of the mobile camera, very little work has been done in {\em actively} guiding the user towards specific points of interest that maximise the effectiveness of the underlying visual algorithms.
-In this paper, we propose a control algorithm based on a Markov Decision Process (MDP) that generates instructions, in real-time, to guide a user searching for a target object with a smartphone's camera.
+In this paper, we propose a control algorithm based on a Markov Decision Process (MDP) that generates real-time instructions to guide a user searching for a target object with a smartphone's camera.
 The solution is part of a more general active vision application for the visually impaired.
@@
 \noindent It is estimated that almost half a billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives.
-Modern improvements to mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem.
-%The ActiVis project aims to contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or
+Modern improvements in mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem.
 The work presented here is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone.
@@
 The goal of our active search system is to understand the user's surroundings and determine what the next best course of action is to reach the target object based on what is currently within view and what has been observed in the past.
-To this end, we implemented a smartphone's guidance system based on a Markov Decision Process (MDP)~\cite{bellman1957markovian} that generates, in real-time, an optimal set of instructions (policy) for the user to point to the target, depending on a previously-learned spatial distribution of known objects and on the current camera's view.
+To this end, we implemented a smartphone guidance system based on a Markov Decision Process (MDP)~\cite{bellman1957markovian} that generates, in real-time, a series of instructions for the user to point to the target, depending on a previously-learned spatial distribution of known objects and on the camera's current view.
 %
@@
 
-Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a general explanation of the active vision system for human guidance in Sections~\ref{sec:system-design}, and a detailed explanation of the human-control module in Section~\ref{sec:controller-design}.
+Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a general explanation of the active vision system for human guidance in Section~\ref{sec:system-design}, and a detailed explanation of the human-control module in Section~\ref{sec:controller-design}.
 The experimental results are presented in Section~\ref{sec:experiments}, after which we conclude the paper and discuss future work in Section~\ref{sec:conclusion}.
@@
 Earlier attempts at the problem involved placing special markers or barcodes around an environment, which the user then scans with a smartphone or similar mobile device~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}.
-This device then uses some feedback mode, e.g.~Braille or sound, to guide the user towards the target.
+This device then uses some feedback mode, e.g.\ Braille or sound, to guide the user towards the target.
 %The major drawbacks to this approach is the significant upfront effort required to augment entire areas with markers to a point where the system will be useful to a VI user.
@@
 SIFT and SURF-based object detectors have also been used to detect known objects, when they are in the camera's view, and to guide the user to them using sonified instructions~\cite{schauerte2012assistive}.
-This type of systems is more flexible than the tag-based ones, but it has the same drawback of being {\em passive}, in the sense that it relies on having the object within the camera's view in the first place.
+These type of systems is more flexible than the tag-based ones, but it has the same drawback of being {\em passive}, in the sense that it relies on having the object within the camera's view in the first place.
 Also, no clear performance metrics are reported in the previous paper.
-The VizWize system~\cite{bigham2010vizwiz} offloads the object recognition tasks to an Amazon Mechanical Turk worker who then provides feedback on where the object of interest is located relative to the user.
+The VizWiz system~\cite{bigham2010vizwiz} offloads the object recognition tasks to an Amazon Mechanical Turk worker who then provides feedback on where the object of interest is located relative to the user.
 The VizWiz has the advantage of being fairly robust and is able to classify a great deal of objects with little effort from the user and can provide natural, human-generated and curated directions.

### 2018-11-22 paper.tex
sec III revised

@@
 The work presented here is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone.
-The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}.
-Schematically, the actuators used in a typical control loop, shown in Figure~\ref{fig:control-loop}, are replaced by a human.
+The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017,bellotto2013}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Fig.~\ref{fig:system-use}.
+Schematically, the actuators used in a typical control loop, shown in Fig.~\ref{fig:control-loop}, are replaced by a human.
 %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
@@
 
-%is the design of a guidance system and MDP (the control-block, $K$, pictured in Figure~\ref{fig:control-loop}) that can drive a user to point a mobile device's camera towards a given point in space in and find a target object.
+%is the design of a guidance system and MDP (the control-block, $K$, pictured in Fig.~\ref{fig:control-loop}) that can drive a user to point a mobile device's camera towards a given point in space in and find a target object.
 We also present and discuss preliminary experimental results to show how effective the system is at finding a target.
@@
 
-Many previous researchers have implemented active search and perception strategies in robots and image classifiers~\cite{Bajcsy2017} in an attempt to optimise their classification and planning tasks, for example by exploiting the structured nature of human environments and object placements.
+Previous researchers have implemented active search and perception strategies in robots and image classifiers~\cite{Bajcsy2017} in an attempt to optimise their classification and planning tasks, for example by exploiting the structured nature of human environments and object placements.
 %
@@
 The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets~\cite{song2016ssc,Everingham10}, and are iteratively changed based on the output from the respective models.
-The advantage of their approaches is that fewer windows are generated and submitted to the classifier, resulting in lower object classification times.
-The authors also report comparable accuracy compared to their counterparts.
+The advantage of their approaches is that fewer windows are generated and submitted to the classifier, resulting in lower object classification times, while still keeping state-of-the-art results for the accuracy.
 
@@
 
-\noindent This project's goal is to deliver a stand-alone system that can guide a VI user to their destination with minimal user input or intervention.
-A complete system diagram is given is Figure~\ref{fig:control-loop}.
-The system design loop is similar to that of a classical control problem where a controller generates a control signal that drives a component towards some reference point.
-In this case, the reference signal, $r$, is the object the user wishes to find which is achieved by placing the target object within the camera's view.
-Therefore, the goal of the control block, $K$, is to generate guidance instructions, $u$ to drive the user along a search path towards the target object.
-Since we place a human in the control loop, we have an extra block, $H$, that interprets $u$ and executes a physical action, $u^*$, that manipulates the sensor, $P$, that makes a new object observation.
-The new observation is then fed back to the loop and the error signal, $e$, is updated accordingly.
+\noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a VI user to their destination with minimal user input or intervention.
+A complete system diagram is given is Fig.~\ref{fig:control-loop}.
+This closed-loop system is conceptually similar to other classical control problems, where the difference between desired and actual state of a process is used to generate a control signal that changes the process itself.
 
-This work focusses on implementing $K$ and there are 2 points of interest to implementing such a controller successfully.
-Firstly, $K$ must be environment-agnostic, meaning that it cannot be constrained to specific environment since objects are not necessarily placed in the same place in every environment.
-Secondly, the controller must be robust enough to handle a badly interpreted $u$ signal.
-The risk of that happening can be minimised by generating clear and simple signals to help ensure that $u^*$ closely tracks $u$.
+In this case, the reference signal, $r$, is the object the user wishes to capture with the smartphone's camera.
+The goal of the control block, $K$, is to generate human interpretable instructions, $u$, to guide the user towards the target object.
+The process to be controlled involves a human, $H$, who interprets the instruction and executes a physical action, $u^*$, to actually manipulates the smartphone's camera, $P$.
+A new observation, $y$, with the latter is then fed back to the loop and the error signal, $e$, is updated accordingly.
+
+Here we focus in particular on the implementation of the control module $K$.
+Two important points are considered in the design of the controller.
+Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places, unknown a priori.
+Secondly, the controller must be robust enough to handle incorrect interpretations by the human of the instructions $u$.
+This risk can be mitigated by the use of clear and simple instructions that help $u^*$ follow as close as possible $u$.
+The implementation of this controller is discussed in detailed next.
 
@@
 
-Consider the scene in Figure~\ref{fig:route-example} which contains a number of simple, distinct objects (the red boxes).
-The MDP's task is to direct the user to point the camera to the target object (the mug in the bottom-left of Figure~\ref{fig:route-example}).
+Consider the scene in Fig.~\ref{fig:route-example} which contains a number of simple, distinct objects (the red boxes).
+The MDP's task is to direct the user to point the camera to the target object (the mug in the bottom-left of Fig.~\ref{fig:route-example}).
 It does this by inferring the current state by sampling the object currently within the camera's view and generates an action that leads the user to the target object.
@@
 
-The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to benchmark their models.
+The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Fig.~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to benchmark their models.
 The bounding boxes and object labels are used to extract the spatial relationships between the different objects in $\mathbf{O}$.
@@
 
-Figure~\ref{fig:obj-relationships} shows the spatial relationship between a subset of $\mathbf{O}$ (desk, keyboard and mouse).
+Fig.~\ref{fig:obj-relationships} shows the spatial relationship between a subset of $\mathbf{O}$ (desk, keyboard and mouse).
 For example, when the agent is in state $s=\langle{}o=mouse, n, v\rangle$ and searching for a keyboard, there is a strong probability that the target object is $LEFT$ of the mouse.
@@
 
-We incorporated the trained MDP model and policies into an Android app (see Figure~\ref{fig:system-screenshot} for a screenshot).
-This app is responsible for generating the guidance instructions and tracking the agent and sensor ($K$ and $P$ blocks in Figure~\ref{fig:control-loop}) throughout a search session.
+We incorporated the trained MDP model and policies into an Android app (see Fig.~\ref{fig:system-screenshot} for a screenshot).
+This app is responsible for generating the guidance instructions and tracking the agent and sensor ($K$ and $P$ blocks in Fig.~\ref{fig:control-loop}) throughout a search session.
 Tracking the agent's pose allows the app to infer the current state and look up the optimal action to take.
@@
 A generic environment mimicking a typical office desk layout was set up as the experiment environment and contains 7 different objects (i.e.\ encoded QR codes), one of which could be selected for each experiment run.
-See Figure~\ref{fig:env-picture} for a picture of the environment.
+See Fig.~\ref{fig:env-picture} for a picture of the environment.
 
@@
 Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present.
-Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off as the step-limit increases.
+Fig.~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off as the step-limit increases.
 
@@
 
-Figure~\ref{fig:tar-objects} shows the TAR for each object in $\mathbf{O}$.
+Fig.~\ref{fig:tar-objects} shows the TAR for each object in $\mathbf{O}$.
 There are variations the TAR for the different objects, with the smaller objects typically being the hardest to find.
@@
 \noindent The number of steps to the target indicates the number of waypoints the system generated for the participant during the guidance process and is a major indication of system performance, where less waypoints means faster target acquisition and better performance.
-Figure~\ref{fig:nsteps-participants} shows the cumulative distribution of the number of steps to the target for all the participants.
+Fig.~\ref{fig:nsteps-participants} shows the cumulative distribution of the number of steps to the target for all the participants.
 
@@
 %As expected, the number of steps the simulation required on average to find the target object is less than the participants did during the experiments.
-The full set of results for the simulation is given by a frequency mapping of the coincidences between the simulation and experimental data in Figure~\ref{fig:sim-vs-experiment}.
+The full set of results for the simulation is given by a frequency mapping of the coincidences between the simulation and experimental data in Fig.~\ref{fig:sim-vs-experiment}.
 
@@
 
-\noindent The distribution of the total time it took the participants to reach the target object is given in Figure~\ref{fig:time-participants}.
+\noindent The distribution of the total time it took the participants to reach the target object is given in Fig.~\ref{fig:time-participants}.
 We see that the distribution is heavily skewed to the bottom with a long tail.
@@
 %, is far greater than for the number of waypoints they required.
-Indeed, there is not a strong relationship between the number of waypoints a participant required and the time they took to find the target, as showcased by participant $s7$'s wide mean waypoint count and spread in Figure~\ref{fig:nsteps-participants} and the small spread and close-to-average time to target in Figure~\ref{fig:time-participants}.
-Furthermore, the opposite can be observed in participant $s8$'s small spread and low mean waypoint count in Figure~\ref{fig:nsteps-participants} and high spread and high mean time to target in Figure~\ref{fig:time-participants}.
+Indeed, there is not a strong relationship between the number of waypoints a participant required and the time they took to find the target, as showcased by participant $s7$'s wide mean waypoint count and spread in Fig.~\ref{fig:nsteps-participants} and the small spread and close-to-average time to target in Fig.~\ref{fig:time-participants}.
+Furthermore, the opposite can be observed in participant $s8$'s small spread and low mean waypoint count in Fig.~\ref{fig:nsteps-participants} and high spread and high mean time to target in Fig.~\ref{fig:time-participants}.
 

### 2018-11-22 paper.tex
Fixed typo: Figure needs to be spelled out according to their template!

@@
 The work presented here is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone.
-The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017,bellotto2013}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Fig.~\ref{fig:system-use}.
-Schematically, the actuators used in a typical control loop, shown in Fig.~\ref{fig:control-loop}, are replaced by a human.
+The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017,bellotto2013}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}.
+Schematically, the actuators used in a typical control loop, shown in Figure~\ref{fig:control-loop}, are replaced by a human.
 %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
@@
 \noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a VI user to their destination with minimal user input or intervention.
-A complete system diagram is given is Fig.~\ref{fig:control-loop}.
+A complete system diagram is given is Figure~\ref{fig:control-loop}.
 This closed-loop system is conceptually similar to other classical control problems, where the difference between desired and actual state of a process is used to generate a control signal that changes the process itself.
@@
 
-Consider the scene in Fig.~\ref{fig:route-example} which contains a number of simple, distinct objects (the red boxes).
-The MDP's task is to direct the user to point the camera to the target object (the mug in the bottom-left of Fig.~\ref{fig:route-example}).
+Consider the scene in Figure~\ref{fig:route-example} which contains a number of simple, distinct objects (the red boxes).
+The MDP's task is to direct the user to point the camera to the target object (the mug in the bottom-left of Figure~\ref{fig:route-example}).
 It does this by inferring the current state by sampling the object currently within the camera's view and generates an action that leads the user to the target object.
@@
 
-The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Fig.~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to benchmark their models.
+The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to benchmark their models.
 The bounding boxes and object labels are used to extract the spatial relationships between the different objects in $\mathbf{O}$.
@@
 
-Fig.~\ref{fig:obj-relationships} shows the spatial relationship between a subset of $\mathbf{O}$ (desk, keyboard and mouse).
+Figure~\ref{fig:obj-relationships} shows the spatial relationship between a subset of $\mathbf{O}$ (desk, keyboard and mouse).
 For example, when the agent is in state $s=\langle{}o=mouse, n, v\rangle$ and searching for a keyboard, there is a strong probability that the target object is $LEFT$ of the mouse.
@@
 
-We incorporated the trained MDP model and policies into an Android app (see Fig.~\ref{fig:system-screenshot} for a screenshot).
-This app is responsible for generating the guidance instructions and tracking the agent and sensor ($K$ and $P$ blocks in Fig.~\ref{fig:control-loop}) throughout a search session.
+We incorporated the trained MDP model and policies into an Android app (see Figure~\ref{fig:system-screenshot} for a screenshot).
+This app is responsible for generating the guidance instructions and tracking the agent and sensor ($K$ and $P$ blocks in Figure~\ref{fig:control-loop}) throughout a search session.
 Tracking the agent's pose allows the app to infer the current state and look up the optimal action to take.
@@
 A generic environment mimicking a typical office desk layout was set up as the experiment environment and contains 7 different objects (i.e.\ encoded QR codes), one of which could be selected for each experiment run.
-See Fig.~\ref{fig:env-picture} for a picture of the environment.
+See Figure~\ref{fig:env-picture} for a picture of the environment.
 
@@
 Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present.
-Fig.~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off as the step-limit increases.
+Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off as the step-limit increases.
 
@@
 
-Fig.~\ref{fig:tar-objects} shows the TAR for each object in $\mathbf{O}$.
+Figure~\ref{fig:tar-objects} shows the TAR for each object in $\mathbf{O}$.
 There are variations the TAR for the different objects, with the smaller objects typically being the hardest to find.
@@
 \noindent The number of steps to the target indicates the number of waypoints the system generated for the participant during the guidance process and is a major indication of system performance, where less waypoints means faster target acquisition and better performance.
-Fig.~\ref{fig:nsteps-participants} shows the cumulative distribution of the number of steps to the target for all the participants.
+Figure~\ref{fig:nsteps-participants} shows the cumulative distribution of the number of steps to the target for all the participants.
 
@@
 
-\noindent The distribution of the total time it took the participants to reach the target object is given in Fig.~\ref{fig:time-participants}.
+\noindent The distribution of the total time it took the participants to reach the target object is given in Figure~\ref{fig:time-participants}.
 We see that the distribution is heavily skewed to the bottom with a long tail.

### 2018-11-22 paper.tex
Section3 minor typos

@@
 The work presented here is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone.
-The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017,bellotto2013}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}.
+The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017,bellotto2013}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of a user holding the smartphone, as pictured in Figure~\ref{fig:system-use}.
 Schematically, the actuators used in a typical control loop, shown in Figure~\ref{fig:control-loop}, are replaced by a human.
@@
 The goal of the control block, $K$, is to generate human interpretable instructions, $u$, to guide the user towards the target object.
-The process to be controlled involves a human, $H$, who interprets the instruction and executes a physical action, $u^*$, to actually manipulates the smartphone's camera, $P$.
+The process to be controlled involves a human, $H$, who interprets the instruction and executes a physical action, $u^*$, to actually manipulate the smartphone's camera, $P$.
 A new observation, $y$, with the latter is then fed back to the loop and the error signal, $e$, is updated accordingly.
@@
 Two important points are considered in the design of the controller.
-Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places, unknown a priori.
+Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places, with unknown a priori.
 Secondly, the controller must be robust enough to handle incorrect interpretations by the human of the instructions $u$.
-This risk can be mitigated by the use of clear and simple instructions that help $u^*$ follow as close as possible $u$.
+This risk can be mitigated by the use of clear and simple instructions that helps $u^*$ to track $u$ as close as possible.
 The implementation of this controller is discussed in detailed next.

### 2018-11-22 paper.tex
Minor word change to make line-break prettier

@@
 
-\noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a VI user to their destination with minimal user input or intervention.
-A complete system diagram is given is Figure~\ref{fig:control-loop}.
-This closed-loop system is conceptually similar to other classical control problems, where the difference between desired and actual state of a process is used to generate a control signal that changes the process itself.
+\noindent The work presented in this paper is a fundamental step towards an over-arching project's goal to develop a stand-alone system that can guide a VI user to their destination with minimal user input or intervention.
+A complete system diagram is given in Figure~\ref{fig:control-loop}.
+This closed-loop system is conceptually similar to other classical control problems, where the difference between the desired and actual state of a process is used to generate a control signal that changes the process itself.
 

### 2018-11-23 paper.tex
submitted

--- 2018-11-22 paper.tex
@@
 
-%is the design of a guidance system and MDP (the control-block, $K$, pictured in Fig.~\ref{fig:control-loop}) that can drive a user to point a mobile device's camera towards a given point in space in and find a target object.
+%is the design of a guidance system and MDP (the control-block, $K$, pictured in Figure~\ref{fig:control-loop}) that can drive a user to point a mobile device's camera towards a given point in space in and find a target object.
 We also present and discuss preliminary experimental results to show how effective the system is at finding a target.
@@
 For example, some researchers have developed a planning algorithm for a robotic manipulator that performs an optimal object search in a cluttered environment~\cite{dogar2014object}.
-Another team implemented an MDP-based system generating an optimal object search strategy in a room over a belief state of object positions and configurations~\cite{aydemir2011search}.
+Another team implemented an MDP generating an optimal object search strategy in a room over a belief state of object positions and configurations~\cite{aydemir2011search}.
 However, the authors trained their MDP using a custom object-placement and configuration scenario, so their results are sensitive to changes within this distribution.
@@
 
-\noindent The system guides a user by generating a set of waypoints to indicate an area for the user to investigate with the camera and will lead the user to the target object.
-This path is generated one waypoint at a time by the system and is updated with every object observation the user makes after adjusting the camera.
-We modelled the problem using an MDP and the details of the model's design and implementation are discussed in the following sections.
+\noindent Our active search system guides the user by generating a set of waypoints that need to observed by the camera, tracing a path that will eventually lead to the target object.
+Note that the actual location of the latter is {\em unknown}, meaning that the system will guide the user towards the most likely location where to find the object, based on its internal knowledge of spatial relations between objects (e.g.
+a computer is more likely to be above than below a desk).
+This path is generated one waypoint at a time and is updated with every new object observation captured by the camera, or after a re-orientation of the latter beyond a certain angle.
+We tackle the problem using an MDP, the design and implementation of which are discussed in the following sub-sections.
 %For this initial design, the system only works in the pan and tilt dimension and the depth dimension will be added after successful testing of this version of the guidance system.
@@
 However, instead of the traditional, linear grid-world problem, we use the grid in a radial coordinate system which surrounds the user and each grid square represent a pan/tilt angle coordinate.
-See Fig.~\ref{fig:environment} for an example grid.
+See Figure~\ref{fig:environment} for an example grid.
 Since we do not consider the depth dimension yet, each grid square is equidistant from the user and agent.
@@
 
-\noindent An MDP is used to produce a policy that defines a set of optimal actions for an agent to take in any given pre-defined state.
+\noindent An MDP produces a policy of optimal actions for an agent to take in any given pre-defined state.
 In this case, the agent is defined as the guidance system and the policy is used to generate the next waypoint on the search path towards the target object.
-We assume perfect state and transition observability for each timestep and the problem is given by the 5-tuple
+We assume the directly observable states and known state transitions probabilities.
+The MDP can be represented by the following 5-tuple:
 
 \begin{equation}
-  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \text{R}, \gamma), 
+  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \gamma)
 \end{equation}
-where $\text{R}$ is the reward function defining the immediate reward the agent receives for reaching state $s'$ after executing action $a$ in state $s$, $\mathbf{S}$ is a set of possible states the agent can be in and $\mathbf{A}$ is a set of possible actions an agent can take in any given state.
-$\mathbf{T}$ is a set of state transition probabilities defining the probability of transitioning from state $s$ to state $s'$ after executing action $a$ and $\gamma$ is a discount factor which prioritises immediate over long-term rewards.
+where $\mathbf{S}$ is a set of possible agent' states, $\mathbf{A}$ is a set of possible actions an agent can take in any given state, $\mathbf{T}$ is a set of state transition probabilities from state $s$ to state $s'$, with ${s,s'~\in~\mathbf{S}}$, and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a \in \mathbf{A}$ in state $s$.
+The scalar $\gamma$ is a discount factor which prioritises immediate over long-term rewards.
 Each of these elements are defined and discussed next.
@@
 
-\noindent The state is a combination of parameters that defines the agent's world and decision process. The agent's state vector is given by
+\noindent The state is a combination of parameters that defines the agent's world and decision process. Our state vector is defined as follows:
 
 \begin{equation}
-  s = \langle{}o, n, v\rangle, s\in{}\mathbf{S}, 
+  s = \langle o, n, v \rangle, 
 \end{equation}
-where $o$ is the current object in view, $n$ is the number of steps taken since the search started and $v$ is a binary variable that tracks whether a waypoint has been generated in the same pan/tilt position before during the search.
+where $o$ is the current object in viewed by the camera, $n$ is the number of steps taken since the search started, and $v$ is a binary variable that keeps track of whether a waypoint for the current state was already generated during the current object search.
 
@@
 The policy produced by an MDP define the action an agent will take when it finds itself in any given state.
-In this case, the action is the direction the next waypoint should be generated relative to the device's current view pose.
-The actions are defined by
-
-\begin{equation}
-  a = \langle{}s\rangle, a\in{}\mathbf{A},
-\end{equation}
-and the possible actions are
+In this case, the action is the direction of the next waypoint relatively to the current device's pose.
+The possible actions are four:
 
@@
 
-Consider the scene in Figure~\ref{fig:route-example} which contains a number of simple, distinct objects (the red boxes).
-The MDP's task is to direct the user to point the camera to the target object (the mug in the bottom-left of Figure~\ref{fig:route-example}).
-It does this by inferring the current state by sampling the object currently within the camera's view and generates an action that leads the user to the target object.
-The states are sampled and the actions are generated in discretised steps as the user moves the camera's view in the instructed direction.
+To illustrate an example of actions sequence, let us consider the scene in Figure~\ref{fig:route-example}, which contains a number of simple, distinct objects (red boxes).
+The MDP guides the user in pointing the camera to the target object (mug at the bottom-left of the figure).
+It does this by inferring the current state, which depends on the object currently observed by the camera, and generating an action, or instruction, that leads the user to the target object.
+%The states are sampled and the actions are generated in discretised steps as the user moves the camera's view in the instructed direction.
 %This discrete behaviour is similar to a waypoint navigation approach where the user goes from one waypoint to the next, until the user points the camera to target object.
+An action is considered completed, and therefore a new state reached, when the camera has rotated more than a predefined angle or a new object is detected.
 
@@
   \includegraphics[width=0.5\textwidth]{figures/office_desk_example.png}
-  \caption{An example of a guidance strategy the MDP generates. }\label{fig:route-example}
+  \caption{An example action policies generated by the MDP to guide the user in pointing the camera from a random starting object (e.g.
+monitor) to a target object (e.g.
+mug).
+}\label{fig:route-example}
 \end{figure}
@@
 
-\noindent The state transition function, $\mathbf{T}$, defines the probability of the agent transitioning into state $s'$ from state $s$ when taking action $a$, i.e.\ the likelihood of moving to a new pan/tilt position and observing object $o$ after performing action $a$.
-Therefore, $\mathbf{T}$ represents the spatial relationships between the different objects in the environment model.
-Formally, the transition function is defined by
-
-\begin{equation}
-  t=\langle{}s, a, s'\rangle, t\in{}\mathbf{T}.
-\end{equation}
+\noindent The state transition $\mathbf{T}$ defines the probability of the agent switching from state $s$ to state $s'$ due to action $a$, i.e.\ the probability of observing object $o'$ after object $o$ due to a pan/tilt rotation of the camera.
+Therefore, $\mathbf{T}$ represents the spatial relationships between the different objects in our environment model.
+% Formally, the transition function is defined by
+% 
+% \begin{equation}
+%   t=\langle{}s, a, s'\rangle, t\in{}\mathbf{T}.
+% \end{equation}
+These spatial relationships are learned from a dataset during an initial training process, which is discussed more in detail in Section~\ref{sec:training}.
 
@@
 
-\noindent The reward function, $R$, is the immediate reward that the agent receives after transitioning from state $s$ to state $s'$ and is given by
-
-\begin{equation}
-  R\in r(s, s').
-\end{equation}
-
-The goal of the agent is to maximise the cumulative reward it receives and is a very important parameter for producing a good policy that will define the optimal action for the agent to execute for any given state.
-In order to encourage the agent to actively search for the target object, a set of negative rewards must be defined, along with a relatively large positive reward for successfully reaching the target object.
-These parameters must be finely balanced to ensure efficient object search behaviour from the agent.
+\noindent The reward $\mathbf{R}$ is the immediate reward that the agent receives after transitioning from state $s$ to state $s'$.
+% and is given by 
+% 
+% \begin{equation}
+%   R\in r(s, s').
+% \end{equation} 
+% 
+The goal of the agent is to maximise its cumulative reward, therefore this is a very important parameter for producing a good action policy.
+In order to encourage the agent to find the target object as quick as possible, a relatively large positive reward should be assigned for successfully reaching the goal state, and a negative one in any other case.
+These parameters must be finely balanced to ensure an effective object search behaviour.
 
@@
 
-\subsubsection{Model Training}
+This section describe the actual implementation details of the MDP for active object search, including training and software deployment on our smartphone device.
+
+\subsubsection{Training} \label{sec:training}
 
 \noindent A policy that defines the optimal action for an agent to take for any given state is generated through a training process that involves letting the agent explore the entire state-space and iteratively improve its decision function, i.e.\ policy, in order to reach the target state in a way that maximises its cumulative reward.
-This method is called Q-learning and does not require a model of its environment during training.
+This method, called Q-learning~\cite{Watkins1992}, does not require a model of the agent's environment during training.
 
-The agent's target state is any state where $s = \langle{}o=o_{target}, n, v\rangle$.
-This gives a total of 14 terminal states (7$\times$2) per policy, since the target object can can be found at any point in the search or in a position that was previously explored by the agent and user.
-Each target object has its own unique policy file.
-
-The reward function was crafted by hand and the parameters were empirically selected.
-The function values can be found in Table~\ref{tab:rewards}.
-$R$ punishes the agent for every step it takes where it does not find the target object and the negative reward is increased if the agent is taking too long to find the target ($n > n_{\max}$) or when it generates a waypoint in a location that it has generated a waypoint previously ($v = true$).
-Conversely, it gives a significant positive reward when the target object is found.
-
-\begin{table}
-  \centering
-  \caption{The reward functions for the MDP.\ }\label{tab:rewards}
-  \begin{tabular}{cc}
-    \toprule
-    $r(s, s'), s\in\mathbf{S}$ & -1  \\ \midrule
-    $r(n > n_{\max})$ & -10 \\ \midrule
-    $r(v = true)$  & -10 \\ \midrule
-    $r(o = o_{target})$ & 10000 \\ \midrule
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Currently there are 8 objects encoded into the system, including a `nothing' instance where nothing of note is observed.
+Currently there are 7 objects encoded into the system, plus a `nothing' instance where nothing of note is observed.
 Our initial implementation considers a simple office desk scenario containing the following objects:
@@
 
-The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset~\cite{openimages} that consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example) and is primarily aimed toward object recognition researchers to benchmark their models.
-The bounding boxes and object labels are used to extract the spatial relationships between the different objects in $\mathbf{O}$.
-Since the camera perspectives and absolute distances between the objects in the images are not given, we can only extract the relationships in the basic action terms specified in $\mathbf{A}$, e.g.\ we can only say that object 1 is above object 2, but not how far above.
-Our simple action-space and grid environment somewhat compensates for the dataset's lack of complexity.
+The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset~\cite{openimages}, which consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example).
+The dataset is primarily aimed toward object recognition researchers to benchmark their models.
+In our case though, the bounding boxes and object labels are used to extract the spatial relationships between the different objects in $\mathbf{O}$.
+Since the camera perspectives and absolute distances between the objects in the images are not given, we can only extract the relationships in the basic action terms specified in $\mathbf{A}$, e.g.
+we can only say that object 1 is above object 2, but not how far above.
+Our relatively simple action-space is therefore suitable for the dataset's lack of information.
 
@@
 Figure~\ref{fig:obj-relationships} shows the spatial relationship between a subset of $\mathbf{O}$ (desk, keyboard and mouse).
-For example, when the agent is in state $s=\langle{}o=mouse, n, v\rangle$ and searching for a keyboard, there is a strong probability that the target object is $LEFT$ of the mouse.
-The MDP model considers all of the objects' spatial relationships when generating the optimal policy.
+For example, when the agent is in state ${s=\langle o=mouse, n, v \rangle}$ and is searching for the object $o_{target} = keyboard$, there is a strong probability that the target object is on the mouse $LEFT$.
+The MDP of course will consider all of the objects' spatial relationships when generating the optimal policy.
 
@@
   \caption{Examples of the spatial relationships between the desk, keyboard and mouse objects.
-Each square corresponds to the probability of executing the action that square represent (top square for $UP$, etc.)}\label{fig:obj-relationships}
+Each square corresponds to the probability of executing an action (top square for $UP$, left square for $LEFT$, etc.)}\label{fig:obj-relationships}
 \end{figure}
 
-We set the model to track a maximum of of 11 (inclusive) steps to the target, with 11 being the longest possible route on the grid (more details about the grid are in Section~\ref{sec:system-implementation}).
-A search can take longer than 11 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function.
+The agent's target state is then any state where ${s = \langle o=o_{target}, n, v \rangle}$.
+This gives a total of 14 terminal states (7$\times$2) per policy, since the target object can be found at any point in the search or in a position that was previously explored by the user.
+Each target object has its own unique policy file.
+
+The reward function was hand-crafted and the parameters were empirically selected.
+The function values can be found in Table~\ref{tab:rewards}.
+The reward punishes the agent for every step it takes without finding the target object.
+The reward becomes more and more negatives as the agent progresses without finding the target~($n > n_{\max}$) or when it generates a waypoint in a location that was previously visited~($v = true$).
+Conversely, it gives a significant positive reward when the target object is found.
+
+\begin{table}
+  \centering
+  \caption{The reward functions for the MDP.\ }\label{tab:rewards}
+  \begin{tabular}{cc}
+    \toprule
+    $r(o = o_{target})$ & 10000 \\ \midrule
+    $r(v = true)$  & -10 \\ \midrule
+    $r(n > n_{\max})$ & -10 \\ \midrule
+    otherwise $r(\cdot)$ & -1  \\ \midrule
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+We force the MDP to generate a maximum of 11 (inclusive) steps to the target, with 11 being the longest possible route on the action grid (more details about the grid are in Section~\ref{sec:system-implementation}).
+A search could take longer than 11 steps, but the MDP considers that the maximum, which is convenient for keeping a manageable state-space and a simple reward function.
 The MDP therefore has a total of 154 reachable states ($s_{total}=11\times7\times2$).
 
-The lack of absolute spatial information in the OpenImage dataset generates ambiguities which makes it hard for the model to converge to a single, optimal solution.
+The lack of absolute spatial information in the OpenImage dataset generates ambiguities, which makes it hard for the model to converge to a single, optimal solution.
 We therefore could not use the popular value iteration algorithm~\cite{bellman1957markovian} and opted for the state-action-reward-state-action (SARSA) algorithm~\cite{rummery1994line} instead.
-SARSA is an on-policy algorithm that allows us to control the level of exploration vs.\ exploitation that makes it easier to find a solution, but this solution is not guaranteed to be optimal.
+SARSA is an on-policy algorithm that allows us to control the level of exploration vs.\ exploitation that makes it easier to find a solution, although this is not guaranteed to be optimal.
 
-The model is trained until it converges to the optimal policy, or for a total of approximately 17 million episodes.
-The parameter, $\alpha$, that controls the exploration vs.\ exploitation behaviour during training maximises exploration when it is set to $1$ and exploitation when it is $0$.
-We set $\alpha$ to a function that starts at a high exploration value and exponentially changes it behaviour to exploitation as it becomes more trained.
-$\alpha$ is given by
+The MDP is trained until it converges to the optimal policy, or for a total of approximately 17 million episodes.
+The parameter $\alpha$, which controls the exploration vs.\ exploitation behaviour during training, maximises the exploration when set to $1$ and the exploitation when $0$.
+We therefore set $\alpha$ to be a function of the training episodes, starting with a high exploration value and exponentially changing to exploitation as the training progresses:
 
 \begin{equation}
-  \alpha = \exp\Big(\frac{-i}{10s_{total}}\Big) - 0.001,
+  \alpha = \exp\Big(\frac{-i}{10~s_{total}}\Big) - 0.001,
 \end{equation}
@@
 Therefore, a solution can be found in a reasonable amount of time.
-However, it should be noted that adjusting the angle interval, or adding more actions or objects, can easily blow up the size of the state-space.
+However, it should be noted that adjusting the angle interval, or adding more actions or objects, can easily lead to an intractable size of the state-space.
 
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{figures/system_screenshot2.png}
+  \includegraphics[width=0.35\textwidth]{figures/system_screenshot2.png}
   \caption{A screenshot of the guidance interface showing a waypoint (based on an 3D Android model), the object scanner area and the guidance instruction arrows. }\label{fig:system-screenshot}
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/test_env_picture.jpg}
+  \includegraphics[width=0.45\textwidth]{figures/test_env_picture.jpg}
   \caption{A picture of the environment used for the experiments. Each QR code represents an object.}\label{fig:env-picture}
@@
 %As expected, the number of steps the simulation required on average to find the target object is less than the participants did during the experiments.
-The full set of results for the simulation is given by a frequency mapping of the coincidences between the simulation and experimental data in Fig.~\ref{fig:sim-vs-experiment}.
+The full set of results for the simulation is given by a frequency mapping of the coincidences between the simulation and experimental data in Figure~\ref{fig:sim-vs-experiment}.
 
@@
 %, is far greater than for the number of waypoints they required.
-Indeed, there is not a strong relationship between the number of waypoints a participant required and the time they took to find the target, as showcased by participant $s7$'s wide mean waypoint count and spread in Fig.~\ref{fig:nsteps-participants} and the small spread and close-to-average time to target in Fig.~\ref{fig:time-participants}.
-Furthermore, the opposite can be observed in participant $s8$'s small spread and low mean waypoint count in Fig.~\ref{fig:nsteps-participants} and high spread and high mean time to target in Fig.~\ref{fig:time-participants}.
+Indeed, there is not a strong relationship between the number of waypoints a participant required and the time they took to find the target, as showcased by participant $s7$'s wide mean waypoint count and spread in Figure~\ref{fig:nsteps-participants} and the small spread and close-to-average time to target in Figure~\ref{fig:time-participants}.
+Furthermore, the opposite can be observed in participant $s8$'s small spread and low mean waypoint count in Figure~\ref{fig:nsteps-participants} and high spread and high mean time to target in Figure~\ref{fig:time-participants}.
 

### 2018-11-23 paper.tex

@@
 \author{
-  \authorname{Anon McAnon{\sup{1}}}
-  \affiliation{\sup{1}Anon University of Anon, Anonville, Anonistan}
-  \email{anon.anon@anon.com}
+  \authorname{~}%Anon McAnon{\sup{1}}}
+  \affiliation{~}%\sup{1}Anon University of Anon, Anonville, Anonistan}
+  \email{~}%anon.anon@anon.com}
 %\affiliation{\sup{1}Lincoln Centre for Autonomous Systems (L-CAS), University of Lincoln, Lincoln, UK}
@@
 
-This section describe the actual implementation details of the MDP for active object search, including training and software deployment on our smartphone device.
+This section describe the actual implementation details of the MDP for active object search, including initial training and software deployment on our smartphone device.
 
@@
 \noindent A policy that defines the optimal action for an agent to take for any given state is generated through a training process that involves letting the agent explore the entire state-space and iteratively improve its decision function, i.e.\ policy, in order to reach the target state in a way that maximises its cumulative reward.
-This method, called Q-learning~\cite{Watkins1992}, does not require a model of the agent's environment during training.
+This method, called Q-learning~\cite{Watkins1992}, does not require a model of the agent's environment during training, allowing the policy to be used in many different scenarios.
 
@@
 The lack of absolute spatial information in the OpenImage dataset generates ambiguities, which makes it hard for the model to converge to a single, optimal solution.
-We therefore could not use the popular value iteration algorithm~\cite{bellman1957markovian} and opted for the state-action-reward-state-action (SARSA) algorithm~\cite{rummery1994line} instead.
+We therefore opted to use the more conservative state-action-reward-state-action (SARSA) algorithm~\cite{rummery1994line}.
 SARSA is an on-policy algorithm that allows us to control the level of exploration vs.\ exploitation that makes it easier to find a solution, although this is not guaranteed to be optimal.
@@
 
-We incorporated the trained MDP model and policies into an Android app (see Figure~\ref{fig:system-screenshot} for a screenshot).
-This app is responsible for generating the guidance instructions and tracking the agent and sensor ($K$ and $P$ blocks in Figure~\ref{fig:control-loop}) throughout a search session.
-Tracking the agent's pose allows the app to infer the current state and look up the optimal action to take.
+We incorporated the trained MDP-based controller into an app (see Figure~\ref{fig:system-screenshot}) for an Asus ZenPhone AR smartphone, running Android 7.0, with the Google's augmented reality toolkit (ARCore), which provides the necessary 3D pose of the device.
+No further software or hardware modifications were required.
+This app is responsible for generating the guidance instructions and tracking the camera sensor ($K$ and $P$ blocks in Figure~\ref{fig:control-loop}) throughout a search session.
+Tracking the camera's pose allows the app to infer the current state and choose the optimal action to take next.
 
@@
 The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes.
-In this setup, the policy action is interpreted by the app and a new search waypoint is generated in the centre of the cell specified by the action, e.g.\ an `$UP$' action will generate a waypoint one grid cell up from where the user is currently pointing the camera.
+A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation.
+Note that this cell is not part of the MDP' state: this radial grid is only used to discretised the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions.
 The app's guidance system then uses the new waypoint's location to provide the user with guidance instructions.
@@
 This scanner area is $300\times300$ pixels and scans for barcodes without causing any frame-rate drops.
-
-The app was developed on and experimented with an Asus ZenPhone AR running Android version 7.0 with Google's augmented reality toolkit (ARCore) enabled for measurement and device tracking.
-No hardware or software modifications were required.
 

### 2018-11-23 paper.tex
Minor typo changes

@@
 Secondly, the controller must be robust enough to handle incorrect interpretations by the human of the instructions $u$.
-This risk can be mitigated by the use of clear and simple instructions that help $u^*$ follow as close as possible $u$.
-The implementation of this controller is discussed in detailed next.
+This risk can be mitigated by the use of clear and simple instructions that helps $u$ track $u^*$ as closely as possible.
+The implementation of this controller is discussed in detail next.
 
@@
 \noindent Our active search system guides the user by generating a set of waypoints that need to observed by the camera, tracing a path that will eventually lead to the target object.
-Note that the actual location of the latter is {\em unknown}, meaning that the system will guide the user towards the most likely location where to find the object, based on its internal knowledge of spatial relations between objects (e.g.
-a computer is more likely to be above than below a desk).
+Note that the actual location of the latter is {\em unknown}, meaning that the system will guide the user towards the most likely location where to find the object, based on its internal knowledge of spatial relations between objects (e.g.\ a computer is more likely to be above than below a desk).
 This path is generated one waypoint at a time and is updated with every new object observation captured by the camera, or after a re-orientation of the latter beyond a certain angle.

### 2018-11-23 paper.tex

--- 2018-11-23 paper.tex
@@
 The reward punishes the agent for every step it takes without finding the target object.
-The reward becomes more and more negatives as the agent progresses without finding the target~($n > n_{\max}$) or when it generates a waypoint in a location that was previously visited~($v = true$).
+The reward becomes more and more negatives as the agent progresses without finding the target~($n > n_{\max}$) or when it generates the same waypoint more than once~($v = true$) during the same search.
 Conversely, it gives a significant positive reward when the target object is found.
@@
 A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation.
-Note that this cell is not part of the MDP' state: this radial grid is only used to discretised the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions.
-The app's guidance system then uses the new waypoint's location to provide the user with guidance instructions.
-The grid is generated at the app's start-up and remains constant throughout the app's lifetime.
-The policy actions, and waypoints by extension, are given in relative to the user's current viewing pan/tilt position.
+Note that this cell is not part of the MDP' state: the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions.
+The grid is generated at the app's start-up and remains constant throughout its lifetime.
+The app then uses the new waypoint's location to provide the user with guidance instructions.
+The policy actions, and waypoints by extension, are given relatively to the current camera's pan-tilt orientation.
 The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.

### 2018-11-23 paper.tex
last version

@@
   \includegraphics[width=0.35\textwidth]{figures/system_screenshot2.png}
-  \caption{A screenshot of the guidance interface showing a waypoint (based on an 3D Android model), the object scanner area and the guidance instruction arrows. }\label{fig:system-screenshot}
+  \caption{A screenshot of the guidance interface showing an example of guidance instructions towards a waypoint and the QR-object scanner area.}\label{fig:system-screenshot}
 \end{figure}
@@
 The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes.
+The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.
 A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation.
@@
 The policy actions, and waypoints by extension, are given relatively to the current camera's pan-tilt orientation.
-The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.
 
-By recording the previous positions and waypoint locations the app generated, it can infer the state values for $v$ and $n$.
-Furthermore, the camera provides the ID of the object in view, populating $o$ in the state.
-A real-time object detector was not used in this system to avoid unnecessary complexity and processing overhead and encoded QR codes and barcode scanner library were used to simulate object detection instead.
+By recording the previous positions and waypoint locations, the system can infer the state values for $n$ and $v$ described in Section~\ref{sec:states}.
+Furthermore, the camera provides the ID of current object in view, which is assigned to the state variable $o$.
+As explained in the next section, we did not use a real object detector in our experiments, but we simulated it with 7 different QR codes, one for each object's type, and a camera-based QR scanner from the Android's machine learning API (MLKit).
 
-The QR code scanner requires raw image data.
-To avoid scanning multiple QR codes and using excess processing power by scanning large images, we only used the centre part of the screen to scan for a barcode.
-This scanner area is $300\times300$ pixels and scans for barcodes without causing any frame-rate drops.
+The QR scanner requires raw image data.
+To avoid scanning multiple QR codes and speed up the image processing, we only used the central part of the camera's frame, which is $300\times300$ pixels.
+This choice defines also the precision required in pointing the camera towards the object (see also Figure~\ref{fig:system-screenshot}).
 

### 2018-11-23 paper.tex
Added navigation instruction paragraph

--- 2018-11-23 paper.tex
@@
 The app then uses the new waypoint's location to provide the user with guidance instructions.
-The policy actions, and waypoints by extension, are given relatively to the current camera's pan-tilt orientation.
+The policy actions, and waypoints by extension, are given relative to the current camera's pan-tilt orientation.
 The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.
+
+The position of the waypoint is given to the user by a set of guidance instructions (the arrows seen on-screen in Figure~\ref{fig:system-screenshot}) in terms of the actions defined in $\textbf{A}$.
+This might seem like an unnecessary extra step, but since we are designing this system for VI users who are limited to audio instructions.
+This makes it necessary to split the instructions up into separate channels that can be communicated more simply, especially so when one considers the bandwidth limitations of a human's audio channel as compared to the visual one.
 

### 2018-11-23 paper.tex
Edits to instructions paragraph

@@
 The position of the waypoint is given to the user by a set of guidance instructions (the arrows seen on-screen in Figure~\ref{fig:system-screenshot}) in terms of the actions defined in $\textbf{A}$.
-This might seem like an unnecessary extra step, but since we are designing this system for VI users who are limited to audio instructions.
-This makes it necessary to split the instructions up into separate channels that can be communicated more simply, especially so when one considers the bandwidth limitations of a human's audio channel as compared to the visual one.
+This might seem like an unnecessary extra step, but this system is designed for VI users who are limited to audio instructions, which makes it necessary to split the instructions up into separate channels that can be communicated more simply.
+This requirement becomes clear when one considers the bandwidth limitations of a human's audio channel as compared to the visual one.
 

### 2018-11-23 paper.tex

--- 2018-11-23 paper.tex
@@
 
+The position of the waypoint is given to the user by a set of guidance instructions (the arrows seen on-screen in Figure~\ref{fig:system-screenshot}) in terms of the actions defined in $\textbf{A}$.
+This might seem like an unnecessary extra step, but this system is designed for VI users who are limited to audio instructions, which makes it necessary to split the instructions up into separate channels that can be communicated more simply.
+This requirement becomes clear when one considers the bandwidth limitations of a human's audio channel as compared to the visual one.
+
 By recording the previous positions and waypoint locations, the system can infer the state values for $n$ and $v$ described in Section~\ref{sec:states}.

### 2018-12-22 review_edition/reviewed.tex
Added review suggestions

--- 2018-11-23 paper.tex
@@
 
-\title{Active Object Search with a Mobile Device for the Visually Impaired}
+\title{Active Object Search with a Mobile Device for People with Visual Impairments}
 
 \author{
-  \authorname{~}%Anon McAnon{\sup{1}}}
-  \affiliation{~}%\sup{1}Anon University of Anon, Anonville, Anonistan}
-  \email{~}%anon.anon@anon.com}
-%\affiliation{\sup{1}Lincoln Centre for Autonomous Systems (L-CAS), University of Lincoln, Lincoln, UK}
-%\email{jlock@lincoln.ac.uk}
+  \authorname{Jacobus C. Lock{\sup{1}}, Grzegorz Cielniak\sup{1}, Nicola Bellotto\sup{1}}
+  \affiliation{\sup{1}Lincoln Centre for Autonomous Systems (L-CAS), University of Lincoln, Lincoln, UK}
+  \email{\{jlock, gcielniak, nbellotto\}@lincoln.ac.uk}
 }
@@
 
-\abstract{Modern smartphones can provide a multitude of services to assist people with visual impairments.
-The cameras embedded in these mobile devices, in particular, can be useful for many tasks, like reading signs or searching for objects in unknown environments.
-Although previous research in computer vision has looked at ways to solve these tasks by processing the video frames of the mobile camera, very little work has been done in {\em actively} guiding the user towards specific points of interest that maximise the effectiveness of the underlying visual algorithms.
-In this paper, we propose a control algorithm based on a Markov Decision Process (MDP) that generates real-time instructions to guide a user searching for a target object with a smartphone's camera.
-The solution is part of a more general active vision application for the visually impaired.
-An initial implementation of the system on an Android smartphone was experimentally evaluated with sighted participants to determine the performance of the control algorithm.
-The results show the effectiveness of our solution and its potential application to help the visually impaired find objects in unknown environments.}
+\abstract{Modern smartphones can provide a multitude of services to assist people with visual impairments, and their cameras in particular can be useful for assisting with tasks, such as reading signs or searching for objects in unknown environments.
+Previous research has looked at ways to solve these problems by processing the camera's video feed, but very little work has been done in {\em actively} guiding the user towards specific points of interest, maximising the effectiveness of the underlying visual algorithms.
+In this paper, we propose a control algorithm based on a Markov Decision Process that uses a smartphone's camera to generate real-time instructions to guide a user towards a target object.
+The solution is part of a more general active vision application for people with visual impairments.
+An initial implementation of the system on a smartphone was experimentally evaluated with participants with healthy eyesight to determine the performance of the control algorithm.
+The results show the effectiveness of our solution and its application to help people with visual impairments find objects in unknown environments.}
 
@@
 
-\noindent It is estimated that almost half a billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives.
+\noindent It is estimated that almost half a billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more independent lives.
 Modern improvements in mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem.
-The work presented here is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone.
+The work presented here is part of a project to assist people with vision impairments to navigate and find objects in unknown environments with the aid of a smartphone.
 The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017,bellotto2013}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}.
-Schematically, the actuators used in a typical control loop, shown in Figure~\ref{fig:control-loop}, are replaced by a human.
-%This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
+This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
 
@@
   \centering
-  \includegraphics[width=0.38\textwidth]{figures/system_use.png}
+  \includegraphics[width=0.38\textwidth]{../figures/system_use.png}
   \caption{The system in use during an experiment. }\label{fig:system-use}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
-  \caption{System control loop: $r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation.
-$K$, $H$ and $P$ are the control, human and sensor blocks respectively.
-}\label{fig:control-loop}
 \end{figure}
@@
 
-\noindent Assistive vision and guidance for the VI is a growing research area.
+\noindent Assistive vision and guidance for people living with vision impairments is a growing research area.
 In recent years, the increase in mobile processing power and computer vision improvements have led to research in the use of smartphone cameras to augment or enhance a user's vision and help them find objects or other points of interest.
@@
 The VizWiz has the advantage of being fairly robust and is able to classify a great deal of objects with little effort from the user and can provide natural, human-generated and curated directions.
-However, this approach does not enhance user independence, since the VI person is now beholden to an online worker instead of a relative, friend or bystander.
+However, this approach does not enhance user independence, since a person with vision impairments is now beholden to an online worker instead of a relative, friend or bystander.
 Furthermore, a good internet connection is required on the device, possibly limiting its use in some poor-reception areas.
@@
 Two research teams have recently implemented an active object search strategy into their image classifiers~\cite{caicedo2015active,gonzalez2015active}.
-Their approaches use different methods but conceptually similar models to generate windows of interest for visual classification.
+Their approaches use different methods, but conceptually similar models to generate windows of interest for visual classification.
 The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets~\cite{song2016ssc,Everingham10}, and are iteratively changed based on the output from the respective models.
-The advantage of their approaches is that fewer windows are generated and submitted to the classifier, resulting in lower object classification times, while still keeping state-of-the-art results for the accuracy.
+The advantage of their approaches is that fewer windows are generated and submitted to the classifier, resulting in lower object classification times while still keeping state-of-the-art results for accuracy.
 
@@
 In summary, much research has been conducted on recognition of and guidance towards target objects, including active vision solutions for image classifiers and robotic systems.
-However, to our knowledge, no previous work has been done on {\em active} object search and guidance for humans, which would especially benefit VI users.
+However, to our knowledge, no previous work has been done on {\em active} object search and guidance for humans, which would especially benefit people with vision impairments.
 In this paper, we implement such an active vision system with a human in the loop
@@
 
-\noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a VI user to their destination with minimal user input or intervention.
+\noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a user living with vision impairments to their destination with minimal user input or intervention.
 A complete system diagram is given is Figure~\ref{fig:control-loop}.
 This closed-loop system is conceptually similar to other classical control problems, where the difference between desired and actual state of a process is used to generate a control signal that changes the process itself.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{../figures/control_loop.png}
+  \caption{System control loop: $r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation.
+$K$, $H$ and $P$ are the control, human and sensor blocks respectively.
+}\label{fig:control-loop}
+\end{figure}
 
@@
 The process to be controlled involves a human, $H$, who interprets the instruction and executes a physical action, $u^*$, to actually manipulate the smartphone's camera, $P$.
-A new observation, $y$, with the latter is then fed back to the loop and the error signal, $e$, is updated accordingly.
+A new observation, $y$, with the camera is then fed back to the loop and the error signal, $e$, is updated accordingly.
 
@@
 Two important points are considered in the design of the controller.
-Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places, unknown a priori.
+Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places with unknown a priori.
 Secondly, the controller must be robust enough to handle incorrect interpretations by the human of the instructions $u$.
+Since each person interprets audio signals differently (modelled by the transformation block $H$), this is an important consideration.
+For example, one person might interpret and execute an `UP' instruction correctly (i.e.
+$u\approx u^*$), while another might interpret it correctly, but execute an incorrect action.
 This risk can be mitigated by the use of clear and simple instructions that helps $u$ track $u^*$ as closely as possible.
@@
 
-\noindent Our active search system guides the user by generating a set of waypoints that need to observed by the camera, tracing a path that will eventually lead to the target object.
-Note that the actual location of the latter is {\em unknown}, meaning that the system will guide the user towards the most likely location where to find the object, based on its internal knowledge of spatial relations between objects (e.g.\ a computer is more likely to be above than below a desk).
+\noindent Our active search system guides the user by generating a set of waypoints that need to be observed by the camera, tracing a path that will eventually lead to the target object.
+Note that the actual location of the latter is {\em unknown}, meaning that the system will guide the user towards the most likely location where the object might be found, based on its internal knowledge of spatial relations between objects (e.g.\ a computer monitor is more likely to be above than below a desk).
 This path is generated one waypoint at a time and is updated with every new object observation captured by the camera, or after a re-orientation of the latter beyond a certain angle.
@@
 In this case, the agent is defined as the guidance system and the policy is used to generate the next waypoint on the search path towards the target object.
-We assume the directly observable states and known state transitions probabilities.
-The MDP can be represented by the following 5-tuple:
+We assume fully observable states and known state transitions probabilities.
+The MDP is represented by the 5-tuple
 
 \begin{equation}
-  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \gamma)
+  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \gamma),
 \end{equation}
-where $\mathbf{S}$ is a set of possible agent' states, $\mathbf{A}$ is a set of possible actions an agent can take in any given state, $\mathbf{T}$ is a set of state transition probabilities from state $s$ to state $s'$, with ${s,s'~\in~\mathbf{S}}$, and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a \in \mathbf{A}$ in state $s$.
-The scalar $\gamma$ is a discount factor which prioritises immediate over long-term rewards.
+where $\mathbf{S}$ is a set of possible agent' states, $\mathbf{A}$ is a set of possible actions the agent can take in any given state, $\mathbf{T}$ is a set of state transition probabilities from state $s$ to state $s'$, with ${s,s'~\in~\mathbf{S}}$, and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a \in \mathbf{A}$ in state $s$.
+The scalar $\gamma$ is a discount factor which prioritises immediate over long-term rewards and affects the model's convergence rate.
 Each of these elements are defined and discussed next.
@@
 
-\noindent The state is a combination of parameters that defines the agent's world and decision process. Our state vector is defined as follows:
+\noindent The state is a combination of parameters that defines the agent's world and decision process. Our state vector is defined as
 
@@
 
-The policy produced by an MDP define the action an agent will take when it finds itself in any given state.
+The policy produced by an MDP define the action the agent will take when it finds itself in any given state.
 In this case, the action is the direction of the next waypoint relatively to the current device's pose.
-The possible actions are four:
+The possible actions are given by
 
@@
 To illustrate an example of actions sequence, let us consider the scene in Figure~\ref{fig:route-example}, which contains a number of simple, distinct objects (red boxes).
-The MDP guides the user in pointing the camera to the target object (mug at the bottom-left of the figure).
+The MDP guides the user in pointing the camera to the target object (the mug at the bottom-left of the figure).
 It does this by inferring the current state, which depends on the object currently observed by the camera, and generating an action, or instruction, that leads the user to the target object.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/office_desk_example.png}
+  \includegraphics[width=0.5\textwidth]{../figures/office_desk_example.png}
   \caption{An example action policies generated by the MDP to guide the user in pointing the camera from a random starting object (e.g.
@@
 % 
-The goal of the agent is to maximise its cumulative reward, therefore this is a very important parameter for producing a good action policy.
-In order to encourage the agent to find the target object as quick as possible, a relatively large positive reward should be assigned for successfully reaching the goal state, and a negative one in any other case.
-These parameters must be finely balanced to ensure an effective object search behaviour.
+The goal of the agent is to maximise its cumulative reward and it is very important to fine-tune $\mathbf{R}$ correctly in order to produce an effective action policy.
+In order to encourage the agent to find the target object as fast as possible, a relatively large positive reward should be assigned for successfully reaching the goal state, and a negative one in any other case.
+These parameters must be finely balanced to ensure effective object search behaviour.
 
@@
   \begin{aligned}
-    o\in \mathbf{O} = \{monitor, mouse, keyboard, window,\\mug, stationary, desk, nothing\}.
+    o\in \mathbf{O} = \{monitor, mouse, keyboard, window,\\mug, stationery, desk, nothing\}.
   \end{aligned}
@@
     \centering
-    \includegraphics[width=0.4\textwidth]{figures/desk_example.png}
+    \includegraphics[width=0.4\textwidth]{../figures/desk_example.png}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=0.4\textwidth]{figures/mug_example.png}
+    \includegraphics[width=0.4\textwidth]{../figures/mug_example.png}
   \end{subfigure}
@@
 Figure~\ref{fig:obj-relationships} shows the spatial relationship between a subset of $\mathbf{O}$ (desk, keyboard and mouse).
-For example, when the agent is in state ${s=\langle o=mouse, n, v \rangle}$ and is searching for the object $o_{target} = keyboard$, there is a strong probability that the target object is on the mouse $LEFT$.
+For example, when the agent is in state ${s=\langle o=mouse, n, v \rangle}$ and is searching for the object $o_{target} = keyboard$, there is a strong probability that the target object is on the mouse's $LEFT$.
 The MDP of course will consider all of the objects' spatial relationships when generating the optimal policy.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/object_relationships.png}
+  \includegraphics[width=0.5\textwidth]{../figures/object_relationships.png}
   \caption{Examples of the spatial relationships between the desk, keyboard and mouse objects.
@@
 The reward punishes the agent for every step it takes without finding the target object.
-The reward becomes more and more negatives as the agent progresses without finding the target~($n > n_{\max}$) or when it generates the same waypoint more than once~($v = true$) during the same search.
+The reward becomes increasingly negatives as the agent progresses without finding the target~($n > n_{\max}$) or when it generates the same waypoint more than once~($v = true$) during the same search.
 Conversely, it gives a significant positive reward when the target object is found.
@@
 \end{equation}
-where $i$ is the episode index.  $\gamma$ is set to 0.95 to prioritise long-term reward.
+where $i$ is the episode index.  $\gamma$ is set to 0.95 to prioritise long-term reward and guarantee convergence.
 
@@
 
-We incorporated the trained MDP-based controller into an app (see Figure~\ref{fig:system-screenshot}) for an Asus ZenPhone AR smartphone, running Android 7.0, with the Google's augmented reality toolkit (ARCore), which provides the necessary 3D pose of the device.
+We incorporated the trained MDP-based controller into an app (see Figure~\ref{fig:system-screenshot}) for an Asus ZenPhone AR smartphone, running Android 7.0, with Google's augmented reality toolkit (ARCore), which provides the necessary 3D pose of the device.
 No further software or hardware modifications were required.
@@
   \centering
-  \includegraphics[width=0.35\textwidth]{figures/system_screenshot2.png}
+  \includegraphics[width=0.35\textwidth]{../figures/system_screenshot2.png}
   \caption{A screenshot of the guidance interface showing an example of guidance instructions towards a waypoint and the QR-object scanner area.}\label{fig:system-screenshot}
@@
 The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.
-A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation.
-Note that this cell is not part of the MDP' state: the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions.
+A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the camera's current orientation.
+Note that this cell is not part of the MDP's state and the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variation between subsequent actions.
 The grid is generated at the app's start-up and remains constant throughout its lifetime.
 The app then uses the new waypoint's location to provide the user with guidance instructions.
-The policy actions, and waypoints by extension, are given relatively to the current camera's pan-tilt orientation.
+The policy actions, and waypoints by extension, are given relative to the current camera's pan-tilt orientation.
+The grid is wrapped, so if a waypoint's location exceeds the \SI{120}{\degree} limit, the waypoint is generated at the opposite side of the grid instead, limiting the search space to a \SI{120}{\degree}$\times$\SI{120}{\degree} area.
 
 The position of the waypoint is given to the user by a set of guidance instructions (the arrows seen on-screen in Figure~\ref{fig:system-screenshot}) in terms of the actions defined in $\textbf{A}$.
-This might seem like an unnecessary extra step, but this system is designed for VI users who are limited to audio instructions, which makes it necessary to split the instructions up into separate channels that can be communicated more simply.
-This requirement becomes clear when one considers the bandwidth limitations of a human's audio channel as compared to the visual one.
+This might seem like an unnecessary extra step, but this system is designed for user with vision impairments who are limited to audio instructions, which makes it necessary to split the instructions up into separate channels that can be communicated more simply.
+This requirement becomes clear when one considers the bandwidth limitations of a person's audio channel compared to the visual one.
+To clarify, the arrows were used for debugging and experimentation and they will be translated into audio signals once the audio interface is implemented.
 
 By recording the previous positions and waypoint locations, the system can infer the state values for $n$ and $v$ described in Section~\ref{sec:states}.
-Furthermore, the camera provides the ID of current object in view, which is assigned to the state variable $o$.
-As explained in the next section, we did not use a real object detector in our experiments, but we simulated it with 7 different QR codes, one for each object's type, and a camera-based QR scanner from the Android's machine learning API (MLKit).
+Furthermore, the camera provides the ID of the object currently within view, which is assigned to the state variable $o$.
+As explained in the next section, we did not use a real object detector in our experiments, but we simulated it with 7 different QR codes, one for each unique object, and a camera-based QR code scanner from Android's machine learning API (MLKit).
 
@@
 To avoid scanning multiple QR codes and speed up the image processing, we only used the central part of the camera's frame, which is $300\times300$ pixels.
-This choice defines also the precision required in pointing the camera towards the object (see also Figure~\ref{fig:system-screenshot}).
+This choice also defines the precision required in pointing the camera towards the object (see also Figure~\ref{fig:system-screenshot}).
 
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{figures/test_env_picture.jpg}
+  \includegraphics[width=0.45\textwidth]{../figures/test_env_picture.jpg}
   \caption{A picture of the environment used for the experiments. Each QR code represents an object.}\label{fig:env-picture}
@@
 The participants were left to repeat this process until we recorded 10 searches per object, giving us a total number of 70 recorded search samples per participant.
-We tested a total of 10 different participants (sex: 8 M, 2 F;\@ age: $\mu$ 31.2 years, $\sigma$ 8 years), most of which were sourced from our laboratory with none having any disabilities or handicaps.
+We tested a total of 10 different participants (sex: 8 M, 2 F;\@ age: $\mu$ 31.2 years, $\sigma$ 8 years), most of whom were sourced from our laboratory.
 This gives our dataset a total of 700 search samples.
@@
 The results for each individual participant is presented in Table~\ref{tab:results-full} and Table~\ref{tab:results-summary} gives the results across all of the participants.
-To provide a baseline measure for the ideal case, we ran a number of simulations in an environment mimicking the experiment setup with an agent that perfectly executes the policy, i.e.\ $u=u^*$.
+To provide a baseline measure for the ideal case, we ran a number of simulations in an environment mimicking the experiment setup with user that perfectly executes the policy, i.e.\ $u=u^*$.
 The TAR and steps to target results for the simulation are included in Table~\ref{tab:results-summary}.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/cdf_tar_limit.png}
+  \includegraphics[width=0.5\textwidth]{../figures/cdf_tar_limit.png}
   \caption{The distribution of the TAR as a function of the step limit for a search. The `x' indicates the cases that exceeded the 15-step limit. }\label{fig:tar-steps}
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{figures/tar_objects.png}
+  \includegraphics[width=0.45\textwidth]{../figures/tar_objects.png}
   \caption{The TAR for each of the objects within $\mathbf{O}$. }\label{fig:tar-objects}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/cdf_total_steps.png}
+  \includegraphics[width=0.5\textwidth]{../figures/cdf_total_steps.png}
   \caption{The cumulative distribution of the participants' number of steps taken to find a target object. }\label{fig:nsteps-participants}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/cdf_total_time.png}
+  \includegraphics[width=0.5\textwidth]{../figures/cdf_total_time.png}
   \caption{The cumulative distribution of the participants' time taken to find a target object. }\label{fig:time-participants}
@@
 In comparison to the VizWiz system~\cite{bigham2010vizwiz} (mean 92s, standard deviation 37.7s), our results look very reasonable.
-However, these results may greatly change when we test the system with VI participants.
+However, these results may greatly change when we test the system with participants with vision impairments.
 
@@
 
-\noindent In this work we presented and tested an MDP-based system to guide a visually impaired (VI) person towards a target object with no apriori knowledge of the environment.
+\noindent In this work we presented and tested an MDP-based system to guide a person with vision impairments towards a target object with no apriori knowledge of the environment.
 We implemented the system in an Android app that we tested with a small group of sighted people to determine its viability and effectiveness at guiding a user to manipulating a camera and finding a target object.

### 2018-12-22 paper.tex

@@
 
-\noindent To test the effectiveness of our MDP and its policies, we designed a set of experiments that determined how effective the system is at directing a participant to point the device's camera towards a target object.
-This section discusses the experiments and their results.
+\noindent To test the effectiveness of our MDP and its policies, we designed a set of experiments to determine how effective the system is at guiding the participant in pointing the camera towards a target object.
+This section presents the experiments and following results.
 

### 2018-12-27 review_edition/reviewed.tex
Some revisions up to sec 4 (included). In particular, restructured 4.2.2 (now 4.2.2 and 4.2.3).

@@
 \usepackage{apalike}
+\usepackage{balance}
 
@@
 
-\title{Active Object Search with a Mobile Device for People with Visual Impairments}
+\title{Active Object Search with a Mobile Device\\for People with Visual Impairments}
 
@@
 The work presented here is part of a project to assist people with vision impairments to navigate and find objects in unknown environments with the aid of a smartphone.
-The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017,bellotto2013}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}.
-This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
+The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}, expanding upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
 
@@
   \centering
-  \includegraphics[width=0.38\textwidth]{../figures/system_use.png}
+  \includegraphics[width=0.85\columnwidth]{../figures/system_use.png}
   \caption{The system in use during an experiment. }\label{fig:system-use}
@@
 
-\noindent Assistive vision and guidance for people living with vision impairments is a growing research area.
+\noindent Assistive technology for people living with vision impairments is a growing research area~\cite{Manduchi2012,khoo2016multimodal}.
 In recent years, the increase in mobile processing power and computer vision improvements have led to research in the use of smartphone cameras to augment or enhance a user's vision and help them find objects or other points of interest.
@@
 Two research teams have recently implemented an active object search strategy into their image classifiers~\cite{caicedo2015active,gonzalez2015active}.
-Their approaches use different methods, but conceptually similar models to generate windows of interest for visual classification.
+Their approaches use different methods but conceptually similar models to generate windows of interest for visual classification.
 The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets~\cite{song2016ssc,Everingham10}, and are iteratively changed based on the output from the respective models.
@@
 
-\noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a user living with vision impairments to their destination with minimal user input or intervention.
+\noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a person with vision impairments to his/her destination with minimal user input or intervention.
 A complete system diagram is given is Figure~\ref{fig:control-loop}.
@@
 Two important points are considered in the design of the controller.
-Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places with unknown a priori.
-Secondly, the controller must be robust enough to handle incorrect interpretations by the human of the instructions $u$.
-Since each person interprets audio signals differently (modelled by the transformation block $H$), this is an important consideration.
+Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places with unknown a~priori information.
+Secondly, since each person could interpret the instruction $u$ differently (i.e.
+different transformation block $H$), the controller must be robust enough to handle such incorrect interpretations.
 For example, one person might interpret and execute an `UP' instruction correctly (i.e.
-$u\approx u^*$), while another might interpret it correctly, but execute an incorrect action.
-This risk can be mitigated by the use of clear and simple instructions that helps $u$ track $u^*$ as closely as possible.
+$u \backsimeq u^*$), while another might interpret it correctly, but execute the wrong action.
+This risk can be mitigated by the use of clear and simple instructions that helps $u^*$ be as close as possible to $u$.
 The implementation of this controller is discussed in detail next.
@@
 where $\mathbf{S}$ is a set of possible agent' states, $\mathbf{A}$ is a set of possible actions the agent can take in any given state, $\mathbf{T}$ is a set of state transition probabilities from state $s$ to state $s'$, with ${s,s'~\in~\mathbf{S}}$, and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a \in \mathbf{A}$ in state $s$.
-The scalar $\gamma$ is a discount factor which prioritises immediate over long-term rewards and affects the model's convergence rate.
+The scalar $\gamma$ is a discount factor that prioritises immediate over long-term rewards and which affects the model's convergence rate~\cite{Russell2009}.
 Each of these elements are defined and discussed next.
@@
 
-The policy produced by an MDP define the action the agent will take when it finds itself in any given state.
+The policy produced by an MDP defines the action the agent will take when it finds itself in any given state.
 In this case, the action is the direction of the next waypoint relatively to the current device's pose.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{../figures/office_desk_example.png}
-  \caption{An example action policies generated by the MDP to guide the user in pointing the camera from a random starting object (e.g.
+  \includegraphics[width=\columnwidth]{../figures/office_desk_example.png}
+  \caption{Example of action policies generated by the MDP to guide the user in pointing the camera from a random starting object (e.g.
 monitor) to a target object (e.g.
@@
 % 
-The goal of the agent is to maximise its cumulative reward and it is very important to fine-tune $\mathbf{R}$ correctly in order to produce an effective action policy.
+The goal of the agent is to maximise its cumulative reward and it is very important to fine-tune $\mathbf{R}$ correctly for producing an effective action policy.
 In order to encourage the agent to find the target object as fast as possible, a relatively large positive reward should be assigned for successfully reaching the goal state, and a negative one in any other case.
@@
 
-\subsection{MDP Implementation}
+\subsection{System Implementation}
 
@@
 
-\subsubsection{Training} \label{sec:training}
+\subsubsection{MDP Training} \label{sec:training}
 
@@
 
-The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset~\cite{openimages}, which consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for an example).
+The spatial relationships between the objects in $\mathbf{O}$ are extracted from the OpenImage dataset~\cite{openimages}, which consists of 1.74M images containing 14.6M manually drawn and labelled bounding boxes around objects (see Figure~\ref{fig:openimage-example} for some examples).
 The dataset is primarily aimed toward object recognition researchers to benchmark their models.
@@
 we can only say that object 1 is above object 2, but not how far above.
-Our relatively simple action-space is therefore suitable for the dataset's lack of information.
+Our relatively simple action-space is therefore suitable for the limited dataset information.
 
@@
     \centering
-    \includegraphics[width=0.4\textwidth]{../figures/desk_example.png}
+    \includegraphics[width=\columnwidth]{../figures/desk_example.png}
   \end{subfigure}
+  \vfill
   \begin{subfigure}
     \centering
-    \includegraphics[width=0.4\textwidth]{../figures/mug_example.png}
+    \includegraphics[width=\columnwidth]{../figures/mug_example.png}
   \end{subfigure}
-  \caption{Examples of images from the OpenImage dataset containing objects from $\mathit{O}$~\cite{openimages}. }\label{fig:openimage-example}
+  \caption{Examples of images from the OpenImage dataset containing objects from our set $\mathbf{O}$~\cite{openimages}. }\label{fig:openimage-example}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{../figures/object_relationships.png}
+  \includegraphics[width=\columnwidth]{../figures/object_relationships.png}
   \caption{Examples of the spatial relationships between the desk, keyboard and mouse objects.
@@
 
-We force the MDP to generate a maximum of 11 (inclusive) steps to the target, with 11 being the longest possible route on the action grid (more details about the grid are in Section~\ref{sec:system-implementation}).
+We force the MDP to generate a maximum of 11 (inclusive) steps to the target, with 11 being the longest possible route on the action grid (more details about the grid are in Section~\ref{sec:waypoints-generation}).
 A search could take longer than 11 steps, but the MDP considers that the maximum, which is convenient for keeping a manageable state-space and a simple reward function.
-The MDP therefore has a total of 154 reachable states ($s_{total}=11\times7\times2$).
+The MDP therefore has a total of 154 reachable states ($s_{tot}=11\times7\times2$).
 
@@
 \begin{equation}
-  \alpha = \exp\Big(\frac{-i}{10~s_{total}}\Big) - 0.001,
+  \alpha = \exp\Big(\frac{-i}{10~s_{tot}}\Big) - 0.001,
 \end{equation}
-where $i$ is the episode index.  $\gamma$ is set to 0.95 to prioritise long-term reward and guarantee convergence.
+where $i$ is the episode index. The discount factor $\gamma$ is set to 0.95 to prioritise long-term rewards and guarantee convergence.
 
 Our MDP has a relatively small state-action space.
-Therefore, a solution can be found in a reasonable amount of time.
-However, it should be noted that adjusting the angle interval, or adding more actions or objects, can easily lead to an intractable size of the state-space.
+Therefore, a solution can be found within a reasonable amount of time.
+However, it should be noted that adjusting the angle interval, or adding more actions or objects, can easily lead to an intractable space size.
 
-\subsubsection{Android Implementation}\label{sec:system-implementation}
+\subsubsection{Waypoints Generation}\label{sec:waypoints-generation}
 
-We incorporated the trained MDP-based controller into an app (see Figure~\ref{fig:system-screenshot}) for an Asus ZenPhone AR smartphone, running Android 7.0, with Google's augmented reality toolkit (ARCore), which provides the necessary 3D pose of the device.
+The system uses a 6$\times$6 discretised radial grid to simplify the tracking and waypoint generation processes.
+The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.
+A policy action is converted by the system into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the camera's current orientation.
+Note that this cell is not part of the MDP' state and the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variation between subsequent actions.
+
+% The grid is generated at the system's start-up and remains constant throughout its lifetime.
+The system uses the waypoint's location to provide the user with guidance instructions (i.e.
+$u$ in Figure~\ref{fig:control-loop}).
+The policy actions, and waypoints by extension, are relative to the current camera's pan-tilt orientation.
+The grid is also wrapped so, if the location of a waypoint exceeds the \SI{120}{\degree} limit, the same waypoint is moved to the opposite side of the grid, effectively limiting the search space to a \SI{120}{\degree}$\times$\SI{120}{\degree} area.
+
+\subsubsection{Smartphone Application}\label{sec:smartphone-application}
+
+We incorporated the trained system into an app (see Figure~\ref{fig:system-screenshot}) for an Asus ZenPhone AR smartphone, running Android 7.0, with Google's augmented reality toolkit (ARCore), which provides the necessary 3D pose of the device.
 No further software or hardware modifications were required.
@@
   \centering
-  \includegraphics[width=0.35\textwidth]{../figures/system_screenshot2.png}
-  \caption{A screenshot of the guidance interface showing an example of guidance instructions towards a waypoint and the QR-object scanner area.}\label{fig:system-screenshot}
+  \includegraphics[width=\columnwidth]{../figures/system_screenshot2.png}
+  \caption{A screenshot of the smartphone interface showing an example of guidance instruction (down-left in this case) towards a waypoint and the QR-object scanner area.}\label{fig:system-screenshot}
 \end{figure}
 
-The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes.
-The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.
-A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the camera's current orientation.
-Note that this cell is not part of the MDP's state and the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variation between subsequent actions.
-The grid is generated at the app's start-up and remains constant throughout its lifetime.
-The app then uses the new waypoint's location to provide the user with guidance instructions.
-The policy actions, and waypoints by extension, are given relative to the current camera's pan-tilt orientation.
-The grid is wrapped, so if a waypoint's location exceeds the \SI{120}{\degree} limit, the waypoint is generated at the opposite side of the grid instead, limiting the search space to a \SI{120}{\degree}$\times$\SI{120}{\degree} area.
+The system determines the state values for $n$ (number of search steps so far) and $v$ (waypoint already visited or not) described in Section~\ref{sec:states}, by recording the previous positions and waypoint locations.
+The camera provides the ID of the object currently within view, which is assigned to the state variable $o$.
+In the current implementation, we did not use a real object detector, but we simulated it with 7 different QR codes, one for each unique object, and a camera-based QR code scanner from Android's machine learning API (MLKit).
+This simplification guarantees full observability of the state and let us focus on the performance of the MDP-based controller in the following experiments.
+%
+% The QR scanner requires raw image data.
+Moreover, to speed up the image processing and avoid scanning multiple QR codes, we only used the central part of the camera's frame, which is $300\times300$ pixels.
+This choice also defines the precision required in pointing the camera towards the object (see Figure~\ref{fig:system-screenshot}).
 
-The position of the waypoint is given to the user by a set of guidance instructions (the arrows seen on-screen in Figure~\ref{fig:system-screenshot}) in terms of the actions defined in $\textbf{A}$.
-This might seem like an unnecessary extra step, but this system is designed for user with vision impairments who are limited to audio instructions, which makes it necessary to split the instructions up into separate channels that can be communicated more simply.
-This requirement becomes clear when one considers the bandwidth limitations of a person's audio channel compared to the visual one.
-To clarify, the arrows were used for debugging and experimentation and they will be translated into audio signals once the audio interface is implemented.
-
-By recording the previous positions and waypoint locations, the system can infer the state values for $n$ and $v$ described in Section~\ref{sec:states}.
-Furthermore, the camera provides the ID of the object currently within view, which is assigned to the state variable $o$.
-As explained in the next section, we did not use a real object detector in our experiments, but we simulated it with 7 different QR codes, one for each unique object, and a camera-based QR code scanner from Android's machine learning API (MLKit).
-
-The QR scanner requires raw image data.
-To avoid scanning multiple QR codes and speed up the image processing, we only used the central part of the camera's frame, which is $300\times300$ pixels.
-This choice also defines the precision required in pointing the camera towards the object (see also Figure~\ref{fig:system-screenshot}).
+In a real application for people with visual impairments, the position of the waypoint would be given to the user by a set of audio or vibrotactile instructions.
+However, since we are mainly interested in evaluating the control algorithm of our system and not the interface ($K$ and not $u$), our current prototype generates guidance instructions with four on-screen arrows (see Figure~\ref{fig:system-screenshot}).
+% This might seem like an unnecessary extra step, but this system is designed for user with vision impairments who are limited to audio instructions, which makes it necessary to split the instructions up into separate channels that can be communicated more simply.
+% This requirement becomes clear when one considers the bandwidth limitations of a person's audio channel compared to the visual one.
+Obviously, this visual interface is only used for debugging and experimental evaluation of the controller, and it will be replaced by an opportune audio interface, e.g.~\cite{bellotto2013}, at a second stage.
 
@@
 \noindent To test the effectiveness of our MDP and its policies, we designed a set of experiments that determined how effective the system is at directing a participant to point the device's camera towards a target object.
-This section discusses the experiments and their results.
+% This section discusses the experiments and their results.
 
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{../figures/test_env_picture.jpg}
+  \includegraphics[width=\columnwidth]{../figures/test_env_picture.jpg}
   \caption{A picture of the environment used for the experiments. Each QR code represents an object.}\label{fig:env-picture}
@@
 The results for each individual participant is presented in Table~\ref{tab:results-full} and Table~\ref{tab:results-summary} gives the results across all of the participants.
-To provide a baseline measure for the ideal case, we ran a number of simulations in an environment mimicking the experiment setup with user that perfectly executes the policy, i.e.\ $u=u^*$.
+To provide a baseline measure for the ideal case, we ran a number of simulations in an environment mimicking the experiment setup with a user who perfectly executes the policy, i.e.\ $u=u^*$.
 The TAR and steps to target results for the simulation are included in Table~\ref{tab:results-summary}.
@@
 
-\noindent In this work we presented and tested an MDP-based system to guide a person with vision impairments towards a target object with no apriori knowledge of the environment.
+\noindent In this work we presented and tested an MDP-based system to guide a person with vision impairments towards a target object with no a~priori knowledge of the environment.
 We implemented the system in an Android app that we tested with a small group of sighted people to determine its viability and effectiveness at guiding a user to manipulating a camera and finding a target object.
@@
 
+\balance
+
 % \clearpage

### 2018-12-28 review_edition/reviewed.tex
some tidy up of sec 5 and 6

@@
 
-\noindent To test the effectiveness of our MDP and its policies, we designed a set of experiments that determined how effective the system is at directing a participant to point the device's camera towards a target object.
+\noindent To evaluate our system, we designed a set of experiments that determined how effective the MDP and its policies are at guiding the user in an object search task with the smartphone's camera.
 % This section discusses the experiments and their results.
@@
   \centering
-  \caption{A table containing the results for the TAR, number of steps and time to target means and standard deviations for each participant. }\label{tab:results-full}
+  \caption{Results for the TAR, number of steps and time to target means and standard deviations for each participant. }\label{tab:results-full}
   \begin{tabular}{cccc}
@@
 
-\begin{table}                      
+\begin{table}[b]                      
   \centering                       
@@
 
-\begin{figure}
+\begin{figure}[b]
   \centering
-  \includegraphics[width=0.5\textwidth]{../figures/cdf_tar_limit.png}
-  \caption{The distribution of the TAR as a function of the step limit for a search. The `x' indicates the cases that exceeded the 15-step limit. }\label{fig:tar-steps}
+  \includegraphics[height=5.9cm]{../figures/cdf_tar_limit.png}
+  \caption{TAR as a function of the step limit for a search. The `x' indicates the cases that exceeded the 15-step limit. }\label{fig:tar-steps}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{../figures/tar_objects.png}
+  \includegraphics[width=\columnwidth]{../figures/tar_objects.png}
   \caption{The TAR for each of the objects within $\mathbf{O}$. }\label{fig:tar-objects}
@@
 
-\begin{figure}
+\begin{figure}[b]
   \centering
-  \includegraphics[width=0.5\textwidth]{../figures/cdf_total_steps.png}
+  \includegraphics[height=5.9cm]{../figures/cdf_total_steps.png}
   \caption{The cumulative distribution of the participants' number of steps taken to find a target object. }\label{fig:nsteps-participants}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{../figures/cdf_total_time.png}
+  \includegraphics[width=\columnwidth]{../figures/cdf_total_time.png}
   \caption{The cumulative distribution of the participants' time taken to find a target object. }\label{fig:time-participants}
@@
 
-In comparison to the VizWiz system~\cite{bigham2010vizwiz} (mean 92s, standard deviation 37.7s), our results look very reasonable.
-However, these results may greatly change when we test the system with participants with vision impairments.
+In comparison to the VizWiz system~\cite{bigham2010vizwiz} (mean 92s, standard deviation 37.7s), our results look very reasonable, although there might be significant variations in case of participants with vision impairments.
 

### 2018-12-28 review_edition/reviewed.tex

@@
 \noindent To evaluate our system, we designed a set of experiments that determined how effective the MDP and its policies are at guiding the user in an object search task with the smartphone's camera.
+Since the focus of this work is on the algorithm for active object search, and not on the actual human performance, in the following experiments the system was tested by participants without any significant visual impairment.
+As explained in the previous section, this simplified the experimental design, allowing us to use the smartphone's display for the guidance instructions.
 % This section discusses the experiments and their results.
 
-\subsection{Experiment Design}
+\subsection{Experimental Design}
 
 \noindent For the experiment, the MDP policies were integrated into an Android application that uses the camera to provide observation data and track the pose and viewing direction.
-We avoided adding unnecessary variability and complexity to the experiment by providing visual waypoints on screen which the participants were allowed to use.
-A generic environment mimicking a typical office desk layout was set up as the experiment environment and contains 7 different objects (i.e.\ encoded QR codes), one of which could be selected for each experiment run.
-See Figure~\ref{fig:env-picture} for a picture of the environment.
+Guidance instructions towards the waypoints were visualised on the screen, which the participants were allowed to use.
+The experimental environment mimicked a typical office desk layout and contained 7 different objects (i.e.\ encoded QR codes), one of which could be selected for each experiment run.
+See Figure~\ref{fig:env-picture} for a snapshot of the environment.
 
@@
   \includegraphics[width=\columnwidth]{../figures/test_env_picture.jpg}
-  \caption{A picture of the environment used for the experiments. Each QR code represents an object.}\label{fig:env-picture}
+  \caption{A snapshot of the environment used for the experiments. Each QR code represents an object.}\label{fig:env-picture}
 \end{figure}
 
-For each experiment, the participant was placed roughly \SI{1}{\meter} from the barcodes and was asked not to move from that spot during the experiment.
-The participant then pressed a button on the app that randomly selected a target object and was then guided towards that target by the app.
-Since the participants were allowed to use their vision, the targets were randomly selected and the participants were uninformed of what the target object was until it was found.
-This was done to avoid the participants learning the target objects' locations between each search run.
+For each experiment, the participant was placed approximately at 1m from the closest barcodes and was asked to remain on that spot during the experiment.
+The participant started by pressing a button on the app, which randomly selected a target object and then guided the user towards it.
+Since the participants were allowed to use the smartphone's display, the target was randomly selected by the app without informing them, at least until it was found.
+This prevented the participants from learning the target objects' locations between subsequent runs of the experiment.
 
-During in-house tests, we noted that the system sometimes makes guidance mistakes that lead the user towards an uncluttered edge of the search space, at which point the system had difficulty guiding the user back to the centre.
-To avoid this having an adverse impact and drawing out the experiments too long, we set a search step limit of 15, which means that the search was terminated when the number of waypoints exceeded 15.
+To avoid pointing at uncluttered edges of the search space, where the system had difficulty guiding the user back to the centre, we set a search step-limit of 15, which means the search was terminated when the number of waypoints generated by the system exceeded 15.
 A search run therefore ended when the participant either successfully found the target object by pointing the phone camera to it and scanning the barcode, or exceeded the waypoint limit.
-After this, the participant then resets to the central position, selects a new target object and resumes the experiment.
+After this, the participant then restarted from the central position, generating a new random target object and repeating the experiment.
 
-The participants were left to repeat this process until we recorded 10 searches per object, giving us a total number of 70 recorded search samples per participant.
-We tested a total of 10 different participants (sex: 8 M, 2 F;\@ age: $\mu$ 31.2 years, $\sigma$ 8 years), most of whom were sourced from our laboratory.
-This gives our dataset a total of 700 search samples.
+We recorded 10 searches per object, giving us a total number of 70 search samples per participant.
+The system was tested by 10 participants, mostly from our research group.
+Our final dataset consisted therefore of 700 search samples, which are analysed next.
 
@@
 We present and discuss the results for each of these parameters in the next sections.
-The results for each individual participant is presented in Table~\ref{tab:results-full} and Table~\ref{tab:results-summary} gives the results across all of the participants.
-To provide a baseline measure for the ideal case, we ran a number of simulations in an environment mimicking the experiment setup with a user who perfectly executes the policy, i.e.\ $u=u^*$.
+The results for each individual participant are presented in Table~\ref{tab:results-full}, while those across all the participants are shown in Table~\ref{tab:results-summary}.
+To provide a baseline measure for the ideal case, we ran a number of simulations in an environment mimicking the experiment setup with a ``virtual'' user who perfectly executes the policy, i.e.\ $u=u^*$.
 The TAR and steps to target results for the simulation are included in Table~\ref{tab:results-summary}.
@@
   \caption{The means and standard deviations for the entire participant population for the experiments and simulations.}\label{tab:results-summary}
-  \begin{tabular}{ccc}
+  \begin{tabular}{lcc}
+%     \toprule
+%     \multirow{2}{*}{TAR [\%]} & Experiment & 82 $\pm$ 11  \\ 
+% 			      & Simulation & 99.7 \\ \midrule
+%     \multirow{2}{*}{Num. Steps} & Experiment & 6.8 $\pm$ 5.1 \\ 
+% 			        & Simulation & 5.4 \\ \midrule
+%     Time [s] & Experiment & 34 $\pm$ 23  \\ \midrule
+%     \bottomrule
     \toprule
-    \multirow{2}{*}{TAR [\%]} & Experiment & 82 $\pm$ 11  \\ 
-			      & Simulation & 99.7 \\ \midrule
-    \multirow{2}{*}{Num. Steps} & Experiment & 6.8 $\pm$ 5.1 \\ 
-			        & Simulation & 5.4 \\ \midrule
-    Time [s] & Experiment & 34 $\pm$ 23  \\ \midrule
+     & Experiments & Simulations \\ \midrule
+    TAR [\%] & 82 $\pm$ 11 & 99.7 \\ \midrule
+    Num. Steps & 6.8 $\pm$ 5.1 & 5.4 \\ \midrule
+    Time [s] & 34 $\pm$ 23 & --  \\ \midrule
     \bottomrule
@@
 
-\noindent The TAR is a measure of how successful the system was at directing a participant to the target object within the 15-step limit we set and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches.
-Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present.
+\noindent The TAR is a measure of how successful the system was at directing a participant to the target object within our 15-step limit.
+It is simply calculated as a ratio between the number of completed searches vs.\ the total number of searches.
+Please note, however, that this ratio depends also on the step-limit and should not be taken as an absolute measure of performance (i.e.
+if the step limit was much bigger, the TAR would tend to 100\%).
 Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off as the step-limit increases.
@@
 
-Figure~\ref{fig:tar-objects} shows the TAR for each object in $\mathbf{O}$.
-There are variations the TAR for the different objects, with the smaller objects typically being the hardest to find.
-However, the differences are not extreme and indicate that all the objects in $\mathbf{O}$ are roughly equally hard to find.
+Figure~\ref{fig:tar-objects} shows the TAR for each object in our set~$\mathbf{O}$.
+There are TAR variations for the different objects, with the smaller objects typically being the hardest to find.
+However, the differences are not extreme and indicate that all the objects in $\mathbf{O}$ are roughly equally hard to locate.
 This is also displayed in the simulation's TAR in Table~\ref{tab:results-summary}, which could not achieve 100\% because of the difficulty the agent had in finding the objects on the fringes of the environment.
@@
 
-Failure cases were typically caused by the system entering a no-recovery state where the system directed a user into dead-space with no spatial information (e.g.\ a ceiling or wall section) and could not gather the information it required to intelligently guide the user.
-Subsequent system updates will have to consider implementing fall-back methods or automatic recovery modes that can detect entry of a no-recovery state (e.g.\ exceeding a set number of steps/time without making an observation) and guide the user back to the initial position and restart a search.
+Failure cases were typically caused by the system entering a no-recovery state where the user was directed into dead-space with no spatial information (e.g.\ ceiling or wall section).
+In this case the system could not observe useful clues to intelligently guide the user.
+Possible improvements for future versions of the algorithm would be to implement some fall-back method that can detect a no-recovery state (e.g.\ exceeding a set number of steps/time without any new object observation) and guide the user back to a position where to restart the search.
 
@@
 
-\noindent The number of steps to the target indicates the number of waypoints the system generated for the participant during the guidance process and is a major indication of system performance, where less waypoints means faster target acquisition and better performance.
+\noindent The number of steps to the target indicates the number of waypoints the system generated for the participant during the guidance process.
+This is a good indication of system performance, where less waypoints means faster target acquisition and therefore better object search strategy.
 Figure~\ref{fig:nsteps-participants} shows the cumulative distribution of the number of steps to the target for all the participants.
@@
 
-The number of waypoints each participant required is fairly evenly spread across all of the participants, with the majority of searches ending within 4 steps of initialisation or ending.
-The population mean and standard deviation is 6.8 and 5.1 waypoints respectively.
+The number of waypoints each participant required is fairly evenly spread across all of the participants, with the majority of searches ending within a few search steps.
+The population mean and standard deviation is 6.8 and 5.1 waypoints, respectively.
 This is a reasonable result, since most target objects were placed within approximately 4 grid squares away from the participants' initial looking directions.
-However, the relatively high standard deviation should be noted and can also be reduced by implementing the automatic recovery mode mentioned previously, and avoiding information-sparse areas.
+The relatively high standard deviation is due to the aforementioned no-recovery states and could be reduced by opportune mitigation strategies to avoid uninformative areas.
 
@@
 
-\noindent The distribution of the total time it took the participants to reach the target object is given in Figure~\ref{fig:time-participants}.
+\noindent The cumulative distribution of the time it took the participants to reach the target object is given in Figure~\ref{fig:time-participants}.
 We see that the distribution is heavily skewed to the bottom with a long tail.
@@
 
-In comparison to the VizWiz system~\cite{bigham2010vizwiz} (mean 92s, standard deviation 37.7s), our results look very reasonable, although there might be significant variations in case of participants with vision impairments.
+In comparison to the remotely-assisted VizWiz system~\cite{bigham2010vizwiz} covered in Section~\ref{sec:previous-work} (mean 92s, standard deviation 37.7s), our results look very encouraging, although there might be significant variations in case of participants with actual vision impairments.
 

### 2018-12-28 review_edition/reviewed.tex
final revision

@@
 
-\keywords{Active vision, object search, vision impairment, Markov Decision Process}
+\keywords{Active vision, object search, visual impairment, Markov Decision Process}
 
@@
 An initial implementation of the system on a smartphone was experimentally evaluated with participants with healthy eyesight to determine the performance of the control algorithm.
-The results show the effectiveness of our solution and its application to help people with visual impairments find objects in unknown environments.}
+The results show the effectiveness of our solution and its potential application to help people with visual impairments find objects in unknown environments.}
 
@@
 Modern improvements in mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem.
-The work presented here is part of a project to assist people with vision impairments to navigate and find objects in unknown environments with the aid of a smartphone.
+The work presented here is part of a project to assist people with visual impairments to navigate and find objects in unknown environments with the aid of a smartphone.
 The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}, expanding upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
@@
 
-\noindent Assistive technology for people living with vision impairments is a growing research area~\cite{Manduchi2012,khoo2016multimodal}.
+\noindent Assistive technology for people living with visual impairments is a growing research area~\cite{Manduchi2012,khoo2016multimodal}.
 In recent years, the increase in mobile processing power and computer vision improvements have led to research in the use of smartphone cameras to augment or enhance a user's vision and help them find objects or other points of interest.
@@
 The VizWiz has the advantage of being fairly robust and is able to classify a great deal of objects with little effort from the user and can provide natural, human-generated and curated directions.
-However, this approach does not enhance user independence, since a person with vision impairments is now beholden to an online worker instead of a relative, friend or bystander.
+However, this approach does not enhance user independence, since a person with visual impairments is now beholden to an online worker instead of a relative, friend or bystander.
 Furthermore, a good internet connection is required on the device, possibly limiting its use in some poor-reception areas.
@@
 In summary, much research has been conducted on recognition of and guidance towards target objects, including active vision solutions for image classifiers and robotic systems.
-However, to our knowledge, no previous work has been done on {\em active} object search and guidance for humans, which would especially benefit people with vision impairments.
+However, to our knowledge, no previous work has been done on {\em active} object search and guidance for humans, which would especially benefit people with visual impairments.
 In this paper, we implement such an active vision system with a human in the loop
@@
 
-\noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a person with vision impairments to his/her destination with minimal user input or intervention.
+\noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a person with visual impairments to his/her destination with minimal user input or intervention.
 A complete system diagram is given is Figure~\ref{fig:control-loop}.
@@
 However, since we are mainly interested in evaluating the control algorithm of our system and not the interface ($K$ and not $u$), our current prototype generates guidance instructions with four on-screen arrows (see Figure~\ref{fig:system-screenshot}).
-% This might seem like an unnecessary extra step, but this system is designed for user with vision impairments who are limited to audio instructions, which makes it necessary to split the instructions up into separate channels that can be communicated more simply.
+% This might seem like an unnecessary extra step, but this system is designed for user with visual impairments who are limited to audio instructions, which makes it necessary to split the instructions up into separate channels that can be communicated more simply.
 % This requirement becomes clear when one considers the bandwidth limitations of a person's audio channel compared to the visual one.
@@
 Table~\ref{tab:results-full} shows a fairly consistent spread for the TAR across the participants.
-The inter-participant spread ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance, but with an average TAR of $82\%$, it is clear that the system successfully finds the target object during the vast majority of searches.
+The inter-participant spread in Table~\ref{tab:results-summary} ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance, but with an average TAR of $82\%$, it is clear that the system successfully finds the target object during the vast majority of searches.
 
@@
 We see that the distribution is heavily skewed to the bottom with a long tail.
-The mean and standard deviation of the data is 29.8s and 23s respectively.
+The mean and standard deviation of the data is 34s and 23s respectively.
 %, is far greater than for the number of waypoints they required.
@@
 
-In comparison to the remotely-assisted VizWiz system~\cite{bigham2010vizwiz} covered in Section~\ref{sec:previous-work} (mean 92s, standard deviation 37.7s), our results look very encouraging, although there might be significant variations in case of participants with actual vision impairments.
+In comparison to the remotely-assisted VizWiz system~\cite{bigham2010vizwiz} covered in the related work (mean 92s, standard deviation 37.7s), our results look very encouraging, although there might be variations in case of participants with visual impairments.
 
@@
 
-\noindent In this work we presented and tested an MDP-based system to guide a person with vision impairments towards a target object with no a~priori knowledge of the environment.
-We implemented the system in an Android app that we tested with a small group of sighted people to determine its viability and effectiveness at guiding a user to manipulating a camera and finding a target object.
-We found that is works well when compared to alternative systems, with a respectable mean time of target acquisition of 32s.
-However, the system can be improved by refining the search strategy and implementing an automatic fail-state recovery system that will guide a user back to neutral position if a fail-state is entered (e.g.\ a blank section of wall).
-Furthermore, a different dataset, purpose-built for object spatial relations, will give the MDP a more accurate understanding of the world and an improved transition model.
+\noindent In this work we presented and tested an MDP-based system to guide a person with visual impairments towards a target object with no prior knowledge of the environment.
+We implemented the system in an Android app and tested it with sighted users to determine the effectiveness of the active object search algorithm.
+We found that it works generally well, even when compared to alternative human-guided systems.
+However, the solution can be improved by refining the search strategy and implementing an automatic fail-state recovery when the user points to an empty scenario, like a blank wall.
+Furthermore, a purpose-built dataset with clear object spatial relations would enable the creation of a more accurate transition model for the MDP controller.
 
-The next steps to this project will involve using the data recorded here to improve and refine the MDP model that provides the guidance.
-The model can also be expanded to include more objects and actions.
-However, an important consideration and expansion to the problem is to change the MDP to an Partially Observable MDP (POMDP) model that will bring the model more in line with reality by acknowledging that the objects are not perfectly observable and humans do not perfectly follow guidance instructions.
-This adjustment may be very important when we replace the QR code scanner with an object recognition that are typically more prone to making classification errors.
-Finally, the model can be adapted to use on-line learning techniques in order to further refine its transition model as the guidance system is used.
+Future work will include the replacement of the QR codes with a real vision-based object detector, possibly extending the number of items and actions.
+However, in order to consider the uncertainty introduced by such detector, the MDP will have to be replaced by a Partially Observable MDP (POMDP), taking into account that the objects are not perfectly observable and humans might not follow the guidance instructions accurately.
+Further directions of research include on-line learning techniques for model adaptation that better follow the user profile of each individual and the possible performance change over time.
 

### 2019-12-19 paper.tex
Fixing base repo to reflect camera ready

--- 2018-11-23 paper.tex
@@
 
-\title{Active Object Search with a Mobile Device for the Visually Impaired}
+\title{Active Object Search with a Mobile Device\\for People with Visual Impairments}
 
 \author{
-  \authorname{~}%Anon McAnon{\sup{1}}}
-  \affiliation{~}%\sup{1}Anon University of Anon, Anonville, Anonistan}
-  \email{~}%anon.anon@anon.com}
-%\affiliation{\sup{1}Lincoln Centre for Autonomous Systems (L-CAS), University of Lincoln, Lincoln, UK}
-%\email{jlock@lincoln.ac.uk}
+  \authorname{Jacobus C. Lock{\sup{1}}, Grzegorz Cielniak\sup{1}, Nicola Bellotto\sup{1}}
+  \affiliation{\sup{1}Lincoln Centre for Autonomous Systems (L-CAS), University of Lincoln, Lincoln, UK}
+  \email{\{jlock, gcielniak, nbellotto\}@lincoln.ac.uk}
 }
 
-\keywords{Active vision, object search, vision impairment, Markov Decision Process}
+\keywords{Active vision, object search, visual impairment, Markov Decision Process}
 
-\abstract{Modern smartphones can provide a multitude of services to assist people with visual impairments.
-The cameras embedded in these mobile devices, in particular, can be useful for many tasks, like reading signs or searching for objects in unknown environments.
-Although previous research in computer vision has looked at ways to solve these tasks by processing the video frames of the mobile camera, very little work has been done in {\em actively} guiding the user towards specific points of interest that maximise the effectiveness of the underlying visual algorithms.
-In this paper, we propose a control algorithm based on a Markov Decision Process (MDP) that generates real-time instructions to guide a user searching for a target object with a smartphone's camera.
-The solution is part of a more general active vision application for the visually impaired.
-An initial implementation of the system on an Android smartphone was experimentally evaluated with sighted participants to determine the performance of the control algorithm.
-The results show the effectiveness of our solution and its potential application to help the visually impaired find objects in unknown environments.}
+\abstract{Modern smartphones can provide a multitude of services to assist people with visual impairments, and their cameras in particular can be useful for assisting with tasks, such as reading signs or searching for objects in unknown environments.
+Previous research has looked at ways to solve these problems by processing the camera's video feed, but very little work has been done in {\em actively} guiding the user towards specific points of interest, maximising the effectiveness of the underlying visual algorithms.
+In this paper, we propose a control algorithm based on a Markov Decision Process that uses a smartphone's camera to generate real-time instructions to guide a user towards a target object.
+The solution is part of a more general active vision application for people with visual impairments.
+An initial implementation of the system on a smartphone was experimentally evaluated with participants with healthy eyesight to determine the performance of the control algorithm.
+The results show the effectiveness of our solution and its potential application to help people with visual impairments find objects in unknown environments.}
 
@@
 
-\noindent It is estimated that almost half a billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives.
+\noindent It is estimated that almost half a billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more independent lives.
 Modern improvements in mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem.
-The work presented here is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone.
-The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017,bellotto2013}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}.
-Schematically, the actuators used in a typical control loop, shown in Figure~\ref{fig:control-loop}, are replaced by a human.
-%This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
+The work presented here is part of a project to assist people with visual impairments to navigate and find objects in unknown environments with the aid of a smartphone.
+The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of a moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}, expanding upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.
 
@@
   \centering
-  \includegraphics[width=0.38\textwidth]{figures/system_use.png}
+  \includegraphics[width=0.85\columnwidth]{figures/system_use.png}
   \caption{The system in use during an experiment. }\label{fig:system-use}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
-  \caption{System control loop: $r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation.
-$K$, $H$ and $P$ are the control, human and sensor blocks respectively.
-}\label{fig:control-loop}
 \end{figure}
@@
 
-\noindent Assistive vision and guidance for the VI is a growing research area.
+\noindent Assistive technology for people living with visual impairments is a growing research area~\cite{Manduchi2012,khoo2016multimodal}.
 In recent years, the increase in mobile processing power and computer vision improvements have led to research in the use of smartphone cameras to augment or enhance a user's vision and help them find objects or other points of interest.
@@
 The VizWiz has the advantage of being fairly robust and is able to classify a great deal of objects with little effort from the user and can provide natural, human-generated and curated directions.
-However, this approach does not enhance user independence, since the VI person is now beholden to an online worker instead of a relative, friend or bystander.
+However, this approach does not enhance user independence, since a person with visual impairments is now beholden to an online worker instead of a relative, friend or bystander.
 Furthermore, a good internet connection is required on the device, possibly limiting its use in some poor-reception areas.
@@
 The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets~\cite{song2016ssc,Everingham10}, and are iteratively changed based on the output from the respective models.
-The advantage of their approaches is that fewer windows are generated and submitted to the classifier, resulting in lower object classification times, while still keeping state-of-the-art results for the accuracy.
+The advantage of their approaches is that fewer windows are generated and submitted to the classifier, resulting in lower object classification times while still keeping state-of-the-art results for accuracy.
 
@@
 In summary, much research has been conducted on recognition of and guidance towards target objects, including active vision solutions for image classifiers and robotic systems.
-However, to our knowledge, no previous work has been done on {\em active} object search and guidance for humans, which would especially benefit VI users.
+However, to our knowledge, no previous work has been done on {\em active} object search and guidance for humans, which would especially benefit people with visual impairments.
 In this paper, we implement such an active vision system with a human in the loop
@@
 
-\noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a VI user to their destination with minimal user input or intervention.
+\noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a person with visual impairments to his/her destination with minimal user input or intervention.
 A complete system diagram is given is Figure~\ref{fig:control-loop}.
 This closed-loop system is conceptually similar to other classical control problems, where the difference between desired and actual state of a process is used to generate a control signal that changes the process itself.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
+  \caption{System control loop: $r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation.
+$K$, $H$ and $P$ are the control, human and sensor blocks respectively.
+}\label{fig:control-loop}
+\end{figure}
 
@@
 Two important points are considered in the design of the controller.
-Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places, unknown a priori.
-Secondly, the controller must be robust enough to handle incorrect interpretations by the human of the instructions $u$.
-This risk can be mitigated by the use of clear and simple instructions that helps $u$ track $u^*$ as closely as possible.
+Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places with unknown a~priori information.
+Secondly, since each person could interpret the instruction $u$ differently (i.e.
+different transformation block $H$), the controller must be robust enough to handle such incorrect interpretations.
+For example, one person might interpret and execute an `UP' instruction correctly (i.e.
+$u \backsimeq u^*$), while another might interpret it correctly, but execute the wrong action.
+This risk can be mitigated by the use of clear and simple instructions that helps $u^*$ be as close as possible to $u$.
 The implementation of this controller is discussed in detail next.
@@
 In this case, the agent is defined as the guidance system and the policy is used to generate the next waypoint on the search path towards the target object.
-We assume the directly observable states and known state transitions probabilities.
-The MDP can be represented by the following 5-tuple:
+We assume fully observable states and known state transitions probabilities.
+The MDP is represented by the 5-tuple
 
 \begin{equation}
-  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \gamma)
+  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \gamma),
 \end{equation}
-where $\mathbf{S}$ is a set of possible agent' states, $\mathbf{A}$ is a set of possible actions an agent can take in any given state, $\mathbf{T}$ is a set of state transition probabilities from state $s$ to state $s'$, with ${s,s'~\in~\mathbf{S}}$, and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a \in \mathbf{A}$ in state $s$.
-The scalar $\gamma$ is a discount factor which prioritises immediate over long-term rewards.
+where $\mathbf{S}$ is a set of possible agent' states, $\mathbf{A}$ is a set of possible actions the agent can take in any given state, $\mathbf{T}$ is a set of state transition probabilities from state $s$ to state $s'$, with ${s,s'~\in~\mathbf{S}}$, and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a \in \mathbf{A}$ in state $s$.
+The scalar $\gamma$ is a discount factor that prioritises immediate over long-term rewards and which affects the model's convergence rate~\cite{Russell2009}.
 Each of these elements are defined and discussed next.
@@
 
-The policy produced by an MDP define the action an agent will take when it finds itself in any given state.
+The policy produced by an MDP defines the action the agent will take when it finds itself in any given state.
 In this case, the action is the direction of the next waypoint relatively to the current device's pose.
-The possible actions are four:
+The possible actions are given by
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/office_desk_example.png}
-  \caption{An example action policies generated by the MDP to guide the user in pointing the camera from a random starting object (e.g.
+  \includegraphics[width=\columnwidth]{figures/office_desk_example.png}
+  \caption{Example of action policies generated by the MDP to guide the user in pointing the camera from a random starting object (e.g.
 monitor) to a target object (e.g.
@@
 % 
-The goal of the agent is to maximise its cumulative reward, therefore this is a very important parameter for producing a good action policy.
-In order to encourage the agent to find the target object as quick as possible, a relatively large positive reward should be assigned for successfully reaching the goal state, and a negative one in any other case.
-These parameters must be finely balanced to ensure an effective object search behaviour.
+The goal of the agent is to maximise its cumulative reward and it is very important to fine-tune $\mathbf{R}$ correctly for producing an effective action policy.
+In order to encourage the agent to find the target object as fast as possible, a relatively large positive reward should be assigned for successfully reaching the goal state, and a negative one in any other case.
+These parameters must be finely balanced to ensure effective object search behaviour.
 
@@
     \centering
-    \includegraphics[width=0.4\textwidth]{figures/desk_example.png}
+    \includegraphics[width=\columnwidth]{figures/desk_example.png}
   \end{subfigure}
+  \vfill
   \begin{subfigure}
     \centering
-    \includegraphics[width=0.4\textwidth]{figures/mug_example.png}
+    \includegraphics[width=\columnwidth]{figures/mug_example.png}
   \end{subfigure}
-  \caption{Examples of images from the OpenImage dataset containing objects from $\mathit{O}$~\cite{openimages}. }\label{fig:openimage-example}
+  \caption{Examples of images from the OpenImage dataset containing objects from our set $\mathbf{O}$~\cite{openimages}. }\label{fig:openimage-example}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/object_relationships.png}
+  \includegraphics[width=\columnwidth]{figures/object_relationships.png}
   \caption{Examples of the spatial relationships between the desk, keyboard and mouse objects.
@@
 \begin{equation}
-  \alpha = \exp\Big(\frac{-i}{10~s_{total}}\Big) - 0.001,
+  \alpha = \exp\Big(\frac{-i}{10~s_{tot}}\Big) - 0.001,
 \end{equation}
-where $i$ is the episode index.  $\gamma$ is set to 0.95 to prioritise long-term reward.
+where $i$ is the episode index. The discount factor $\gamma$ is set to 0.95 to prioritise long-term rewards and guarantee convergence.
 
 Our MDP has a relatively small state-action space.
-Therefore, a solution can be found in a reasonable amount of time.
-However, it should be noted that adjusting the angle interval, or adding more actions or objects, can easily lead to an intractable size of the state-space.
+Therefore, a solution can be found within a reasonable amount of time.
+However, it should be noted that adjusting the angle interval, or adding more actions or objects, can easily lead to an intractable space size.
 
-\subsubsection{Android Implementation}\label{sec:system-implementation}
+\subsubsection{Waypoints Generation}\label{sec:waypoints-generation}
 
-We incorporated the trained MDP-based controller into an app (see Figure~\ref{fig:system-screenshot}) for an Asus ZenPhone AR smartphone, running Android 7.0, with the Google's augmented reality toolkit (ARCore), which provides the necessary 3D pose of the device.
+The system uses a 6$\times$6 discretised radial grid to simplify the tracking and waypoint generation processes.
+The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.
+A policy action is converted by the system into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the camera's current orientation.
+Note that this cell is not part of the MDP' state and the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variation between subsequent actions.
+
+% The grid is generated at the system's start-up and remains constant throughout its lifetime.
+The system uses the waypoint's location to provide the user with guidance instructions (i.e.
+$u$ in Figure~\ref{fig:control-loop}).
+The policy actions, and waypoints by extension, are relative to the current camera's pan-tilt orientation.
+The grid is also wrapped so, if the location of a waypoint exceeds the \SI{120}{\degree} limit, the same waypoint is moved to the opposite side of the grid, effectively limiting the search space to a \SI{120}{\degree}$\times$\SI{120}{\degree} area.
+
+\subsubsection{Smartphone Application}\label{sec:smartphone-application}
+
+We incorporated the trained system into an app (see Figure~\ref{fig:system-screenshot}) for an Asus ZenPhone AR smartphone, running Android 7.0, with Google's augmented reality toolkit (ARCore), which provides the necessary 3D pose of the device.
 No further software or hardware modifications were required.
@@
   \centering
-  \includegraphics[width=0.35\textwidth]{figures/system_screenshot2.png}
-  \caption{A screenshot of the guidance interface showing a waypoint (based on an 3D Android model), the object scanner area and the guidance instruction arrows. }\label{fig:system-screenshot}
+  \includegraphics[width=\columnwidth]{figures/system_screenshot2.png}
+  \caption{A screenshot of the smartphone interface showing an example of guidance instruction (down-left in this case) towards a waypoint and the QR-object scanner area.}\label{fig:system-screenshot}
 \end{figure}
 
-The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes.
-A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation.
-Note that this cell is not part of the MDP' state: the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions.
-The grid is generated at the app's start-up and remains constant throughout its lifetime.
-The app then uses the new waypoint's location to provide the user with guidance instructions.
-The policy actions, and waypoints by extension, are given relative to the current camera's pan-tilt orientation.
-The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.
+The system determines the state values for $n$ (number of search steps so far) and $v$ (waypoint already visited or not) described in Section~\ref{sec:states}, by recording the previous positions and waypoint locations.
+The camera provides the ID of the object currently within view, which is assigned to the state variable $o$.
+In the current implementation, we did not use a real object detector, but we simulated it with 7 different QR codes, one for each unique object, and a camera-based QR code scanner from Android's machine learning API (MLKit).
+This simplification guarantees full observability of the state and let us focus on the performance of the MDP-based controller in the following experiments.
+%
+% The QR scanner requires raw image data.
+Moreover, to speed up the image processing and avoid scanning multiple QR codes, we only used the central part of the camera's frame, which is $300\times300$ pixels.
+This choice also defines the precision required in pointing the camera towards the object (see Figure~\ref{fig:system-screenshot}).
 
-The position of the waypoint is given to the user by a set of guidance instructions (the arrows seen on-screen in Figure~\ref{fig:system-screenshot}) in terms of the actions defined in $\textbf{A}$.
-This might seem like an unnecessary extra step, but this system is designed for VI users who are limited to audio instructions, which makes it necessary to split the instructions up into separate channels that can be communicated more simply.
-This requirement becomes clear when one considers the bandwidth limitations of a human's audio channel as compared to the visual one.
-
-By recording the previous positions and waypoint locations the app generated, it can infer the state values for $v$ and $n$.
-Furthermore, the camera provides the ID of the object in view, populating $o$ in the state.
-A real-time object detector was not used in this system to avoid unnecessary complexity and processing overhead and encoded QR codes and barcode scanner library were used to simulate object detection instead.
-
-The QR code scanner requires raw image data.
-To avoid scanning multiple QR codes and using excess processing power by scanning large images, we only used the centre part of the screen to scan for a barcode.
-This scanner area is $300\times300$ pixels and scans for barcodes without causing any frame-rate drops.
+In a real application for people with visual impairments, the position of the waypoint would be given to the user by a set of audio or vibrotactile instructions.
+However, since we are mainly interested in evaluating the control algorithm of our system and not the interface ($K$ and not $u$), our current prototype generates guidance instructions with four on-screen arrows (see Figure~\ref{fig:system-screenshot}).
+% This might seem like an unnecessary extra step, but this system is designed for user with visual impairments who are limited to audio instructions, which makes it necessary to split the instructions up into separate channels that can be communicated more simply.
+% This requirement becomes clear when one considers the bandwidth limitations of a person's audio channel compared to the visual one.
+Obviously, this visual interface is only used for debugging and experimental evaluation of the controller, and it will be replaced by an opportune audio interface, e.g.~\cite{bellotto2013}, at a second stage.
 
@@
 
-\noindent To test the effectiveness of our MDP and its policies, we designed a set of experiments that determined how effective the system is at directing a participant to point the device's camera towards a target object.
-This section discusses the experiments and their results.
+\noindent To evaluate our system, we designed a set of experiments that determined how effective the MDP and its policies are at guiding the user in an object search task with the smartphone's camera.
+Since the focus of this work is on the algorithm for active object search, and not on the actual human performance, in the following experiments the system was tested by participants without any significant visual impairment.
+As explained in the previous section, this simplified the experimental design, allowing us to use the smartphone's display for the guidance instructions.
+% This section discusses the experiments and their results.
 
-\subsection{Experiment Design}
+\subsection{Experimental Design}
 
 \noindent For the experiment, the MDP policies were integrated into an Android application that uses the camera to provide observation data and track the pose and viewing direction.
-We avoided adding unnecessary variability and complexity to the experiment by providing visual waypoints on screen which the participants were allowed to use.
-A generic environment mimicking a typical office desk layout was set up as the experiment environment and contains 7 different objects (i.e.\ encoded QR codes), one of which could be selected for each experiment run.
-See Figure~\ref{fig:env-picture} for a picture of the environment.
+Guidance instructions towards the waypoints were visualised on the screen, which the participants were allowed to use.
+The experimental environment mimicked a typical office desk layout and contained 7 different objects (i.e.\ encoded QR codes), one of which could be selected for each experiment run.
+See Figure~\ref{fig:env-picture} for a snapshot of the environment.
 
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{figures/test_env_picture.jpg}
-  \caption{A picture of the environment used for the experiments. Each QR code represents an object.}\label{fig:env-picture}
+  \includegraphics[width=\columnwidth]{figures/test_env_picture.jpg}
+  \caption{A snapshot of the environment used for the experiments. Each QR code represents an object.}\label{fig:env-picture}
 \end{figure}
 
-For each experiment, the participant was placed roughly \SI{1}{\meter} from the barcodes and was asked not to move from that spot during the experiment.
-The participant then pressed a button on the app that randomly selected a target object and was then guided towards that target by the app.
-Since the participants were allowed to use their vision, the targets were randomly selected and the participants were uninformed of what the target object was until it was found.
-This was done to avoid the participants learning the target objects' locations between each search run.
+For each experiment, the participant was placed approximately at 1m from the closest barcodes and was asked to remain on that spot during the experiment.
+The participant started by pressing a button on the app, which randomly selected a target object and then guided the user towards it.
+Since the participants were allowed to use the smartphone's display, the target was randomly selected by the app without informing them, at least until it was found.
+This prevented the participants from learning the target objects' locations between subsequent runs of the experiment.
 
-During in-house tests, we noted that the system sometimes makes guidance mistakes that lead the user towards an uncluttered edge of the search space, at which point the system had difficulty guiding the user back to the centre.
-To avoid this having an adverse impact and drawing out the experiments too long, we set a search step limit of 15, which means that the search was terminated when the number of waypoints exceeded 15.
+To avoid pointing at uncluttered edges of the search space, where the system had difficulty guiding the user back to the centre, we set a search step-limit of 15, which means the search was terminated when the number of waypoints generated by the system exceeded 15.
 A search run therefore ended when the participant either successfully found the target object by pointing the phone camera to it and scanning the barcode, or exceeded the waypoint limit.
-After this, the participant then resets to the central position, selects a new target object and resumes the experiment.
+After this, the participant then restarted from the central position, generating a new random target object and repeating the experiment.
 
-The participants were left to repeat this process until we recorded 10 searches per object, giving us a total number of 70 recorded search samples per participant.
-We tested a total of 10 different participants (sex: 8 M, 2 F;\@ age: $\mu$ 31.2 years, $\sigma$ 8 years), most of which were sourced from our laboratory with none having any disabilities or handicaps.
-This gives our dataset a total of 700 search samples.
+We recorded 10 searches per object, giving us a total number of 70 search samples per participant.
+The system was tested by 10 participants, mostly from our research group.
+Our final dataset consisted therefore of 700 search samples, which are analysed next.
 
@@
 We present and discuss the results for each of these parameters in the next sections.
-The results for each individual participant is presented in Table~\ref{tab:results-full} and Table~\ref{tab:results-summary} gives the results across all of the participants.
-To provide a baseline measure for the ideal case, we ran a number of simulations in an environment mimicking the experiment setup with an agent that perfectly executes the policy, i.e.\ $u=u^*$.
+The results for each individual participant are presented in Table~\ref{tab:results-full}, while those across all the participants are shown in Table~\ref{tab:results-summary}.
+To provide a baseline measure for the ideal case, we ran a number of simulations in an environment mimicking the experiment setup with a ``virtual'' user who perfectly executes the policy, i.e.\ $u=u^*$.
 The TAR and steps to target results for the simulation are included in Table~\ref{tab:results-summary}.
@@
 
-\begin{table}                      
+\begin{table}[b]                      
   \centering                       
   \caption{The means and standard deviations for the entire participant population for the experiments and simulations.}\label{tab:results-summary}
-  \begin{tabular}{ccc}
+  \begin{tabular}{lcc}
+%     \toprule
+%     \multirow{2}{*}{TAR [\%]} & Experiment & 82 $\pm$ 11  \\ 
+% 			      & Simulation & 99.7 \\ \midrule
+%     \multirow{2}{*}{Num. Steps} & Experiment & 6.8 $\pm$ 5.1 \\ 
+% 			        & Simulation & 5.4 \\ \midrule
+%     Time [s] & Experiment & 34 $\pm$ 23  \\ \midrule
+%     \bottomrule
     \toprule
-    \multirow{2}{*}{TAR [\%]} & Experiment & 82 $\pm$ 11  \\ 
-			      & Simulation & 99.7 \\ \midrule
-    \multirow{2}{*}{Num. Steps} & Experiment & 6.8 $\pm$ 5.1 \\ 
-			        & Simulation & 5.4 \\ \midrule
-    Time [s] & Experiment & 34 $\pm$ 23  \\ \midrule
+     & Experiments & Simulations \\ \midrule
+    TAR [\%] & 82 $\pm$ 11 & 99.7 \\ \midrule
+    Num. Steps & 6.8 $\pm$ 5.1 & 5.4 \\ \midrule
+    Time [s] & 34 $\pm$ 23 & --  \\ \midrule
     \bottomrule
@@
 
-\noindent The TAR is a measure of how successful the system was at directing a participant to the target object within the 15-step limit we set and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches.
-Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present.
+\noindent The TAR is a measure of how successful the system was at directing a participant to the target object within our 15-step limit.
+It is simply calculated as a ratio between the number of completed searches vs.\ the total number of searches.
+Please note, however, that this ratio depends also on the step-limit and should not be taken as an absolute measure of performance (i.e.
+if the step limit was much bigger, the TAR would tend to 100\%).
 Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off as the step-limit increases.
 
-\begin{figure}
+\begin{figure}[b]
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/cdf_tar_limit.png}
-  \caption{The distribution of the TAR as a function of the step limit for a search. The `x' indicates the cases that exceeded the 15-step limit. }\label{fig:tar-steps}
+  \includegraphics[height=5.9cm]{figures/cdf_tar_limit.png}
+  \caption{TAR as a function of the step limit for a search. The `x' indicates the cases that exceeded the 15-step limit. }\label{fig:tar-steps}
 \end{figure}
@@
 Table~\ref{tab:results-full} shows a fairly consistent spread for the TAR across the participants.
-The inter-participant spread ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance, but with an average TAR of $82\%$, it is clear that the system successfully finds the target object during the vast majority of searches.
+The inter-participant spread in Table~\ref{tab:results-summary} ($\sigma=11\%$) is fairly significant, perhaps indicating that the user's search behaviour and strategy affects the target acquisition performance, but with an average TAR of $82\%$, it is clear that the system successfully finds the target object during the vast majority of searches.
 
-Figure~\ref{fig:tar-objects} shows the TAR for each object in $\mathbf{O}$.
-There are variations the TAR for the different objects, with the smaller objects typically being the hardest to find.
-However, the differences are not extreme and indicate that all the objects in $\mathbf{O}$ are roughly equally hard to find.
+Figure~\ref{fig:tar-objects} shows the TAR for each object in our set~$\mathbf{O}$.
+There are TAR variations for the different objects, with the smaller objects typically being the hardest to find.
+However, the differences are not extreme and indicate that all the objects in $\mathbf{O}$ are roughly equally hard to locate.
 This is also displayed in the simulation's TAR in Table~\ref{tab:results-summary}, which could not achieve 100\% because of the difficulty the agent had in finding the objects on the fringes of the environment.
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{figures/tar_objects.png}
+  \includegraphics[width=\columnwidth]{figures/tar_objects.png}
   \caption{The TAR for each of the objects within $\mathbf{O}$. }\label{fig:tar-objects}
@@
 
-\noindent The number of steps to the target indicates the number of waypoints the system generated for the participant during the guidance process and is a major indication of system performance, where less waypoints means faster target acquisition and better performance.
+\noindent The number of steps to the target indicates the number of waypoints the system generated for the participant during the guidance process.
+This is a good indication of system performance, where less waypoints means faster target acquisition and therefore better object search strategy.
 Figure~\ref{fig:nsteps-participants} shows the cumulative distribution of the number of steps to the target for all the participants.
 
-\begin{figure}
+\begin{figure}[b]
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/cdf_total_steps.png}
+  \includegraphics[height=5.9cm]{figures/cdf_total_steps.png}
   \caption{The cumulative distribution of the participants' number of steps taken to find a target object. }\label{fig:nsteps-participants}
@@
 
-\noindent The distribution of the total time it took the participants to reach the target object is given in Figure~\ref{fig:time-participants}.
+\noindent The cumulative distribution of the time it took the participants to reach the target object is given in Figure~\ref{fig:time-participants}.
 We see that the distribution is heavily skewed to the bottom with a long tail.
-The mean and standard deviation of the data is 29.8s and 23s respectively.
+The mean and standard deviation of the data is 34s and 23s respectively.
 %, is far greater than for the number of waypoints they required.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/cdf_total_time.png}
+  \includegraphics[width=\columnwidth]{figures/cdf_total_time.png}
   \caption{The cumulative distribution of the participants' time taken to find a target object. }\label{fig:time-participants}
@@
 
-In comparison to the VizWiz system~\cite{bigham2010vizwiz} (mean 92s, standard deviation 37.7s), our results look very reasonable.
-However, these results may greatly change when we test the system with VI participants.
+In comparison to the remotely-assisted VizWiz system~\cite{bigham2010vizwiz} covered in the related work (mean 92s, standard deviation 37.7s), our results look very encouraging, although there might be variations in case of participants with visual impairments.
 
@@
 
-\noindent In this work we presented and tested an MDP-based system to guide a visually impaired (VI) person towards a target object with no apriori knowledge of the environment.
-We implemented the system in an Android app that we tested with a small group of sighted people to determine its viability and effectiveness at guiding a user to manipulating a camera and finding a target object.
-We found that is works well when compared to alternative systems, with a respectable mean time of target acquisition of 32s.
-However, the system can be improved by refining the search strategy and implementing an automatic fail-state recovery system that will guide a user back to neutral position if a fail-state is entered (e.g.\ a blank section of wall).
-Furthermore, a different dataset, purpose-built for object spatial relations, will give the MDP a more accurate understanding of the world and an improved transition model.
+\noindent In this work we presented and tested an MDP-based system to guide a person with visual impairments towards a target object with no prior knowledge of the environment.
+We implemented the system in an Android app and tested it with sighted users to determine the effectiveness of the active object search algorithm.
+We found that it works generally well, even when compared to alternative human-guided systems.
+However, the solution can be improved by refining the search strategy and implementing an automatic fail-state recovery when the user points to an empty scenario, like a blank wall.
+Furthermore, a purpose-built dataset with clear object spatial relations would enable the creation of a more accurate transition model for the MDP controller.
 
-The next steps to this project will involve using the data recorded here to improve and refine the MDP model that provides the guidance.
-The model can also be expanded to include more objects and actions.
-However, an important consideration and expansion to the problem is to change the MDP to an Partially Observable MDP (POMDP) model that will bring the model more in line with reality by acknowledging that the objects are not perfectly observable and humans do not perfectly follow guidance instructions.
-This adjustment may be very important when we replace the QR code scanner with an object recognition that are typically more prone to making classification errors.
-Finally, the model can be adapted to use on-line learning techniques in order to further refine its transition model as the guidance system is used.
+Future work will include the replacement of the QR codes with a real vision-based object detector, possibly extending the number of items and actions.
+However, in order to consider the uncertainty introduced by such detector, the MDP will have to be replaced by a Partially Observable MDP (POMDP), taking into account that the objects are not perfectly observable and humans might not follow the guidance instructions accurately.
+Further directions of research include on-line learning techniques for model adaptation that better follow the user profile of each individual and the possible performance change over time.
+
+\balance
 
